---
title: "Survival in colon, rectal and small intestinal cancers in the nordic countries through a half century"
subtitle: "Full R code"
author: "Filip Tichanek, Asta Försti, Vaclav Liska, Akseli Hemminki, Kari Hemminki"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  html_document:
    df_print: paged
    toc: true
    toc_float: true
  word_document: default
  toc: yes
  toc_depth: 5
  number_sections: yes
  theme: united
  pdf_document: default
urlcolor: blue
---
\large
\tableofcontents 
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
\Large
Please, **cite as** [original article](*TO BE ADDED*) published in [*TO BE ADDED*]

Full citation:
\large
[*TO BE ADDED*]

# Introduction
\large
This report shows source data, their wrangling, fitting statistical models, outputs of the models, and visualizations of both data and probabilistic models. 

All analyses were done using [R sofware](https://www.r-project.org/) in [RStudio](https://www.rstudio.com/) interface.

\newpage
## Software and Packages
\normalsize
Software versions.
\small
```{r}
rm(list=ls()) # removing all data and objects from R environment
R.version
rstudioapi::versionInfo()$version
```
\normalsize
Uploading R packages and their version
\small
```{r,errors=FALSE}
library(stringr);packageVersion('stringr')
library(brms);packageVersion('brms')
packageVersion('Rstan') # uploaded automatically with brms
library(dplyr);packageVersion('dplyr')
library(cowplot);packageVersion('cowplot')
```



\normalsize
# Incidence and mortality
\small
```{r}
## setting parameters for smoothing
spar=0.4
knot=15

## Defining colors 

cola<-c(
  rgb(1,0.1,0.1,alpha=1),
  rgb(0.1,0.1,1,alpha=1),
  rgb(0, 0.6, 0.3,alpha=1),
  rgb(0.7,0.7,0.1,alpha=1))

colb<-c(
  rgb(1,0.1,0.1,alpha=0.2),
  rgb(0.1,0.1,1,alpha=0.2),
  rgb(0, 0.6, 0.3,alpha=0.2),
  rgb(0.7,0.7,0.1,alpha=0.2))

colc<-c(
  rgb(1,0.1,0.1,alpha=0.8),
  rgb(0.1,0.1,1,alpha=0.8),
  rgb(0, 0.6, 0.3,alpha=0.8),
  rgb(0.7,0.7,0.1,alpha=0.8))

```

## Data upload and wrangling

### Colon cancer data
\normalsize
Data were downloaded from [Nordcan](https://nordcan.iarc.fr/en/dataviz/trends?sexes=1_2&cancers=90&populations=208_246_752_578&mode=population&multiple_populations=1&multiple_cancers=0&survival=1&types=0_1)

\small
```{r}
urlfile="https://raw.githubusercontent.com/filip-tichanek/nord_intestine/main/colon_inc_mor.csv"
colon_inc_mor<-read.csv(url(urlfile),sep=",")
```
\small
```{r}
colon_inc_mor
```

\normalsize
Data wrangling
\small
```{r}
colnam<-colon_inc_mor[,1]
colon_inc_mor<-data.frame(t(colon_inc_mor))[-1,]
colnames(colon_inc_mor) <- colnam
colon_inc_mor$year <- 1943:2020

### Subseting years 1961-2020
colon_inc_mor<-colon_inc_mor[colon_inc_mor$year>1960,]

### Removing space character and converting characters to numbers
x=1;repeat{
colon_inc_mor[,x]<-str_trim(colon_inc_mor[,x])
colon_inc_mor[,x]<-as.numeric(colon_inc_mor[,x])
x=x+1;if(x>17){break}}
summary(colon_inc_mor) 
```

### Rectal cancer data
\normalsize
Data were downloaded from [Nordcan](https://nordcan.iarc.fr/en/dataviz/trends?sexes=1_2&cancers=100&populations=208_246_752_578&mode=population&multiple_populations=1&multiple_cancers=0&survival=1&types=0_1)

\small
```{r}
urlfile="https://raw.githubusercontent.com/filip-tichanek/nord_intestine/main/rectum_inc_mor.csv"
rectum_inc_mor<-read.csv(url(urlfile),sep=",")
```
\normalsize
\small
```{r}
rectum_inc_mor
```

\normalsize
Data wrangling
\small
```{r}
colnam<-rectum_inc_mor[,1]
rectum_inc_mor<-data.frame(t(rectum_inc_mor))[-1,]
colnames(rectum_inc_mor) <- colnam
rectum_inc_mor$year <- 1943:2020

### Sub-setting years 1961-2020
rectum_inc_mor<-rectum_inc_mor[rectum_inc_mor$year>1960,]

### Removing space character and converting characters to numbers
x=1;repeat{
rectum_inc_mor[,x]<-str_trim(rectum_inc_mor[,x])
rectum_inc_mor[,x]<-as.numeric(rectum_inc_mor[,x])
x=x+1;if(x>17){break}}
summary(rectum_inc_mor)
```


### Small intestine data
\normalsize
Data were downloaded from [Nordcan](https://nordcan.iarc.fr/en/dataviz/trends?sexes=1_2&cancers=80&populations=208_246_752_578&mode=population&multiple_populations=1&multiple_cancers=0&survival=1&types=0_1)

\small
```{r}
urlfile="https://raw.githubusercontent.com/filip-tichanek/nord_intestine/main/small_intestine_inc_mor.csv"
small_intestine_inc_mor<-read.csv(url(urlfile),sep=",")
```
\small
```{r}
small_intestine_inc_mor
```

\normalsize
Data wrangling
\small
```{r}
colnam<-small_intestine_inc_mor[,1]
small_intestine_inc_mor<-data.frame(t(small_intestine_inc_mor))[-1,]
colnames(small_intestine_inc_mor) <- colnam
small_intestine_inc_mor$year <- 1943:2020

### Subseting years 1961-2020
small_intestine_inc_mor<-small_intestine_inc_mor[small_intestine_inc_mor$year>1960,]

### Removing space character and converting characters to numbers
x=1;repeat{
small_intestine_inc_mor[,x]<-str_trim(small_intestine_inc_mor[,x])
small_intestine_inc_mor[,x]<-as.numeric(small_intestine_inc_mor[,x])
x=x+1;if(x>17){break}}
summary(small_intestine_inc_mor)
```

## Suppl. Figure 1 - Incidence
\small
```{r, fig.height=4,fig.width=8}
### General setting and titles of plots
m <- matrix(c(1,2,3
             ,4,5,6), nrow = 2, ncol =3 ,byrow = TRUE)
layout(mat = m,heights = c(0.06,1-0.06))
par(mgp=c(1.6,0.8,0))
par(mar=c(0,0,0,0))

plot(NULL, axes=FALSE,xlab="",ylab="",xlim=c(-1,1),ylim=c(-0.85,0.85))
text(0,-0.2,"Colon cancer",cex=1.6,font=3,xpd=TRUE)

plot(NULL, axes=FALSE,xlab="",ylab="",xlim=c(-1,1),ylim=c(-0.85,0.85))
text(0,-0.2,"Rectal cancer",cex=1.6,font=3,xpd=TRUE)

plot(NULL, axes=FALSE,xlab="",ylab="",xlim=c(-1,1),ylim=c(-0.85,0.85))
text(0,-0.2,"Small intestine cancer",cex=1.6,font=3,xpd=TRUE)

## Plot of colon cancer incidence
par(mgp=c(1.6,0.8,0))
par(mar=c(2,2.5,0,0.7))

range<-c(0,30);scal<-range[2]-range[1]
xrange<-c(1961,2020)

plot(NULL,xlim=xrange,ylim=c(range[1],range[2]),xlab="",ylab=""
     ,las=1, axes=FALSE)
rect(xrange[1],range[2],xrange[2],range[1],col="grey90",border=NA)
x<-range[1]
repeat{
  lines(c(xrange[1],xrange[2]),c(x,x),col="white")
  x=x+1;if(x>range[2]){break}}

x<- round(xrange[1]+5,-1)
repeat{
  lines(c(x,x),c(range[1],range[2]),col="white")
  x=x+10;if(x>2020){break}}

data=colon_inc_mor;xx<-1
repeat{
smoothingSpline = smooth.spline(data$year, data[,xx], spar=spar, nknots=knot)
lines(smoothingSpline,col=colc[xx],lty=1,lwd=2,lend=1)
xx=xx+1;if(xx>4){break}}

repeat{
  smoothingSpline = smooth.spline(data$year, data[,xx], spar=spar, nknots=knot)
  lines(smoothingSpline,col=colc[xx-4],lty=4,lwd=2,lend=1)
  xx=xx+1;if(xx>8){break}}

axis(2,las=2,cex.axis=1.4,at=seq(range[1],range[2],by=1),
 labels=c(range[1],rep("",length(seq(range[1],range[2],by=1))-2),range[2]),pos=xrange[1])
title(ylab="Incidence per 100,000 (ASR - World)", line=1, cex.lab=1.4)
axis(side=1,las=1,cex.axis=1.4,at=c(seq(round(xrange[1]+5,-1),2020,by=10)),pos=range[1])
lines(c(xrange[1],xrange[2]),c(range[1],range[1]))
title(xlab="Year", line=1, cex.lab=1.4,xpd=TRUE)
text(1965,range[2]-0.05*scal,"a",cex=2.5)

xx=1;yy=range[1]+scal*0.25
rect(1979.7,yy+0.035*scal,2017.9,yy-0.21*scal,col="white",border="grey50",lwd=0.8)
repeat{
  lines(c(1997,2000.5),c(yy,yy),lwd=14,col=cola[xx],lend=1)
  xx<-xx+1;yy=yy-(scal*0.058);if(xx>4){break}}

text(1988,0.23*scal,"Males",cex=1.25)
lines(c(1982,1994),c(0.185*scal,0.185*scal),lwd=2)

text(1988,0.12*scal,"Females",cex=1.25)
lines(c(1982,1994),c(0.075*scal,0.075*scal),lwd=2,lty=4)

xx=1;yy=range[1]+scal*0.25
text(2008.5,yy,"Denmark",col=cola[xx],cex=1.25);xx=xx+1;yy=yy-(scal*0.058)
text(2008.5,yy,"Finland",col=cola[xx],cex=1.25);xx=xx+1;yy=yy-(scal*0.058)
text(2008.5,yy,"Norway",col=cola[xx],cex=1.25);xx=xx+1;yy=yy-(scal*0.058)
text(2008.5,yy,"Sweden",col=cola[xx],cex=1.25);xx=xx+1;yy=yy-(scal*0.058)
  
## Plot of rectal cancer incidence
  par(mgp=c(1.6,0.8,0))
  par(mar=c(2,2.5,0,0.7))
  
  range<-c(0,20);scal<-range[2]-range[1]
  xrange<-c(1961,2020)
  
  plot(NULL,xlim=xrange,ylim=c(range[1],range[2]),xlab="",ylab=""
       ,las=1, axes=FALSE)
  rect(xrange[1],range[2],xrange[2],range[1],col="grey90",border=NA)
  x<-range[1]
  repeat{
    lines(c(xrange[1],xrange[2]),c(x,x),col="white")
    x=x+1;if(x>range[2]){break}}
  
  x<- round(xrange[1]+5,-1)
  repeat{
    lines(c(x,x),c(range[1],range[2]),col="white")
    x=x+10;if(x>2020){break}}
  
  data=rectum_inc_mor;xx<-1
  repeat{
    smoothingSpline = smooth.spline(data$year, data[,xx], spar=spar, nknots=knot)
    lines(smoothingSpline,col=colc[xx],lty=1,lwd=2,lend=1)
    xx=xx+1;if(xx>4){break}}
  
  repeat{
    smoothingSpline = smooth.spline(data$year, data[,xx], spar=spar, nknots=knot)
    lines(smoothingSpline,col=colc[xx-4],lty=4,lwd=2,lend=1)
    xx=xx+1;if(xx>8){break}}
  
  axis(2,las=2,cex.axis=1.4,at=seq(range[1],range[2],by=1),
      labels=c(range[1],rep("",length(seq(range[1],range[2],by=1))-2),range[2]),pos=xrange[1])
  title(ylab="Incidence per 100,000 (ASR - World)", line=1, cex.lab=1.4)
  axis(side=1,las=1,cex.axis=1.4,at=c(seq(round(xrange[1]+5,-1),2020,by=10)),pos=range[1])
  lines(c(xrange[1],xrange[2]),c(range[1],range[1]))
  title(xlab="Year", line=1, cex.lab=1.4,xpd=TRUE)
  text(1965,range[2]-0.05*scal,"b",cex=2.5)
  
## Plot of small_intestine cancer incidence
  par(mgp=c(1.6,0.8,0))
  par(mar=c(2,2.5,0,0.7))
  
  range<-c(0,3);scal<-range[2]-range[1]
  xrange<-c(1961,2020)
  
  plot(NULL,xlim=xrange,ylim=c(range[1],range[2]),xlab="",ylab=""
       ,las=1, axes=FALSE)
  rect(xrange[1],range[2],xrange[2],range[1],col="grey90",border=NA)
  x<-range[1]
  repeat{
    lines(c(xrange[1],xrange[2]),c(x,x),col="white")
    x=x+1;if(x>range[2]){break}}
  
  x<- round(xrange[1]+5,-1)
  repeat{
    lines(c(x,x),c(range[1],range[2]),col="white")
    x=x+10;if(x>2020){break}}
  
  data=small_intestine_inc_mor;xx<-1
  repeat{
    smoothingSpline = smooth.spline(data$year, data[,xx], spar=spar, nknots=knot)
    lines(smoothingSpline,col=colc[xx],lty=1,lwd=2,lend=1)
    xx=xx+1;if(xx>4){break}}
  
  repeat{
    smoothingSpline = smooth.spline(data$year, data[,xx], spar=spar, nknots=knot)
    lines(smoothingSpline,col=colc[xx-4],lty=4,lwd=2,lend=1)
    xx=xx+1;if(xx>8){break}}


  axis(2,las=2,cex.axis=1.4,at=seq(range[1],range[2],by=1),
       labels=c(range[1],rep("",length(seq(range[1],range[2],by=1))-2),range[2]),pos=xrange[1])
  title(ylab="Incidence per 100,000 (ASR - World)", line=1, cex.lab=1.4)
  axis(side=1,las=1,cex.axis=1.4,at=c(seq(round(xrange[1]+5,-1),2020,by=10)),pos=range[1])
  lines(c(xrange[1],xrange[2]),c(range[1],range[1]))
  title(xlab="Year", line=1, cex.lab=1.4,xpd=TRUE)
  text(1965,range[2]-0.05*scal,"c",cex=2.5)
```

## Suppl. Figure 2 - Mortality
\small
```{r, fig.height=4,fig.width=8}
## General setting and titles of plots ------------
  m <- matrix(c(1,2,3
                ,4,5,6), nrow = 2, ncol =3 ,byrow = TRUE)
  layout(mat = m,heights = c(0.06,1-0.06))
  par(mgp=c(1.6,0.8,0))
  par(mar=c(0,0,0,0))
  
  plot(NULL, axes=FALSE,xlab="",ylab="",xlim=c(-1,1),ylim=c(-0.85,0.85))
  text(0,-0.2,"Colon cancer",cex=1.6,font=3,xpd=TRUE)
  
  plot(NULL, axes=FALSE,xlab="",ylab="",xlim=c(-1,1),ylim=c(-0.85,0.85))
  text(0,-0.2,"Rectal cancer",cex=1.6,font=3,xpd=TRUE)
  
  plot(NULL, axes=FALSE,xlab="",ylab="",xlim=c(-1,1),ylim=c(-0.85,0.85))
  text(0,-0.2,"Small intestine cancer",cex=1.6,font=3,xpd=TRUE)
  
## Plot of colon cancer mortality --------
  par(mgp=c(1.6,0.8,0))
  par(mar=c(2,2.5,0,0.7))
  
  range<-c(0,16);scal<-range[2]-range[1]
  xrange<-c(1961,2020)
  
  plot(NULL,xlim=xrange,ylim=c(range[1],range[2]),xlab="",ylab=""
       ,las=1, axes=FALSE)
  rect(xrange[1],range[2],xrange[2],range[1],col="grey90",border=NA)
  x<-range[1]
  repeat{
    lines(c(xrange[1],xrange[2]),c(x,x),col="white")
    x=x+1;if(x>range[2]){break}}
  
  x<- round(xrange[1]+5,-1)
  repeat{
    lines(c(x,x),c(range[1],range[2]),col="white")
    x=x+10;if(x>2020){break}}
  
  data=colon_inc_mor;xx<-9
  repeat{
    smoothingSpline = smooth.spline(data$year, data[,xx], spar=spar, nknots=knot)
    lines(smoothingSpline,col=colc[xx-8],lty=1,lwd=2,lend=1)
    xx=xx+1;if(xx>12){break}}
  
  repeat{
    smoothingSpline = smooth.spline(data$year, data[,xx], spar=spar, nknots=knot)
    lines(smoothingSpline,col=colc[xx-12],lty=4,lwd=2,lend=1)
    xx=xx+1;if(xx>16){break}}
  
  axis(2,las=2,cex.axis=1.4,at=seq(range[1],range[2],by=1),
       labels=c(range[1],rep("",length(seq(range[1],range[2],by=1))-2),range[2]),pos=xrange[1])
  title(ylab="Mortality per 100,000 (ASR - World)", line=1, cex.lab=1.4)
  axis(side=1,las=1,cex.axis=1.4,at=c(seq(round(xrange[1]+5,-1),2020,by=10)),pos=range[1])
  lines(c(xrange[1],xrange[2]),c(range[1],range[1]))
  title(xlab="Year", line=1, cex.lab=1.4,xpd=TRUE)
  text(1965,range[2]-0.05*scal,"a",cex=2.5)
  
  
## Plot of rectal cancer mortality
  par(mgp=c(1.6,0.8,0))
  par(mar=c(2,2.5,0,0.7))
  
  range<-c(0,16);scal<-range[2]-range[1]
  xrange<-c(1961,2020)
  
  plot(NULL,xlim=xrange,ylim=c(range[1],range[2]),xlab="",ylab=""
       ,las=1, axes=FALSE)
  rect(xrange[1],range[2],xrange[2],range[1],col="grey90",border=NA)
  x<-range[1]
  repeat{
    lines(c(xrange[1],xrange[2]),c(x,x),col="white")
    x=x+1;if(x>range[2]){break}}
  
  x<- round(xrange[1]+5,-1)
  repeat{
    lines(c(x,x),c(range[1],range[2]),col="white")
    x=x+10;if(x>2020){break}}
  
  data=rectum_inc_mor;xx<-9
  repeat{
    smoothingSpline = smooth.spline(data$year, data[,xx], spar=spar, nknots=knot)
    lines(smoothingSpline,col=colc[xx-8],lty=1,lwd=2,lend=1)
    xx=xx+1;if(xx>12){break}}
  
  repeat{
    smoothingSpline = smooth.spline(data$year, data[,xx], spar=spar, nknots=knot)
    lines(smoothingSpline,col=colc[xx-12],lty=4,lwd=2,lend=1)
    xx=xx+1;if(xx>16){break}}
  
  axis(2,las=2,cex.axis=1.4,at=seq(range[1],range[2],by=1),
    labels=c(range[1],rep("",length(seq(range[1],range[2],by=1))-2),range[2]),pos=xrange[1])
  title(ylab="Mortality per 100,000 (ASR - World)", line=1, cex.lab=1.4)
  axis(side=1,las=1,cex.axis=1.4,at=c(seq(round(xrange[1]+5,-1),2020,by=10)),pos=range[1])
  lines(c(xrange[1],xrange[2]),c(range[1],range[1]))
  title(xlab="Year", line=1, cex.lab=1.4,xpd=TRUE)
  text(1965,range[2]-0.05*scal,"b",cex=2.5)
  
  xx=1;
  yr=range[1]+scal*0.95
  yy=yr
  rect(1979.7,yy+0.035*scal,2017.9,yy-0.21*scal,col="white",border="grey50",lwd=0.8)
  repeat{
    lines(c(1997,2000.5),c(yy,yy),lwd=14,col=cola[xx],lend=1)
    xx<-xx+1;yy=yy-(scal*0.058);if(xx>4){break}}
  
  
  text(1988,0.93*scal,"Males",cex=1.25)
  lines(c(1982,1994),c(0.885*scal,0.885*scal),lwd=2)
  
  text(1988,0.82*scal,"Females",cex=1.25)
  lines(c(1982,1994),c(0.775*scal,0.775*scal),lwd=2,lty=4)
  
  xx=1;yy=range[1]+scal*0.95
  text(2008.5,yy,"Denmark",col=cola[xx],cex=1.25);xx=xx+1;yy=yy-(scal*0.058)
  text(2008.5,yy,"Finland",col=cola[xx],cex=1.25);xx=xx+1;yy=yy-(scal*0.058)
  text(2008.5,yy,"Norway",col=cola[xx],cex=1.25);xx=xx+1;yy=yy-(scal*0.058)
  text(2008.5,yy,"Sweden",col=cola[xx],cex=1.25);xx=xx+1;yy=yy-(scal*0.058)
  
## Plot of small_intestine cancer mortality 
  par(mgp=c(1.6,0.8,0))
  par(mar=c(2,2.5,0,0.7))
  
  range<-c(0,1);scal<-range[2]-range[1]
  xrange<-c(1961,2020)
  
  plot(NULL,xlim=xrange,ylim=c(range[1],range[2]),xlab="",ylab=""
       ,las=1, axes=FALSE)
  rect(xrange[1],range[2],xrange[2],range[1],col="grey90",border=NA)
  x<-range[1]
  repeat{
    lines(c(xrange[1],xrange[2]),c(x,x),col="white")
    x=x+1;if(x>range[2]){break}}
  
  x<- round(xrange[1]+5,-1)
  repeat{
    lines(c(x,x),c(range[1],range[2]),col="white")
    x=x+10;if(x>2020){break}}
  
  data=small_intestine_inc_mor;xx<-9
  repeat{
    smoothingSpline = smooth.spline(data$year, data[,xx], spar=spar, nknots=knot)
    lines(smoothingSpline,col=colc[xx-8],lty=1,lwd=2,lend=1)
    xx=xx+1;if(xx>12){break}}
  
  repeat{
    smoothingSpline = smooth.spline(data$year, data[,xx], spar=spar, nknots=knot)
    lines(smoothingSpline,col=colc[xx-12],lty=4,lwd=2,lend=1)
    xx=xx+1;if(xx>16){break}}
  
  axis(2,las=2,cex.axis=1.4,at=seq(range[1],range[2],by=1),labels=c(range[1],                          rep("",length(seq(range[1],range[2],by=1))-2),range[2]),pos=xrange[1])
  title(ylab="Mortality per 100,000 (ASR - World)", line=1, cex.lab=1.4)
  axis(side=1,las=1,cex.axis=1.4,at=c(seq(round(xrange[1]+5,-1),2020,by=10)),pos=range[1])
  lines(c(xrange[1],xrange[2]),c(range[1],range[1]))
  title(xlab="Year", line=1, cex.lab=1.4,xpd=TRUE)
  text(1965,range[2]-0.05*scal,"c",cex=2.5)
  
```

# Non-linear trends in survival


## Defining priors
\small
```{r,errors=FALSE}
prior_group <- c(
  set_prior("normal(0,30)", class = "b", coef = "groupFinland.Males"),
  set_prior("normal(0,30)", class = "b", coef = "groupNorway.Males"),
  set_prior("normal(0,30)", class = "b", coef = "groupSweden.Males"),
  set_prior("normal(0,30)", class = "b", coef = "groupDenmark.Males"),
  set_prior("normal(0,30)", class = "b", coef = "groupNorway.Females"),
  set_prior("normal(0,30)", class = "b", coef = "groupFinland.Females"),
  set_prior("normal(0,30)", class = "b", coef = "groupSweden.Females"))
```

## Source data
\normalsize
Data were downloaded from [Nordcan](https://nordcan.iarc.fr/en) in October 2022.

Here are links to 1-year survival in: [colon](https://nordcan.iarc.fr/en/dataviz/survival?populations=208_578_246_752&multiple_populations=1&multiple_cancers=0&survival=1&cancers=90&sexes=1_2&mode=population), [rectal](https://nordcan.iarc.fr/en/dataviz/survival?populations=208_578_246_752&multiple_populations=1&multiple_cancers=0&survival=1&cancers=100&sexes=1_2&mode=population), [small intestine](https://nordcan.iarc.fr/en/dataviz/survival?populations=208_578_246_752&multiple_populations=1&multiple_cancers=0&survival=1&cancers=80&sexes=1_2&mode=population) cancers

Here are links to 5-years survival in: [colon](https://nordcan.iarc.fr/en/dataviz/survival?populations=208_578_246_752&multiple_populations=1&multiple_cancers=0&survival=5&cancers=90&sexes=1_2&mode=population), [rectal](https://nordcan.iarc.fr/en/dataviz/survival?populations=208_578_246_752&multiple_populations=1&multiple_cancers=0&survival=5&cancers=100&sexes=1_2&mode=population), [small intestine](https://nordcan.iarc.fr/en/dataviz/survival?populations=208_578_246_752&multiple_populations=1&multiple_cancers=0&survival=5&cancers=80&sexes=1_2&mode=population) cancers

\small
```{r}
urlfile="https://raw.githubusercontent.com/filip-tichanek/nord_intestine/main/colon_1y.csv"
colon_1y<-read.csv(url(urlfile),sep=";")

urlfile="https://raw.githubusercontent.com/filip-tichanek/nord_intestine/main/colon_5y.csv"
colon_5y<-read.csv(url(urlfile),sep=";")

urlfile="https://raw.githubusercontent.com/filip-tichanek/nord_intestine/main/rectum_1y.csv"
rectum_1y<-read.csv(url(urlfile),sep=";")

urlfile="https://raw.githubusercontent.com/filip-tichanek/nord_intestine/main/rectum_5y.csv"
rectum_5y<-read.csv(url(urlfile),sep=";")

urlfile="https://raw.githubusercontent.com/filip-tichanek/nord_intestine/main/small_intestine_1y.csv"
small_intestine_1y<-read.csv(url(urlfile),sep=";")

urlfile="https://raw.githubusercontent.com/filip-tichanek/nord_intestine/main/small_intestine_5y.csv"
small_intestine_5y<-read.csv(url(urlfile),sep=";")
```
\normalsize
In the tables below, there are data seen also in **Supplementary Table 3**. Columns ending with '.1' indicate data for females (right columns) whereas others are for males (left columns)
\small
```{r}
colon_1y
colon_5y
rectum_1y
rectum_5y
small_intestine_1y
small_intestine_5y
```

## Data wrangling
### Colon cancer
\small
```{r}
x<-2;colon_1y_est<-data.frame(colon_1y[,1])
repeat{colon_1y_est[,x]<-str_sub(colon_1y[,x],1,4);x<-x+1
if(x>9){break}}
repeat{colon_1y_est[,x]<-str_sub(colon_1y[,x-8],6,9);x<-x+1;if(x>17){break}}
x<-2;colon_5y_est<-data.frame(colon_5y[,1])
repeat{colon_5y_est[,x]<-str_sub(colon_5y[,x],1,4);x<-x+1
if(x>9){break}}
repeat{colon_5y_est[,x]<-str_sub(colon_5y[,x-8],6,9);x<-x+1;if(x>17){break}}

colon<-(data.frame(unlist(colon_1y_est[,2:9])));colnames(colon)<-"surv_1y"
colon$cil_1y<-as.numeric(unlist(colon_1y_est[,10:17]))
colon$surv_5y<-as.numeric(unlist(colon_5y_est[,2:9]))
colon$cil_5y<-as.numeric(unlist(colon_5y_est[,10:17]))
colon$year<-rep(seq(1973,2018,by=5),8)
colon$sex<-c(rep("Males",40),rep("Females",40))
colon$country<-c(rep(c(rep("Denmark",10),rep("Finland",10),rep("Norway",10),rep("Sweden",10)),2))
colon$group<-interaction(colon$country,colon$sex)
colon$years10cen<-(colon$year-1995.5)/10 # centered time in tens of years
colon$surv_1y<-as.numeric(colon$surv_1y)
colon$surv_5y<-as.numeric(colon$surv_5y)
colon$cil_1y<-as.numeric(colon$cil_1y)
colon$cil_5y<-as.numeric(colon$cil_5y)
colon$se_1y<-(colon$surv_1y-colon$cil_1y)/1.96
colon$se_5y<-(colon$surv_5y-colon$cil_5y)/1.96
colon$surv_cond<-(colon$surv_5y/colon$surv_1y)*100
colon
```

### Rectal cancer
\small
```{r}
x<-2;rectum_1y_est<-data.frame(rectum_1y[,1])
repeat{rectum_1y_est[,x]<-str_sub(rectum_1y[,x],1,4);x<-x+1
if(x>9){break}}
repeat{rectum_1y_est[,x]<-str_sub(rectum_1y[,x-8],6,9);x<-x+1;if(x>17){break}}
x<-2;rectum_5y_est<-data.frame(rectum_5y[,1])
repeat{rectum_5y_est[,x]<-str_sub(rectum_5y[,x],1,4);x<-x+1
if(x>9){break}}
repeat{rectum_5y_est[,x]<-str_sub(rectum_5y[,x-8],6,9);x<-x+1;if(x>17){break}}

rectum<-(data.frame(unlist(rectum_1y_est[,2:9])));colnames(rectum)<-"surv_1y"
rectum$cil_1y<-as.numeric(unlist(rectum_1y_est[,10:17]))
rectum$surv_5y<-as.numeric(unlist(rectum_5y_est[,2:9]))
rectum$cil_5y<-as.numeric(unlist(rectum_5y_est[,10:17]))
rectum$year<-rep(seq(1973,2018,by=5),8)
rectum$sex<-c(rep("Males",40),rep("Females",40))
rectum$country<-c(rep(c(rep("Denmark",10),rep("Finland",10),rep("Norway",10),rep("Sweden",10)),2))
rectum$group<-interaction(rectum$country,rectum$sex)
rectum$years10cen<-(rectum$year-1995.5)/10 # centered time in tens of years
rectum$surv_1y<-as.numeric(rectum$surv_1y)
rectum$surv_5y<-as.numeric(rectum$surv_5y)
rectum$cil_1y<-as.numeric(rectum$cil_1y)
rectum$cil_5y<-as.numeric(rectum$cil_5y)
rectum$se_1y<-(rectum$surv_1y-rectum$cil_1y)/1.96
rectum$se_5y<-(rectum$surv_5y-rectum$cil_5y)/1.96
rectum$surv_cond<-(rectum$surv_5y/rectum$surv_1y)*100
rectum
```


### Small intestine cancer
\small
```{r}
x<-2;small_intestine_1y_est<-data.frame(small_intestine_1y[,1])
repeat{small_intestine_1y_est[,x]<-str_sub(small_intestine_1y[,x],1,4);x<-x+1
if(x>9){break}}
repeat{small_intestine_1y_est[,x]<-str_sub(small_intestine_1y[,x-8],6,9);x<-x+1;if(x>17){break}}
x<-2;small_intestine_5y_est<-data.frame(small_intestine_5y[,1])
repeat{small_intestine_5y_est[,x]<-str_sub(small_intestine_5y[,x],1,4);x<-x+1
if(x>9){break}}
repeat{small_intestine_5y_est[,x]<-str_sub(small_intestine_5y[,x-8],6,9);x<-x+1;if(x>17){break}}

small_intestine<-(data.frame(unlist(small_intestine_1y_est[,2:9])));colnames(small_intestine)<-"surv_1y"
small_intestine$cil_1y<-as.numeric(unlist(small_intestine_1y_est[,10:17]))
small_intestine$surv_5y<-as.numeric(unlist(small_intestine_5y_est[,2:9]))
small_intestine$cil_5y<-as.numeric(unlist(small_intestine_5y_est[,10:17]))
small_intestine$year<-rep(seq(1973,2018,by=5),8)
small_intestine$sex<-c(rep("Males",40),rep("Females",40))
small_intestine$country<-c(rep(c(rep("Denmark",10),rep("Finland",10),rep("Norway",10),rep("Sweden",10)),2))
small_intestine$group<-interaction(small_intestine$country,small_intestine$sex)
small_intestine$years10cen<-(small_intestine$year-1995.5)/10 # centered time in tens of years
small_intestine$surv_1y<-as.numeric(small_intestine$surv_1y)
small_intestine$surv_5y<-as.numeric(small_intestine$surv_5y)
small_intestine$cil_1y<-as.numeric(small_intestine$cil_1y)
small_intestine$cil_5y<-as.numeric(small_intestine$cil_5y)
small_intestine$se_1y<-(small_intestine$surv_1y-small_intestine$cil_1y)/1.96
small_intestine$se_5y<-(small_intestine$surv_5y-small_intestine$cil_5y)/1.96
small_intestine$surv_cond<-(small_intestine$surv_5y/small_intestine$surv_1y)*100
small_intestine
```

## Models

### Defining colon models

\small
```{r, results = 'hide',cache=TRUE}
set.seed(17)
colon_1y_model<-brm(surv_1y|se(se_1y)~group+s(years10cen,by=group,k=5)
    ,family="Gaussian",save_pars = save_pars(all = TRUE),prior=prior_group,seed=17
    ,data=colon,iter=7000, warmup=2000,chains=2,cores=1,control = list(adapt_delta = 0.98))
conditional_effects(colon_1y_model,effects='years10cen:group')

colon_5y_model<-brm(surv_5y|se(se_5y)~group+s(years10cen,by=group,k=5)
    ,family="Gaussian",save_pars = save_pars(all = TRUE),prior=prior_group,seed=17
    ,data=colon,iter=7000, warmup=2000,chains=2,cores=1,control = list(adapt_delta = 0.98))
conditional_effects(colon_5y_model,effects='years10cen:group')
```

### Defining rectal models
```{r, results = 'hide',cache=TRUE}
set.seed(17)
rectum_1y_model<-brm(surv_1y|se(se_1y)~group+s(years10cen,by=group,k=5)
      ,family="Gaussian",save_pars = save_pars(all = TRUE),prior=prior_group,seed=17
      ,data=rectum,iter=7000, warmup=2000,chains=2,cores=1,control = list(adapt_delta = 0.98))
conditional_effects(rectum_1y_model,effects='years10cen:group')

rectum_5y_model<-brm(surv_5y|se(se_5y)~group+s(years10cen,by=group,k=5)
     ,family="Gaussian",save_pars = save_pars(all = TRUE),prior=prior_group,seed=17
     ,data=rectum,iter=7000, warmup=2000,chains=2,cores=1,control = list(adapt_delta = 0.98))
conditional_effects(rectum_5y_model,effects='years10cen:group')
```

### Defining Small intestine models
```{r, results = 'hide', cache=TRUE}
set.seed(17)
small_intestine_1y_model<-brm(surv_1y|se(se_1y)~group+s(years10cen,by=group,k=5),
   family="Gaussian",save_pars = save_pars(all = TRUE),prior=prior_group,seed=17,
   data=small_intestine,iter=7000, warmup=2000,
   chains=2,cores=1,control = list(adapt_delta = 0.98))
conditional_effects(small_intestine_1y_model,effects='years10cen:group')

small_intestine_5y_model<-brm(surv_5y|se(se_5y)~group+s(years10cen,by=group,k=5)
    ,family="Gaussian",save_pars = save_pars(all = TRUE),prior=prior_group,seed=17
   ,data=small_intestine,iter=7000, warmup=2000,chains=2,cores=1,control = list(adapt_delta = 0.98))
conditional_effects(small_intestine_5y_model,effects='years10cen:group')
```

## Diagnostics of models

\normalsize
In general, diagnostics uses:

[1] *summary(model)*: the columns of intereste are ***Rhat*** (when = 1, model converged well), and columns ***Tail_ESS*** and ***Bulk_ESS*** which should never go under 1,000 and should be mostly above 2,000.  

[2] *pp_check* : graphical tools to explore how well the model predicts real data. 

[not shown in this report] : use also *plot(model)* (not shown as it produces a lot of figures). 

### Colon model diagnostics
```{r,cache=TRUE}
summary(colon_1y_model)
summary(colon_5y_model)

pla<-pp_check(colon_1y_model,type='dens_overlay',ndraws = 100) 
plb<-pp_check(colon_5y_model,type='dens_overlay',ndraws = 100) 
plot_grid(pla, plb, labels=c("A", "B"), ncol = 1, nrow = 2)

pla<-pp_check(colon_1y_model,type='scatter_avg') 
plb<-pp_check(colon_5y_model,type='scatter_avg') 
plot_grid(pla, plb, labels=c("A", "B"), ncol = 1, nrow = 2)

pla<-pp_check(colon_1y_model,type='ecdf_overlay',ndraws = 100) 
plb<-pp_check(colon_5y_model,type='ecdf_overlay',ndraws = 100) 
plot_grid(pla, plb, labels=c("A", "B"), ncol = 1, nrow = 2)

pla<-pp_check(colon_1y_model,type ="stat", stat = "mean")
plb<-pp_check(colon_5y_model,type = "stat", stat = "mean")
plot_grid(pla, plb, labels=c("A", "B"), ncol = 1, nrow = 2)

pla<-pp_check(colon_1y_model,type="stat_2d", stat = c("max", "min"),ndraws=200)
plb<-pp_check(colon_5y_model,type="stat_2d", stat = c("max", "min"),ndraws=200)
plot_grid(pla, plb, labels=c("A", "B"), ncol = 1, nrow = 2)
```


### Rectum models diagnostics
```{r,cache=TRUE}
summary(colon_1y_model)
summary(colon_5y_model)

pla<-pp_check(colon_1y_model,type='dens_overlay',ndraws = 100) 
plb<-pp_check(colon_5y_model,type='dens_overlay',ndraws = 100) 
plot_grid(pla, plb, labels=c("A", "B"), ncol = 1, nrow = 2)

pla<-pp_check(colon_1y_model,type='scatter_avg') 
plb<-pp_check(colon_5y_model,type='scatter_avg') 
plot_grid(pla, plb, labels=c("A", "B"), ncol = 1, nrow = 2)

pla<-pp_check(colon_1y_model,type='ecdf_overlay',ndraws = 100) 
plb<-pp_check(colon_5y_model,type='ecdf_overlay',ndraws = 100) 
plot_grid(pla, plb, labels=c("A", "B"), ncol = 1, nrow = 2)

pla<-pp_check(colon_1y_model,type ="stat", stat = "mean")
plb<-pp_check(colon_5y_model,type = "stat", stat = "mean")
plot_grid(pla, plb, labels=c("A", "B"), ncol = 1, nrow = 2)

pla<-pp_check(colon_1y_model,type="stat_2d", stat = c("max", "min"),ndraws=200)
plb<-pp_check(colon_5y_model,type="stat_2d", stat = c("max", "min"),ndraws=200)
plot_grid(pla, plb, labels=c("A", "B"), ncol = 1, nrow = 2)
```

### Small intestine diag.
```{r,cache=TRUE}
summary(small_intestine_1y_model)
summary(small_intestine_5y_model)

pla<-pp_check(small_intestine_1y_model,type='dens_overlay',ndraws = 100) 
plb<-pp_check(small_intestine_5y_model,type='dens_overlay',ndraws = 100) 
plot_grid(pla, plb, labels=c("A", "B"), ncol = 1, nrow = 2)

pla<-pp_check(small_intestine_1y_model,type='scatter_avg') 
plb<-pp_check(small_intestine_5y_model,type='scatter_avg') 
plot_grid(pla, plb, labels=c("A", "B"), ncol = 1, nrow = 2)

pla<-pp_check(small_intestine_1y_model,type='ecdf_overlay',ndraws = 100) 
plb<-pp_check(small_intestine_5y_model,type='ecdf_overlay',ndraws = 100) 
plot_grid(pla, plb, labels=c("A", "B"), ncol = 1, nrow = 2)

pla<-pp_check(small_intestine_1y_model,type ="stat", stat = "mean")
plb<-pp_check(small_intestine_5y_model,type = "stat", stat = "mean")
plot_grid(pla, plb, labels=c("A", "B"), ncol = 1, nrow = 2)

pla<-pp_check(small_intestine_1y_model,type="stat_2d", stat = c("max", "min"),ndraws=200)
plb<-pp_check(small_intestine_5y_model,type="stat_2d", stat = c("max", "min"),ndraws=200)
plot_grid(pla, plb, labels=c("A", "B"), ncol = 1, nrow = 2)
```


## Extraction of posterior samples

### Colon models samples

\small
```{r}
first <- expand.grid(years10cen = seq(-2.45, 2.45, length=500),
                     group = c('Denmark.Females','Finland.Females','Norway.Females','Sweden.Females','Denmark.Males','Finland.Males','Norway.Males','Sweden.Males'), y = 0)
yreal <- (first[,1]*10)+1995.5 
ms_1y<-posterior_smooths(colon_1y_model,smooth="s(years10cen,by=group,k=5)",newdata = first)
post_fix<-as.data.frame(colon_1y_model, variable = c("b_Intercept","b_groupFinland.Females","b_groupNorway.Females","b_groupSweden.Females","b_groupDenmark.Males", "b_groupFinland.Males","b_groupNorway.Males","b_groupSweden.Males"))

post_colon_den_fem_1y<-ms_1y[,1:500]     +post_fix[,1]
post_colon_fin_fem_1y<-ms_1y[,501:1000]  +post_fix[,1]+post_fix[,2]
post_colon_nor_fem_1y<-ms_1y[,1001:1500] +post_fix[,1]+post_fix[,3]
post_colon_swe_fem_1y<-ms_1y[,1501:2000] +post_fix[,1]+post_fix[,4]
post_colon_den_mal_1y<-ms_1y[,2001:2500] +post_fix[,1]+post_fix[,5]
post_colon_fin_mal_1y<-ms_1y[,2501:3000] +post_fix[,1]+post_fix[,6]
post_colon_nor_mal_1y<-ms_1y[,3001:3500] +post_fix[,1]+post_fix[,7]
post_colon_swe_mal_1y<-ms_1y[,3501:4000] +post_fix[,1]+post_fix[,8]

post_fix<-as.data.frame(colon_5y_model, variable = c("b_Intercept","b_groupFinland.Females", "b_groupNorway.Females","b_groupSweden.Females","b_groupDenmark.Males","b_groupFinland.Males","b_groupNorway.Males","b_groupSweden.Males"))
ms_5y<-posterior_smooths(colon_5y_model,smooth="s(years10cen,by=group,k=5)",newdata = first)
post_colon_den_fem_5y<-ms_5y[,1:500]     +post_fix[,1]
post_colon_fin_fem_5y<-ms_5y[,501:1000]  +post_fix[,1]+post_fix[,2]
post_colon_nor_fem_5y<-ms_5y[,1001:1500] +post_fix[,1]+post_fix[,3]
post_colon_swe_fem_5y<-ms_5y[,1501:2000] +post_fix[,1]+post_fix[,4]
post_colon_den_mal_5y<-ms_5y[,2001:2500] +post_fix[,1]+post_fix[,5]
post_colon_fin_mal_5y<-ms_5y[,2501:3000] +post_fix[,1]+post_fix[,6]
post_colon_nor_mal_5y<-ms_5y[,3001:3500] +post_fix[,1]+post_fix[,7]
post_colon_swe_mal_5y<-ms_5y[,3501:4000] +post_fix[,1]+post_fix[,8]

post_colon_den_fem_cond<-(post_colon_den_fem_5y/post_colon_den_fem_1y)*100
post_colon_den_mal_cond<-(post_colon_den_mal_5y/post_colon_den_mal_1y)*100
post_colon_fin_fem_cond<-(post_colon_fin_fem_5y/post_colon_fin_fem_1y)*100
post_colon_fin_mal_cond<-(post_colon_fin_mal_5y/post_colon_fin_mal_1y)*100
post_colon_nor_fem_cond<-(post_colon_nor_fem_5y/post_colon_nor_fem_1y)*100
post_colon_nor_mal_cond<-(post_colon_nor_mal_5y/post_colon_nor_mal_1y)*100
post_colon_swe_fem_cond<-(post_colon_swe_fem_5y/post_colon_swe_fem_1y)*100
post_colon_swe_mal_cond<-(post_colon_swe_mal_5y/post_colon_swe_mal_1y)*100
```

### Rectum models samples
\small
```{r}
ms_1y<-posterior_smooths(rectum_1y_model,smooth="s(years10cen,by=group,k=5)",newdata = first)
post_fix<-as.data.frame(rectum_1y_model, variable = c("b_Intercept","b_groupFinland.Females","b_groupNorway.Females","b_groupSweden.Females","b_groupDenmark.Males","b_groupFinland.Males","b_groupNorway.Males","b_groupSweden.Males"))

post_rectum_den_fem_1y<-ms_1y[,1:500]     +post_fix[,1]
post_rectum_fin_fem_1y<-ms_1y[,501:1000]  +post_fix[,1]+post_fix[,2]
post_rectum_nor_fem_1y<-ms_1y[,1001:1500] +post_fix[,1]+post_fix[,3]
post_rectum_swe_fem_1y<-ms_1y[,1501:2000] +post_fix[,1]+post_fix[,4]
post_rectum_den_mal_1y<-ms_1y[,2001:2500] +post_fix[,1]+post_fix[,5]
post_rectum_fin_mal_1y<-ms_1y[,2501:3000] +post_fix[,1]+post_fix[,6]
post_rectum_nor_mal_1y<-ms_1y[,3001:3500] +post_fix[,1]+post_fix[,7]
post_rectum_swe_mal_1y<-ms_1y[,3501:4000] +post_fix[,1]+post_fix[,8]

post_fix<-as.data.frame(rectum_5y_model, variable = c("b_Intercept","b_groupFinland.Females","b_groupNorway.Females","b_groupSweden.Females","b_groupDenmark.Males","b_groupFinland.Males","b_groupNorway.Males","b_groupSweden.Males"))
ms_5y<-posterior_smooths(rectum_5y_model,smooth="s(years10cen,by=group,k=5)",newdata = first)
post_rectum_den_fem_5y<-ms_5y[,1:500]     +post_fix[,1]
post_rectum_fin_fem_5y<-ms_5y[,501:1000]  +post_fix[,1]+post_fix[,2]
post_rectum_nor_fem_5y<-ms_5y[,1001:1500] +post_fix[,1]+post_fix[,3]
post_rectum_swe_fem_5y<-ms_5y[,1501:2000] +post_fix[,1]+post_fix[,4]
post_rectum_den_mal_5y<-ms_5y[,2001:2500] +post_fix[,1]+post_fix[,5]
post_rectum_fin_mal_5y<-ms_5y[,2501:3000] +post_fix[,1]+post_fix[,6]
post_rectum_nor_mal_5y<-ms_5y[,3001:3500] +post_fix[,1]+post_fix[,7]
post_rectum_swe_mal_5y<-ms_5y[,3501:4000] +post_fix[,1]+post_fix[,8]

post_rectum_den_fem_cond<-(post_rectum_den_fem_5y/post_rectum_den_fem_1y)*100
post_rectum_den_mal_cond<-(post_rectum_den_mal_5y/post_rectum_den_mal_1y)*100
post_rectum_fin_fem_cond<-(post_rectum_fin_fem_5y/post_rectum_fin_fem_1y)*100
post_rectum_fin_mal_cond<-(post_rectum_fin_mal_5y/post_rectum_fin_mal_1y)*100
post_rectum_nor_fem_cond<-(post_rectum_nor_fem_5y/post_rectum_nor_fem_1y)*100
post_rectum_nor_mal_cond<-(post_rectum_nor_mal_5y/post_rectum_nor_mal_1y)*100
post_rectum_swe_fem_cond<-(post_rectum_swe_fem_5y/post_rectum_swe_fem_1y)*100
post_rectum_swe_mal_cond<-(post_rectum_swe_mal_5y/post_rectum_swe_mal_1y)*100
```

### Small intestine posteriors
\small
```{r}
ms_1y<-posterior_smooths(small_intestine_1y_model,smooth="s(years10cen,by=group,k=5)",newdata = first)
post_fix<-as.data.frame(small_intestine_1y_model, variable = c("b_Intercept", "b_groupFinland.Females","b_groupNorway.Females","b_groupSweden.Females","b_groupDenmark.Males" ,"b_groupFinland.Males","b_groupNorway.Males","b_groupSweden.Males"))

post_small_intestine_den_fem_1y<-ms_1y[,1:500]     +post_fix[,1]
post_small_intestine_fin_fem_1y<-ms_1y[,501:1000]  +post_fix[,1]+post_fix[,2]
post_small_intestine_nor_fem_1y<-ms_1y[,1001:1500] +post_fix[,1]+post_fix[,3]
post_small_intestine_swe_fem_1y<-ms_1y[,1501:2000] +post_fix[,1]+post_fix[,4]
post_small_intestine_den_mal_1y<-ms_1y[,2001:2500] +post_fix[,1]+post_fix[,5]
post_small_intestine_fin_mal_1y<-ms_1y[,2501:3000] +post_fix[,1]+post_fix[,6]
post_small_intestine_nor_mal_1y<-ms_1y[,3001:3500] +post_fix[,1]+post_fix[,7]
post_small_intestine_swe_mal_1y<-ms_1y[,3501:4000] +post_fix[,1]+post_fix[,8]

post_fix<-as.data.frame(small_intestine_5y_model, variable = c("b_Intercept",
    "b_groupFinland.Females","b_groupNorway.Females","b_groupSweden.Females",
    "b_groupDenmark.Males","b_groupFinland.Males","b_groupNorway.Males","b_groupSweden.Males"))
ms_5y<-posterior_smooths(small_intestine_5y_model,smooth="s(years10cen,by=group,k=5)",newdata = first)
post_small_intestine_den_fem_5y<-ms_5y[,1:500]     +post_fix[,1]
post_small_intestine_fin_fem_5y<-ms_5y[,501:1000]  +post_fix[,1]+post_fix[,2]
post_small_intestine_nor_fem_5y<-ms_5y[,1001:1500] +post_fix[,1]+post_fix[,3]
post_small_intestine_swe_fem_5y<-ms_5y[,1501:2000] +post_fix[,1]+post_fix[,4]
post_small_intestine_den_mal_5y<-ms_5y[,2001:2500] +post_fix[,1]+post_fix[,5]
post_small_intestine_fin_mal_5y<-ms_5y[,2501:3000] +post_fix[,1]+post_fix[,6]
post_small_intestine_nor_mal_5y<-ms_5y[,3001:3500] +post_fix[,1]+post_fix[,7]
post_small_intestine_swe_mal_5y<-ms_5y[,3501:4000] +post_fix[,1]+post_fix[,8]

post_small_intestine_den_fem_cond<-(post_small_intestine_den_fem_5y/post_small_intestine_den_fem_1y)*100
post_small_intestine_den_mal_cond<-(post_small_intestine_den_mal_5y/post_small_intestine_den_mal_1y)*100
post_small_intestine_fin_fem_cond<-(post_small_intestine_fin_fem_5y/post_small_intestine_fin_fem_1y)*100
post_small_intestine_fin_mal_cond<-(post_small_intestine_fin_mal_5y/post_small_intestine_fin_mal_1y)*100
post_small_intestine_nor_fem_cond<-(post_small_intestine_nor_fem_5y/post_small_intestine_nor_fem_1y)*100
post_small_intestine_nor_mal_cond<-(post_small_intestine_nor_mal_5y/post_small_intestine_nor_mal_1y)*100
post_small_intestine_swe_fem_cond<-(post_small_intestine_swe_fem_5y/post_small_intestine_swe_fem_1y)*100
post_small_intestine_swe_mal_cond<-(post_small_intestine_swe_mal_5y/post_small_intestine_swe_mal_1y)*100

```

## Samples for Visualisation
\normalsize

The following code wrangles the posterior samples into a form useful for further visualization. It extracts posterior samples for the 1st (slope of survival trend) and the 2nd (change of the trend) derivations of a given relative survival measure. It also uses posterior samples for prediction lines and a 95% credible interval (CI) for relative survival over time and the 1st and 2nd derivations of the survival measure over time. 
```{r}
## Colon cancer ------------------------------------------------------------

### 1y ----------------------------------------------------------------------
slope_den_colon_mal_1y<-(post_colon_den_mal_1y[,-1] - post_colon_den_mal_1y[,-ncol(post_colon_den_mal_1y)])*10
slope_den_colon_mal_1y<-data.frame(slope_den_colon_mal_1y)
slope_den_colon_fem_1y<-(post_colon_den_fem_1y[,-1] - post_colon_den_fem_1y[,-ncol(post_colon_den_fem_1y)])*10
slope_den_colon_fem_1y<-data.frame(slope_den_colon_fem_1y)

slope_fin_colon_mal_1y<-(post_colon_fin_mal_1y[,-1] - post_colon_fin_mal_1y[,-ncol(post_colon_fin_mal_1y)])*10
slope_fin_colon_mal_1y<-data.frame(slope_fin_colon_mal_1y)
slope_fin_colon_fem_1y<-(post_colon_fin_fem_1y[,-1] - post_colon_fin_fem_1y[,-ncol(post_colon_fin_fem_1y)])*10
slope_fin_colon_fem_1y<-data.frame(slope_fin_colon_fem_1y)

slope_nor_colon_mal_1y<-(post_colon_nor_mal_1y[,-1] - post_colon_nor_mal_1y[,-ncol(post_colon_nor_mal_1y)])*10
slope_nor_colon_mal_1y<-data.frame(slope_nor_colon_mal_1y)
slope_nor_colon_fem_1y<-(post_colon_nor_fem_1y[,-1] - post_colon_nor_fem_1y[,-ncol(post_colon_nor_fem_1y)])*10
slope_nor_colon_fem_1y<-data.frame(slope_nor_colon_fem_1y)

slope_swe_colon_mal_1y<-(post_colon_swe_mal_1y[,-1] - post_colon_swe_mal_1y[,-ncol(post_colon_swe_mal_1y)])*10
slope_swe_colon_mal_1y<-data.frame(slope_swe_colon_mal_1y)
slope_swe_colon_fem_1y<-(post_colon_swe_fem_1y[,-1] - post_colon_swe_fem_1y[,-ncol(post_colon_swe_fem_1y)])*10
slope_swe_colon_fem_1y<-data.frame(slope_swe_colon_fem_1y)

cis_den_colon_mal_1y<-sapply(slope_den_colon_mal_1y, function(p) quantile(p, probs = c(0.025,0.975,0.5)))
cis_den_colon_fem_1y<-sapply(slope_den_colon_fem_1y, function(p) quantile(p, probs = c(0.025,0.975,0.5)))
cis_fin_colon_mal_1y<-sapply(slope_fin_colon_mal_1y, function(p) quantile(p, probs = c(0.025,0.975,0.5)))
cis_fin_colon_fem_1y<-sapply(slope_fin_colon_fem_1y, function(p) quantile(p, probs = c(0.025,0.975,0.5)))
cis_nor_colon_mal_1y<-sapply(slope_nor_colon_mal_1y, function(p) quantile(p, probs = c(0.025,0.975,0.5)))
cis_nor_colon_fem_1y<-sapply(slope_nor_colon_fem_1y, function(p) quantile(p, probs = c(0.025,0.975,0.5)))
cis_swe_colon_mal_1y<-sapply(slope_swe_colon_mal_1y, function(p) quantile(p, probs = c(0.025,0.975,0.5)))
cis_swe_colon_fem_1y<-sapply(slope_swe_colon_fem_1y, function(p) quantile(p, probs = c(0.025,0.975,0.5)))

dede_den_colon_mal_1y<-(slope_den_colon_mal_1y[,-1] - slope_den_colon_mal_1y[,-ncol(slope_den_colon_mal_1y)])
dede_den_colon_mal_1y<-data.frame(dede_den_colon_mal_1y)
dede_den_colon_fem_1y<-(slope_den_colon_fem_1y[,-1] - slope_den_colon_fem_1y[,-ncol(slope_den_colon_fem_1y)])
dede_den_colon_fem_1y<-data.frame(dede_den_colon_fem_1y)

dede_fin_colon_mal_1y<-(slope_fin_colon_mal_1y[,-1] - slope_fin_colon_mal_1y[,-ncol(slope_fin_colon_mal_1y)])
dede_fin_colon_mal_1y<-data.frame(dede_fin_colon_mal_1y)
dede_fin_colon_fem_1y<-(slope_fin_colon_fem_1y[,-1] - slope_fin_colon_fem_1y[,-ncol(slope_fin_colon_fem_1y)])
dede_fin_colon_fem_1y<-data.frame(dede_fin_colon_fem_1y)

dede_nor_colon_mal_1y<-(slope_nor_colon_mal_1y[,-1] - slope_nor_colon_mal_1y[,-ncol(slope_nor_colon_mal_1y)])
dede_nor_colon_mal_1y<-data.frame(dede_nor_colon_mal_1y)
dede_nor_colon_fem_1y<-(slope_nor_colon_fem_1y[,-1] - slope_nor_colon_fem_1y[,-ncol(slope_nor_colon_fem_1y)])
dede_nor_colon_fem_1y<-data.frame(dede_nor_colon_fem_1y)

dede_swe_colon_mal_1y<-(slope_swe_colon_mal_1y[,-1] - slope_swe_colon_mal_1y[,-ncol(slope_swe_colon_mal_1y)])
dede_swe_colon_mal_1y<-data.frame(dede_swe_colon_mal_1y)
dede_swe_colon_fem_1y<-(slope_swe_colon_fem_1y[,-1] - slope_swe_colon_fem_1y[,-ncol(slope_swe_colon_fem_1y)])
dede_swe_colon_fem_1y<-data.frame(dede_swe_colon_fem_1y)

post_colon_den_mal_1y<-data.frame(post_colon_den_mal_1y)
cis2_colon_den_mal_1y<-sapply(post_colon_den_mal_1y, function(p) quantile(p, probs = c(0.025,0.975,0.5)))
cis2_colon_den_mal_1y<-c(cis2_colon_den_mal_1y[1,],rev(cis2_colon_den_mal_1y[2,]))

post_colon_fin_mal_1y<-data.frame(post_colon_fin_mal_1y)
cis2_colon_fin_mal_1y<-sapply(post_colon_fin_mal_1y, function(p) quantile(p, probs = c(0.025,0.975,0.5)))
cis2_colon_fin_mal_1y<-c(cis2_colon_fin_mal_1y[1,],rev(cis2_colon_fin_mal_1y[2,]))

post_colon_nor_mal_1y<-data.frame(post_colon_nor_mal_1y)
cis2_colon_nor_mal_1y<-sapply(post_colon_nor_mal_1y, function(p) quantile(p, probs = c(0.025,0.975,0.5)))
cis2_colon_nor_mal_1y<-c(cis2_colon_nor_mal_1y[1,],rev(cis2_colon_nor_mal_1y[2,]))

post_colon_swe_mal_1y<-data.frame(post_colon_swe_mal_1y)
cis2_colon_swe_mal_1y<-sapply(post_colon_swe_mal_1y, function(p) quantile(p, probs = c(0.025,0.975,0.5)))
cis2_colon_swe_mal_1y<-c(cis2_colon_swe_mal_1y[1,],rev(cis2_colon_swe_mal_1y[2,]))

post_colon_den_fem_1y<-data.frame(post_colon_den_fem_1y)
cis2_colon_den_fem_1y<-sapply(post_colon_den_fem_1y, function(p) quantile(p, probs = c(0.025,0.975,0.5)))
cis2_colon_den_fem_1y<-c(cis2_colon_den_fem_1y[1,],rev(cis2_colon_den_fem_1y[2,]))

post_colon_fin_fem_1y<-data.frame(post_colon_fin_fem_1y)
cis2_colon_fin_fem_1y<-sapply(post_colon_fin_fem_1y, function(p) quantile(p, probs = c(0.025,0.975,0.5)))
cis2_colon_fin_fem_1y<-c(cis2_colon_fin_fem_1y[1,],rev(cis2_colon_fin_fem_1y[2,]))

post_colon_nor_fem_1y<-data.frame(post_colon_nor_fem_1y)
cis2_colon_nor_fem_1y<-sapply(post_colon_nor_fem_1y, function(p) quantile(p, probs = c(0.025,0.975,0.5)))
cis2_colon_nor_fem_1y<-c(cis2_colon_nor_fem_1y[1,],rev(cis2_colon_nor_fem_1y[2,]))

post_colon_swe_fem_1y<-data.frame(post_colon_swe_fem_1y)
cis2_colon_swe_fem_1y<-sapply(post_colon_swe_fem_1y, function(p) quantile(p, probs = c(0.025,0.975,0.5)))
cis2_colon_swe_fem_1y<-c(cis2_colon_swe_fem_1y[1,],rev(cis2_colon_swe_fem_1y[2,]))

cis3_den_colon_mal_1y<-sapply(dede_den_colon_mal_1y, function(p) quantile(p, probs = c(0.025,0.975,0.5)))
cis3_den_colon_fem_1y<-sapply(dede_den_colon_fem_1y, function(p) quantile(p, probs = c(0.025,0.975,0.5)))
cis3_fin_colon_mal_1y<-sapply(dede_fin_colon_mal_1y, function(p) quantile(p, probs = c(0.025,0.975,0.5)))
cis3_fin_colon_fem_1y<-sapply(dede_fin_colon_fem_1y, function(p) quantile(p, probs = c(0.025,0.975,0.5)))
cis3_nor_colon_mal_1y<-sapply(dede_nor_colon_mal_1y, function(p) quantile(p, probs = c(0.025,0.975,0.5)))
cis3_nor_colon_fem_1y<-sapply(dede_nor_colon_fem_1y, function(p) quantile(p, probs = c(0.025,0.975,0.5)))
cis3_swe_colon_mal_1y<-sapply(dede_swe_colon_mal_1y, function(p) quantile(p, probs = c(0.025,0.975,0.5)))
cis3_swe_colon_fem_1y<-sapply(dede_swe_colon_fem_1y, function(p) quantile(p, probs = c(0.025,0.975,0.5)))


### 5y ----------------------------------------------------------------------

slope_den_colon_mal_5y<-(post_colon_den_mal_5y[,-1] - post_colon_den_mal_5y[,-ncol(post_colon_den_mal_5y)])*10
slope_den_colon_mal_5y<-data.frame(slope_den_colon_mal_5y)
slope_den_colon_fem_5y<-(post_colon_den_fem_5y[,-1] - post_colon_den_fem_5y[,-ncol(post_colon_den_fem_5y)])*10
slope_den_colon_fem_5y<-data.frame(slope_den_colon_fem_5y)

slope_fin_colon_mal_5y<-(post_colon_fin_mal_5y[,-1] - post_colon_fin_mal_5y[,-ncol(post_colon_fin_mal_5y)])*10
slope_fin_colon_mal_5y<-data.frame(slope_fin_colon_mal_5y)
slope_fin_colon_fem_5y<-(post_colon_fin_fem_5y[,-1] - post_colon_fin_fem_5y[,-ncol(post_colon_fin_fem_5y)])*10
slope_fin_colon_fem_5y<-data.frame(slope_fin_colon_fem_5y)

slope_nor_colon_mal_5y<-(post_colon_nor_mal_5y[,-1] - post_colon_nor_mal_5y[,-ncol(post_colon_nor_mal_5y)])*10
slope_nor_colon_mal_5y<-data.frame(slope_nor_colon_mal_5y)
slope_nor_colon_fem_5y<-(post_colon_nor_fem_5y[,-1] - post_colon_nor_fem_5y[,-ncol(post_colon_nor_fem_5y)])*10
slope_nor_colon_fem_5y<-data.frame(slope_nor_colon_fem_5y)

slope_swe_colon_mal_5y<-(post_colon_swe_mal_5y[,-1] - post_colon_swe_mal_5y[,-ncol(post_colon_swe_mal_5y)])*10
slope_swe_colon_mal_5y<-data.frame(slope_swe_colon_mal_5y)
slope_swe_colon_fem_5y<-(post_colon_swe_fem_5y[,-1] - post_colon_swe_fem_5y[,-ncol(post_colon_swe_fem_5y)])*10
slope_swe_colon_fem_5y<-data.frame(slope_swe_colon_fem_5y)

cis_den_colon_mal_5y<-sapply(slope_den_colon_mal_5y, function(p) quantile(p, probs = c(0.025,0.975,0.5)))
cis_den_colon_fem_5y<-sapply(slope_den_colon_fem_5y, function(p) quantile(p, probs = c(0.025,0.975,0.5)))
cis_fin_colon_mal_5y<-sapply(slope_fin_colon_mal_5y, function(p) quantile(p, probs = c(0.025,0.975,0.5)))
cis_fin_colon_fem_5y<-sapply(slope_fin_colon_fem_5y, function(p) quantile(p, probs = c(0.025,0.975,0.5)))
cis_nor_colon_mal_5y<-sapply(slope_nor_colon_mal_5y, function(p) quantile(p, probs = c(0.025,0.975,0.5)))
cis_nor_colon_fem_5y<-sapply(slope_nor_colon_fem_5y, function(p) quantile(p, probs = c(0.025,0.975,0.5)))
cis_swe_colon_mal_5y<-sapply(slope_swe_colon_mal_5y, function(p) quantile(p, probs = c(0.025,0.975,0.5)))
cis_swe_colon_fem_5y<-sapply(slope_swe_colon_fem_5y, function(p) quantile(p, probs = c(0.025,0.975,0.5)))

dede_den_colon_mal_5y<-(slope_den_colon_mal_5y[,-1] - slope_den_colon_mal_5y[,-ncol(slope_den_colon_mal_5y)])
dede_den_colon_mal_5y<-data.frame(dede_den_colon_mal_5y)
dede_den_colon_fem_5y<-(slope_den_colon_fem_5y[,-1] - slope_den_colon_fem_5y[,-ncol(slope_den_colon_fem_5y)])
dede_den_colon_fem_5y<-data.frame(dede_den_colon_fem_5y)

dede_fin_colon_mal_5y<-(slope_fin_colon_mal_5y[,-1] - slope_fin_colon_mal_5y[,-ncol(slope_fin_colon_mal_5y)])
dede_fin_colon_mal_5y<-data.frame(dede_fin_colon_mal_5y)
dede_fin_colon_fem_5y<-(slope_fin_colon_fem_5y[,-1] - slope_fin_colon_fem_5y[,-ncol(slope_fin_colon_fem_5y)])
dede_fin_colon_fem_5y<-data.frame(dede_fin_colon_fem_5y)

dede_nor_colon_mal_5y<-(slope_nor_colon_mal_5y[,-1] - slope_nor_colon_mal_5y[,-ncol(slope_nor_colon_mal_5y)])
dede_nor_colon_mal_5y<-data.frame(dede_nor_colon_mal_5y)
dede_nor_colon_fem_5y<-(slope_nor_colon_fem_5y[,-1] - slope_nor_colon_fem_5y[,-ncol(slope_nor_colon_fem_5y)])
dede_nor_colon_fem_5y<-data.frame(dede_nor_colon_fem_5y)

dede_swe_colon_mal_5y<-(slope_swe_colon_mal_5y[,-1] - slope_swe_colon_mal_5y[,-ncol(slope_swe_colon_mal_5y)])
dede_swe_colon_mal_5y<-data.frame(dede_swe_colon_mal_5y)
dede_swe_colon_fem_5y<-(slope_swe_colon_fem_5y[,-1] - slope_swe_colon_fem_5y[,-ncol(slope_swe_colon_fem_5y)])
dede_swe_colon_fem_5y<-data.frame(dede_swe_colon_fem_5y)

post_colon_den_mal_5y<-data.frame(post_colon_den_mal_5y)
cis2_colon_den_mal_5y<-sapply(post_colon_den_mal_5y, function(p) quantile(p, probs = c(0.025,0.975,0.5)))
cis2_colon_den_mal_5y<-c(cis2_colon_den_mal_5y[1,],rev(cis2_colon_den_mal_5y[2,]))

post_colon_fin_mal_5y<-data.frame(post_colon_fin_mal_5y)
cis2_colon_fin_mal_5y<-sapply(post_colon_fin_mal_5y, function(p) quantile(p, probs = c(0.025,0.975,0.5)))
cis2_colon_fin_mal_5y<-c(cis2_colon_fin_mal_5y[1,],rev(cis2_colon_fin_mal_5y[2,]))

post_colon_nor_mal_5y<-data.frame(post_colon_nor_mal_5y)
cis2_colon_nor_mal_5y<-sapply(post_colon_nor_mal_5y, function(p) quantile(p, probs = c(0.025,0.975,0.5)))
cis2_colon_nor_mal_5y<-c(cis2_colon_nor_mal_5y[1,],rev(cis2_colon_nor_mal_5y[2,]))

post_colon_swe_mal_5y<-data.frame(post_colon_swe_mal_5y)
cis2_colon_swe_mal_5y<-sapply(post_colon_swe_mal_5y, function(p) quantile(p, probs = c(0.025,0.975,0.5)))
cis2_colon_swe_mal_5y<-c(cis2_colon_swe_mal_5y[1,],rev(cis2_colon_swe_mal_5y[2,]))

post_colon_den_fem_5y<-data.frame(post_colon_den_fem_5y)
cis2_colon_den_fem_5y<-sapply(post_colon_den_fem_5y, function(p) quantile(p, probs = c(0.025,0.975,0.5)))
cis2_colon_den_fem_5y<-c(cis2_colon_den_fem_5y[1,],rev(cis2_colon_den_fem_5y[2,]))

post_colon_fin_fem_5y<-data.frame(post_colon_fin_fem_5y)
cis2_colon_fin_fem_5y<-sapply(post_colon_fin_fem_5y, function(p) quantile(p, probs = c(0.025,0.975,0.5)))
cis2_colon_fin_fem_5y<-c(cis2_colon_fin_fem_5y[1,],rev(cis2_colon_fin_fem_5y[2,]))

post_colon_nor_fem_5y<-data.frame(post_colon_nor_fem_5y)
cis2_colon_nor_fem_5y<-sapply(post_colon_nor_fem_5y, function(p) quantile(p, probs = c(0.025,0.975,0.5)))
cis2_colon_nor_fem_5y<-c(cis2_colon_nor_fem_5y[1,],rev(cis2_colon_nor_fem_5y[2,]))

post_colon_swe_fem_5y<-data.frame(post_colon_swe_fem_5y)
cis2_colon_swe_fem_5y<-sapply(post_colon_swe_fem_5y, function(p) quantile(p, probs = c(0.025,0.975,0.5)))
cis2_colon_swe_fem_5y<-c(cis2_colon_swe_fem_5y[1,],rev(cis2_colon_swe_fem_5y[2,]))

cis3_den_colon_mal_5y<-sapply(dede_den_colon_mal_5y, function(p) quantile(p, probs = c(0.025,0.975,0.5)))
cis3_den_colon_fem_5y<-sapply(dede_den_colon_fem_5y, function(p) quantile(p, probs = c(0.025,0.975,0.5)))
cis3_fin_colon_mal_5y<-sapply(dede_fin_colon_mal_5y, function(p) quantile(p, probs = c(0.025,0.975,0.5)))
cis3_fin_colon_fem_5y<-sapply(dede_fin_colon_fem_5y, function(p) quantile(p, probs = c(0.025,0.975,0.5)))
cis3_nor_colon_mal_5y<-sapply(dede_nor_colon_mal_5y, function(p) quantile(p, probs = c(0.025,0.975,0.5)))
cis3_nor_colon_fem_5y<-sapply(dede_nor_colon_fem_5y, function(p) quantile(p, probs = c(0.025,0.975,0.5)))
cis3_swe_colon_mal_5y<-sapply(dede_swe_colon_mal_5y, function(p) quantile(p, probs = c(0.025,0.975,0.5)))
cis3_swe_colon_fem_5y<-sapply(dede_swe_colon_fem_5y, function(p) quantile(p, probs = c(0.025,0.975,0.5)))


### cond --------------------------------------------------------------------
slope_den_colon_mal_cond<-(post_colon_den_mal_cond[,-1] - post_colon_den_mal_cond[,-ncol(post_colon_den_mal_cond)])*10
slope_den_colon_mal_cond<-data.frame(slope_den_colon_mal_cond)
slope_den_colon_fem_cond<-(post_colon_den_fem_cond[,-1] - post_colon_den_fem_cond[,-ncol(post_colon_den_fem_cond)])*10
slope_den_colon_fem_cond<-data.frame(slope_den_colon_fem_cond)

slope_fin_colon_mal_cond<-(post_colon_fin_mal_cond[,-1] - post_colon_fin_mal_cond[,-ncol(post_colon_fin_mal_cond)])*10
slope_fin_colon_mal_cond<-data.frame(slope_fin_colon_mal_cond)
slope_fin_colon_fem_cond<-(post_colon_fin_fem_cond[,-1] - post_colon_fin_fem_cond[,-ncol(post_colon_fin_fem_cond)])*10
slope_fin_colon_fem_cond<-data.frame(slope_fin_colon_fem_cond)

slope_nor_colon_mal_cond<-(post_colon_nor_mal_cond[,-1] - post_colon_nor_mal_cond[,-ncol(post_colon_nor_mal_cond)])*10
slope_nor_colon_mal_cond<-data.frame(slope_nor_colon_mal_cond)
slope_nor_colon_fem_cond<-(post_colon_nor_fem_cond[,-1] - post_colon_nor_fem_cond[,-ncol(post_colon_nor_fem_cond)])*10
slope_nor_colon_fem_cond<-data.frame(slope_nor_colon_fem_cond)

slope_swe_colon_mal_cond<-(post_colon_swe_mal_cond[,-1] - post_colon_swe_mal_cond[,-ncol(post_colon_swe_mal_cond)])*10
slope_swe_colon_mal_cond<-data.frame(slope_swe_colon_mal_cond)
slope_swe_colon_fem_cond<-(post_colon_swe_fem_cond[,-1] - post_colon_swe_fem_cond[,-ncol(post_colon_swe_fem_cond)])*10
slope_swe_colon_fem_cond<-data.frame(slope_swe_colon_fem_cond)

cis_den_colon_mal_cond<-sapply(slope_den_colon_mal_cond, function(p) quantile(p, probs = c(0.025,0.975,0.5)))
cis_den_colon_fem_cond<-sapply(slope_den_colon_fem_cond, function(p) quantile(p, probs = c(0.025,0.975,0.5)))
cis_fin_colon_mal_cond<-sapply(slope_fin_colon_mal_cond, function(p) quantile(p, probs = c(0.025,0.975,0.5)))
cis_fin_colon_fem_cond<-sapply(slope_fin_colon_fem_cond, function(p) quantile(p, probs = c(0.025,0.975,0.5)))
cis_nor_colon_mal_cond<-sapply(slope_nor_colon_mal_cond, function(p) quantile(p, probs = c(0.025,0.975,0.5)))
cis_nor_colon_fem_cond<-sapply(slope_nor_colon_fem_cond, function(p) quantile(p, probs = c(0.025,0.975,0.5)))
cis_swe_colon_mal_cond<-sapply(slope_swe_colon_mal_cond, function(p) quantile(p, probs = c(0.025,0.975,0.5)))
cis_swe_colon_fem_cond<-sapply(slope_swe_colon_fem_cond, function(p) quantile(p, probs = c(0.025,0.975,0.5)))

dede_den_colon_mal_cond<-(slope_den_colon_mal_cond[,-1] - slope_den_colon_mal_cond[,-ncol(slope_den_colon_mal_cond)])
dede_den_colon_mal_cond<-data.frame(dede_den_colon_mal_cond)
dede_den_colon_fem_cond<-(slope_den_colon_fem_cond[,-1] - slope_den_colon_fem_cond[,-ncol(slope_den_colon_fem_cond)])
dede_den_colon_fem_cond<-data.frame(dede_den_colon_fem_cond)

dede_fin_colon_mal_cond<-(slope_fin_colon_mal_cond[,-1] - slope_fin_colon_mal_cond[,-ncol(slope_fin_colon_mal_cond)])
dede_fin_colon_mal_cond<-data.frame(dede_fin_colon_mal_cond)
dede_fin_colon_fem_cond<-(slope_fin_colon_fem_cond[,-1] - slope_fin_colon_fem_cond[,-ncol(slope_fin_colon_fem_cond)])
dede_fin_colon_fem_cond<-data.frame(dede_fin_colon_fem_cond)

dede_nor_colon_mal_cond<-(slope_nor_colon_mal_cond[,-1] - slope_nor_colon_mal_cond[,-ncol(slope_nor_colon_mal_cond)])
dede_nor_colon_mal_cond<-data.frame(dede_nor_colon_mal_cond)
dede_nor_colon_fem_cond<-(slope_nor_colon_fem_cond[,-1] - slope_nor_colon_fem_cond[,-ncol(slope_nor_colon_fem_cond)])
dede_nor_colon_fem_cond<-data.frame(dede_nor_colon_fem_cond)

dede_swe_colon_mal_cond<-(slope_swe_colon_mal_cond[,-1] - slope_swe_colon_mal_cond[,-ncol(slope_swe_colon_mal_cond)])
dede_swe_colon_mal_cond<-data.frame(dede_swe_colon_mal_cond)
dede_swe_colon_fem_cond<-(slope_swe_colon_fem_cond[,-1] - slope_swe_colon_fem_cond[,-ncol(slope_swe_colon_fem_cond)])
dede_swe_colon_fem_cond<-data.frame(dede_swe_colon_fem_cond)

post_colon_den_mal_cond<-data.frame(post_colon_den_mal_cond)
cis2_colon_den_mal_cond<-sapply(post_colon_den_mal_cond, function(p) quantile(p, probs = c(0.025,0.975,0.5)))
cis2_colon_den_mal_cond<-c(cis2_colon_den_mal_cond[1,],rev(cis2_colon_den_mal_cond[2,]))

post_colon_fin_mal_cond<-data.frame(post_colon_fin_mal_cond)
cis2_colon_fin_mal_cond<-sapply(post_colon_fin_mal_cond, function(p) quantile(p, probs = c(0.025,0.975,0.5)))
cis2_colon_fin_mal_cond<-c(cis2_colon_fin_mal_cond[1,],rev(cis2_colon_fin_mal_cond[2,]))

post_colon_nor_mal_cond<-data.frame(post_colon_nor_mal_cond)
cis2_colon_nor_mal_cond<-sapply(post_colon_nor_mal_cond, function(p) quantile(p, probs = c(0.025,0.975,0.5)))
cis2_colon_nor_mal_cond<-c(cis2_colon_nor_mal_cond[1,],rev(cis2_colon_nor_mal_cond[2,]))

post_colon_swe_mal_cond<-data.frame(post_colon_swe_mal_cond)
cis2_colon_swe_mal_cond<-sapply(post_colon_swe_mal_cond, function(p) quantile(p, probs = c(0.025,0.975,0.5)))
cis2_colon_swe_mal_cond<-c(cis2_colon_swe_mal_cond[1,],rev(cis2_colon_swe_mal_cond[2,]))

post_colon_den_fem_cond<-data.frame(post_colon_den_fem_cond)
cis2_colon_den_fem_cond<-sapply(post_colon_den_fem_cond, function(p) quantile(p, probs = c(0.025,0.975,0.5)))
cis2_colon_den_fem_cond<-c(cis2_colon_den_fem_cond[1,],rev(cis2_colon_den_fem_cond[2,]))

post_colon_fin_fem_cond<-data.frame(post_colon_fin_fem_cond)
cis2_colon_fin_fem_cond<-sapply(post_colon_fin_fem_cond, function(p) quantile(p, probs = c(0.025,0.975,0.5)))
cis2_colon_fin_fem_cond<-c(cis2_colon_fin_fem_cond[1,],rev(cis2_colon_fin_fem_cond[2,]))

post_colon_nor_fem_cond<-data.frame(post_colon_nor_fem_cond)
cis2_colon_nor_fem_cond<-sapply(post_colon_nor_fem_cond, function(p) quantile(p, probs = c(0.025,0.975,0.5)))
cis2_colon_nor_fem_cond<-c(cis2_colon_nor_fem_cond[1,],rev(cis2_colon_nor_fem_cond[2,]))

post_colon_swe_fem_cond<-data.frame(post_colon_swe_fem_cond)
cis2_colon_swe_fem_cond<-sapply(post_colon_swe_fem_cond, function(p) quantile(p, probs = c(0.025,0.975,0.5)))
cis2_colon_swe_fem_cond<-c(cis2_colon_swe_fem_cond[1,],rev(cis2_colon_swe_fem_cond[2,]))

cis3_den_colon_mal_cond<-sapply(dede_den_colon_mal_cond, function(p) quantile(p, probs = c(0.025,0.975,0.5)))
cis3_den_colon_fem_cond<-sapply(dede_den_colon_fem_cond, function(p) quantile(p, probs = c(0.025,0.975,0.5)))
cis3_fin_colon_mal_cond<-sapply(dede_fin_colon_mal_cond, function(p) quantile(p, probs = c(0.025,0.975,0.5)))
cis3_fin_colon_fem_cond<-sapply(dede_fin_colon_fem_cond, function(p) quantile(p, probs = c(0.025,0.975,0.5)))
cis3_nor_colon_mal_cond<-sapply(dede_nor_colon_mal_cond, function(p) quantile(p, probs = c(0.025,0.975,0.5)))
cis3_nor_colon_fem_cond<-sapply(dede_nor_colon_fem_cond, function(p) quantile(p, probs = c(0.025,0.975,0.5)))
cis3_swe_colon_mal_cond<-sapply(dede_swe_colon_mal_cond, function(p) quantile(p, probs = c(0.025,0.975,0.5)))
cis3_swe_colon_fem_cond<-sapply(dede_swe_colon_fem_cond, function(p) quantile(p, probs = c(0.025,0.975,0.5)))




## rectum cancer ------------------------------------------------------------

### 1y ----------------------------------------------------------------------
slope_den_rectum_mal_1y<-(post_rectum_den_mal_1y[,-1] - post_rectum_den_mal_1y[,-ncol(post_rectum_den_mal_1y)])*10
slope_den_rectum_mal_1y<-data.frame(slope_den_rectum_mal_1y)
slope_den_rectum_fem_1y<-(post_rectum_den_fem_1y[,-1] - post_rectum_den_fem_1y[,-ncol(post_rectum_den_fem_1y)])*10
slope_den_rectum_fem_1y<-data.frame(slope_den_rectum_fem_1y)

slope_fin_rectum_mal_1y<-(post_rectum_fin_mal_1y[,-1] - post_rectum_fin_mal_1y[,-ncol(post_rectum_fin_mal_1y)])*10
slope_fin_rectum_mal_1y<-data.frame(slope_fin_rectum_mal_1y)
slope_fin_rectum_fem_1y<-(post_rectum_fin_fem_1y[,-1] - post_rectum_fin_fem_1y[,-ncol(post_rectum_fin_fem_1y)])*10
slope_fin_rectum_fem_1y<-data.frame(slope_fin_rectum_fem_1y)

slope_nor_rectum_mal_1y<-(post_rectum_nor_mal_1y[,-1] - post_rectum_nor_mal_1y[,-ncol(post_rectum_nor_mal_1y)])*10
slope_nor_rectum_mal_1y<-data.frame(slope_nor_rectum_mal_1y)
slope_nor_rectum_fem_1y<-(post_rectum_nor_fem_1y[,-1] - post_rectum_nor_fem_1y[,-ncol(post_rectum_nor_fem_1y)])*10
slope_nor_rectum_fem_1y<-data.frame(slope_nor_rectum_fem_1y)

slope_swe_rectum_mal_1y<-(post_rectum_swe_mal_1y[,-1] - post_rectum_swe_mal_1y[,-ncol(post_rectum_swe_mal_1y)])*10
slope_swe_rectum_mal_1y<-data.frame(slope_swe_rectum_mal_1y)
slope_swe_rectum_fem_1y<-(post_rectum_swe_fem_1y[,-1] - post_rectum_swe_fem_1y[,-ncol(post_rectum_swe_fem_1y)])*10
slope_swe_rectum_fem_1y<-data.frame(slope_swe_rectum_fem_1y)

cis_den_rectum_mal_1y<-sapply(slope_den_rectum_mal_1y, function(p) quantile(p, probs = c(0.025,0.975,0.5)))
cis_den_rectum_fem_1y<-sapply(slope_den_rectum_fem_1y, function(p) quantile(p, probs = c(0.025,0.975,0.5)))
cis_fin_rectum_mal_1y<-sapply(slope_fin_rectum_mal_1y, function(p) quantile(p, probs = c(0.025,0.975,0.5)))
cis_fin_rectum_fem_1y<-sapply(slope_fin_rectum_fem_1y, function(p) quantile(p, probs = c(0.025,0.975,0.5)))
cis_nor_rectum_mal_1y<-sapply(slope_nor_rectum_mal_1y, function(p) quantile(p, probs = c(0.025,0.975,0.5)))
cis_nor_rectum_fem_1y<-sapply(slope_nor_rectum_fem_1y, function(p) quantile(p, probs = c(0.025,0.975,0.5)))
cis_swe_rectum_mal_1y<-sapply(slope_swe_rectum_mal_1y, function(p) quantile(p, probs = c(0.025,0.975,0.5)))
cis_swe_rectum_fem_1y<-sapply(slope_swe_rectum_fem_1y, function(p) quantile(p, probs = c(0.025,0.975,0.5)))

dede_den_rectum_mal_1y<-(slope_den_rectum_mal_1y[,-1] - slope_den_rectum_mal_1y[,-ncol(slope_den_rectum_mal_1y)])
dede_den_rectum_mal_1y<-data.frame(dede_den_rectum_mal_1y)
dede_den_rectum_fem_1y<-(slope_den_rectum_fem_1y[,-1] - slope_den_rectum_fem_1y[,-ncol(slope_den_rectum_fem_1y)])
dede_den_rectum_fem_1y<-data.frame(dede_den_rectum_fem_1y)

dede_fin_rectum_mal_1y<-(slope_fin_rectum_mal_1y[,-1] - slope_fin_rectum_mal_1y[,-ncol(slope_fin_rectum_mal_1y)])
dede_fin_rectum_mal_1y<-data.frame(dede_fin_rectum_mal_1y)
dede_fin_rectum_fem_1y<-(slope_fin_rectum_fem_1y[,-1] - slope_fin_rectum_fem_1y[,-ncol(slope_fin_rectum_fem_1y)])
dede_fin_rectum_fem_1y<-data.frame(dede_fin_rectum_fem_1y)

dede_nor_rectum_mal_1y<-(slope_nor_rectum_mal_1y[,-1] - slope_nor_rectum_mal_1y[,-ncol(slope_nor_rectum_mal_1y)])
dede_nor_rectum_mal_1y<-data.frame(dede_nor_rectum_mal_1y)
dede_nor_rectum_fem_1y<-(slope_nor_rectum_fem_1y[,-1] - slope_nor_rectum_fem_1y[,-ncol(slope_nor_rectum_fem_1y)])
dede_nor_rectum_fem_1y<-data.frame(dede_nor_rectum_fem_1y)

dede_swe_rectum_mal_1y<-(slope_swe_rectum_mal_1y[,-1] - slope_swe_rectum_mal_1y[,-ncol(slope_swe_rectum_mal_1y)])
dede_swe_rectum_mal_1y<-data.frame(dede_swe_rectum_mal_1y)
dede_swe_rectum_fem_1y<-(slope_swe_rectum_fem_1y[,-1] - slope_swe_rectum_fem_1y[,-ncol(slope_swe_rectum_fem_1y)])
dede_swe_rectum_fem_1y<-data.frame(dede_swe_rectum_fem_1y)

post_rectum_den_mal_1y<-data.frame(post_rectum_den_mal_1y)
cis2_rectum_den_mal_1y<-sapply(post_rectum_den_mal_1y, function(p) quantile(p, probs = c(0.025,0.975,0.5)))
cis2_rectum_den_mal_1y<-c(cis2_rectum_den_mal_1y[1,],rev(cis2_rectum_den_mal_1y[2,]))

post_rectum_fin_mal_1y<-data.frame(post_rectum_fin_mal_1y)
cis2_rectum_fin_mal_1y<-sapply(post_rectum_fin_mal_1y, function(p) quantile(p, probs = c(0.025,0.975,0.5)))
cis2_rectum_fin_mal_1y<-c(cis2_rectum_fin_mal_1y[1,],rev(cis2_rectum_fin_mal_1y[2,]))

post_rectum_nor_mal_1y<-data.frame(post_rectum_nor_mal_1y)
cis2_rectum_nor_mal_1y<-sapply(post_rectum_nor_mal_1y, function(p) quantile(p, probs = c(0.025,0.975,0.5)))
cis2_rectum_nor_mal_1y<-c(cis2_rectum_nor_mal_1y[1,],rev(cis2_rectum_nor_mal_1y[2,]))

post_rectum_swe_mal_1y<-data.frame(post_rectum_swe_mal_1y)
cis2_rectum_swe_mal_1y<-sapply(post_rectum_swe_mal_1y, function(p) quantile(p, probs = c(0.025,0.975,0.5)))
cis2_rectum_swe_mal_1y<-c(cis2_rectum_swe_mal_1y[1,],rev(cis2_rectum_swe_mal_1y[2,]))

post_rectum_den_fem_1y<-data.frame(post_rectum_den_fem_1y)
cis2_rectum_den_fem_1y<-sapply(post_rectum_den_fem_1y, function(p) quantile(p, probs = c(0.025,0.975,0.5)))
cis2_rectum_den_fem_1y<-c(cis2_rectum_den_fem_1y[1,],rev(cis2_rectum_den_fem_1y[2,]))

post_rectum_fin_fem_1y<-data.frame(post_rectum_fin_fem_1y)
cis2_rectum_fin_fem_1y<-sapply(post_rectum_fin_fem_1y, function(p) quantile(p, probs = c(0.025,0.975,0.5)))
cis2_rectum_fin_fem_1y<-c(cis2_rectum_fin_fem_1y[1,],rev(cis2_rectum_fin_fem_1y[2,]))

post_rectum_nor_fem_1y<-data.frame(post_rectum_nor_fem_1y)
cis2_rectum_nor_fem_1y<-sapply(post_rectum_nor_fem_1y, function(p) quantile(p, probs = c(0.025,0.975,0.5)))
cis2_rectum_nor_fem_1y<-c(cis2_rectum_nor_fem_1y[1,],rev(cis2_rectum_nor_fem_1y[2,]))

post_rectum_swe_fem_1y<-data.frame(post_rectum_swe_fem_1y)
cis2_rectum_swe_fem_1y<-sapply(post_rectum_swe_fem_1y, function(p) quantile(p, probs = c(0.025,0.975,0.5)))
cis2_rectum_swe_fem_1y<-c(cis2_rectum_swe_fem_1y[1,],rev(cis2_rectum_swe_fem_1y[2,]))

cis3_den_rectum_mal_1y<-sapply(dede_den_rectum_mal_1y, function(p) quantile(p, probs = c(0.025,0.975,0.5)))
cis3_den_rectum_fem_1y<-sapply(dede_den_rectum_fem_1y, function(p) quantile(p, probs = c(0.025,0.975,0.5)))
cis3_fin_rectum_mal_1y<-sapply(dede_fin_rectum_mal_1y, function(p) quantile(p, probs = c(0.025,0.975,0.5)))
cis3_fin_rectum_fem_1y<-sapply(dede_fin_rectum_fem_1y, function(p) quantile(p, probs = c(0.025,0.975,0.5)))
cis3_nor_rectum_mal_1y<-sapply(dede_nor_rectum_mal_1y, function(p) quantile(p, probs = c(0.025,0.975,0.5)))
cis3_nor_rectum_fem_1y<-sapply(dede_nor_rectum_fem_1y, function(p) quantile(p, probs = c(0.025,0.975,0.5)))
cis3_swe_rectum_mal_1y<-sapply(dede_swe_rectum_mal_1y, function(p) quantile(p, probs = c(0.025,0.975,0.5)))
cis3_swe_rectum_fem_1y<-sapply(dede_swe_rectum_fem_1y, function(p) quantile(p, probs = c(0.025,0.975,0.5)))


### 5y ----------------------------------------------------------------------

slope_den_rectum_mal_5y<-(post_rectum_den_mal_5y[,-1] - post_rectum_den_mal_5y[,-ncol(post_rectum_den_mal_5y)])*10
slope_den_rectum_mal_5y<-data.frame(slope_den_rectum_mal_5y)
slope_den_rectum_fem_5y<-(post_rectum_den_fem_5y[,-1] - post_rectum_den_fem_5y[,-ncol(post_rectum_den_fem_5y)])*10
slope_den_rectum_fem_5y<-data.frame(slope_den_rectum_fem_5y)

slope_fin_rectum_mal_5y<-(post_rectum_fin_mal_5y[,-1] - post_rectum_fin_mal_5y[,-ncol(post_rectum_fin_mal_5y)])*10
slope_fin_rectum_mal_5y<-data.frame(slope_fin_rectum_mal_5y)
slope_fin_rectum_fem_5y<-(post_rectum_fin_fem_5y[,-1] - post_rectum_fin_fem_5y[,-ncol(post_rectum_fin_fem_5y)])*10
slope_fin_rectum_fem_5y<-data.frame(slope_fin_rectum_fem_5y)

slope_nor_rectum_mal_5y<-(post_rectum_nor_mal_5y[,-1] - post_rectum_nor_mal_5y[,-ncol(post_rectum_nor_mal_5y)])*10
slope_nor_rectum_mal_5y<-data.frame(slope_nor_rectum_mal_5y)
slope_nor_rectum_fem_5y<-(post_rectum_nor_fem_5y[,-1] - post_rectum_nor_fem_5y[,-ncol(post_rectum_nor_fem_5y)])*10
slope_nor_rectum_fem_5y<-data.frame(slope_nor_rectum_fem_5y)

slope_swe_rectum_mal_5y<-(post_rectum_swe_mal_5y[,-1] - post_rectum_swe_mal_5y[,-ncol(post_rectum_swe_mal_5y)])*10
slope_swe_rectum_mal_5y<-data.frame(slope_swe_rectum_mal_5y)
slope_swe_rectum_fem_5y<-(post_rectum_swe_fem_5y[,-1] - post_rectum_swe_fem_5y[,-ncol(post_rectum_swe_fem_5y)])*10
slope_swe_rectum_fem_5y<-data.frame(slope_swe_rectum_fem_5y)

cis_den_rectum_mal_5y<-sapply(slope_den_rectum_mal_5y, function(p) quantile(p, probs = c(0.025,0.975,0.5)))
cis_den_rectum_fem_5y<-sapply(slope_den_rectum_fem_5y, function(p) quantile(p, probs = c(0.025,0.975,0.5)))
cis_fin_rectum_mal_5y<-sapply(slope_fin_rectum_mal_5y, function(p) quantile(p, probs = c(0.025,0.975,0.5)))
cis_fin_rectum_fem_5y<-sapply(slope_fin_rectum_fem_5y, function(p) quantile(p, probs = c(0.025,0.975,0.5)))
cis_nor_rectum_mal_5y<-sapply(slope_nor_rectum_mal_5y, function(p) quantile(p, probs = c(0.025,0.975,0.5)))
cis_nor_rectum_fem_5y<-sapply(slope_nor_rectum_fem_5y, function(p) quantile(p, probs = c(0.025,0.975,0.5)))
cis_swe_rectum_mal_5y<-sapply(slope_swe_rectum_mal_5y, function(p) quantile(p, probs = c(0.025,0.975,0.5)))
cis_swe_rectum_fem_5y<-sapply(slope_swe_rectum_fem_5y, function(p) quantile(p, probs = c(0.025,0.975,0.5)))

dede_den_rectum_mal_5y<-(slope_den_rectum_mal_5y[,-1] - slope_den_rectum_mal_5y[,-ncol(slope_den_rectum_mal_5y)])
dede_den_rectum_mal_5y<-data.frame(dede_den_rectum_mal_5y)
dede_den_rectum_fem_5y<-(slope_den_rectum_fem_5y[,-1] - slope_den_rectum_fem_5y[,-ncol(slope_den_rectum_fem_5y)])
dede_den_rectum_fem_5y<-data.frame(dede_den_rectum_fem_5y)

dede_fin_rectum_mal_5y<-(slope_fin_rectum_mal_5y[,-1] - slope_fin_rectum_mal_5y[,-ncol(slope_fin_rectum_mal_5y)])
dede_fin_rectum_mal_5y<-data.frame(dede_fin_rectum_mal_5y)
dede_fin_rectum_fem_5y<-(slope_fin_rectum_fem_5y[,-1] - slope_fin_rectum_fem_5y[,-ncol(slope_fin_rectum_fem_5y)])
dede_fin_rectum_fem_5y<-data.frame(dede_fin_rectum_fem_5y)

dede_nor_rectum_mal_5y<-(slope_nor_rectum_mal_5y[,-1] - slope_nor_rectum_mal_5y[,-ncol(slope_nor_rectum_mal_5y)])
dede_nor_rectum_mal_5y<-data.frame(dede_nor_rectum_mal_5y)
dede_nor_rectum_fem_5y<-(slope_nor_rectum_fem_5y[,-1] - slope_nor_rectum_fem_5y[,-ncol(slope_nor_rectum_fem_5y)])
dede_nor_rectum_fem_5y<-data.frame(dede_nor_rectum_fem_5y)

dede_swe_rectum_mal_5y<-(slope_swe_rectum_mal_5y[,-1] - slope_swe_rectum_mal_5y[,-ncol(slope_swe_rectum_mal_5y)])
dede_swe_rectum_mal_5y<-data.frame(dede_swe_rectum_mal_5y)
dede_swe_rectum_fem_5y<-(slope_swe_rectum_fem_5y[,-1] - slope_swe_rectum_fem_5y[,-ncol(slope_swe_rectum_fem_5y)])
dede_swe_rectum_fem_5y<-data.frame(dede_swe_rectum_fem_5y)

post_rectum_den_mal_5y<-data.frame(post_rectum_den_mal_5y)
cis2_rectum_den_mal_5y<-sapply(post_rectum_den_mal_5y, function(p) quantile(p, probs = c(0.025,0.975,0.5)))
cis2_rectum_den_mal_5y<-c(cis2_rectum_den_mal_5y[1,],rev(cis2_rectum_den_mal_5y[2,]))

post_rectum_fin_mal_5y<-data.frame(post_rectum_fin_mal_5y)
cis2_rectum_fin_mal_5y<-sapply(post_rectum_fin_mal_5y, function(p) quantile(p, probs = c(0.025,0.975,0.5)))
cis2_rectum_fin_mal_5y<-c(cis2_rectum_fin_mal_5y[1,],rev(cis2_rectum_fin_mal_5y[2,]))

post_rectum_nor_mal_5y<-data.frame(post_rectum_nor_mal_5y)
cis2_rectum_nor_mal_5y<-sapply(post_rectum_nor_mal_5y, function(p) quantile(p, probs = c(0.025,0.975,0.5)))
cis2_rectum_nor_mal_5y<-c(cis2_rectum_nor_mal_5y[1,],rev(cis2_rectum_nor_mal_5y[2,]))

post_rectum_swe_mal_5y<-data.frame(post_rectum_swe_mal_5y)
cis2_rectum_swe_mal_5y<-sapply(post_rectum_swe_mal_5y, function(p) quantile(p, probs = c(0.025,0.975,0.5)))
cis2_rectum_swe_mal_5y<-c(cis2_rectum_swe_mal_5y[1,],rev(cis2_rectum_swe_mal_5y[2,]))

post_rectum_den_fem_5y<-data.frame(post_rectum_den_fem_5y)
cis2_rectum_den_fem_5y<-sapply(post_rectum_den_fem_5y, function(p) quantile(p, probs = c(0.025,0.975,0.5)))
cis2_rectum_den_fem_5y<-c(cis2_rectum_den_fem_5y[1,],rev(cis2_rectum_den_fem_5y[2,]))

post_rectum_fin_fem_5y<-data.frame(post_rectum_fin_fem_5y)
cis2_rectum_fin_fem_5y<-sapply(post_rectum_fin_fem_5y, function(p) quantile(p, probs = c(0.025,0.975,0.5)))
cis2_rectum_fin_fem_5y<-c(cis2_rectum_fin_fem_5y[1,],rev(cis2_rectum_fin_fem_5y[2,]))

post_rectum_nor_fem_5y<-data.frame(post_rectum_nor_fem_5y)
cis2_rectum_nor_fem_5y<-sapply(post_rectum_nor_fem_5y, function(p) quantile(p, probs = c(0.025,0.975,0.5)))
cis2_rectum_nor_fem_5y<-c(cis2_rectum_nor_fem_5y[1,],rev(cis2_rectum_nor_fem_5y[2,]))

post_rectum_swe_fem_5y<-data.frame(post_rectum_swe_fem_5y)
cis2_rectum_swe_fem_5y<-sapply(post_rectum_swe_fem_5y, function(p) quantile(p, probs = c(0.025,0.975,0.5)))
cis2_rectum_swe_fem_5y<-c(cis2_rectum_swe_fem_5y[1,],rev(cis2_rectum_swe_fem_5y[2,]))

cis3_den_rectum_mal_5y<-sapply(dede_den_rectum_mal_5y, function(p) quantile(p, probs = c(0.025,0.975,0.5)))
cis3_den_rectum_fem_5y<-sapply(dede_den_rectum_fem_5y, function(p) quantile(p, probs = c(0.025,0.975,0.5)))
cis3_fin_rectum_mal_5y<-sapply(dede_fin_rectum_mal_5y, function(p) quantile(p, probs = c(0.025,0.975,0.5)))
cis3_fin_rectum_fem_5y<-sapply(dede_fin_rectum_fem_5y, function(p) quantile(p, probs = c(0.025,0.975,0.5)))
cis3_nor_rectum_mal_5y<-sapply(dede_nor_rectum_mal_5y, function(p) quantile(p, probs = c(0.025,0.975,0.5)))
cis3_nor_rectum_fem_5y<-sapply(dede_nor_rectum_fem_5y, function(p) quantile(p, probs = c(0.025,0.975,0.5)))
cis3_swe_rectum_mal_5y<-sapply(dede_swe_rectum_mal_5y, function(p) quantile(p, probs = c(0.025,0.975,0.5)))
cis3_swe_rectum_fem_5y<-sapply(dede_swe_rectum_fem_5y, function(p) quantile(p, probs = c(0.025,0.975,0.5)))


### cond --------------------------------------------------------------------
slope_den_rectum_mal_cond<-(post_rectum_den_mal_cond[,-1] - post_rectum_den_mal_cond[,-ncol(post_rectum_den_mal_cond)])*10
slope_den_rectum_mal_cond<-data.frame(slope_den_rectum_mal_cond)
slope_den_rectum_fem_cond<-(post_rectum_den_fem_cond[,-1] - post_rectum_den_fem_cond[,-ncol(post_rectum_den_fem_cond)])*10
slope_den_rectum_fem_cond<-data.frame(slope_den_rectum_fem_cond)

slope_fin_rectum_mal_cond<-(post_rectum_fin_mal_cond[,-1] - post_rectum_fin_mal_cond[,-ncol(post_rectum_fin_mal_cond)])*10
slope_fin_rectum_mal_cond<-data.frame(slope_fin_rectum_mal_cond)
slope_fin_rectum_fem_cond<-(post_rectum_fin_fem_cond[,-1] - post_rectum_fin_fem_cond[,-ncol(post_rectum_fin_fem_cond)])*10
slope_fin_rectum_fem_cond<-data.frame(slope_fin_rectum_fem_cond)

slope_nor_rectum_mal_cond<-(post_rectum_nor_mal_cond[,-1] - post_rectum_nor_mal_cond[,-ncol(post_rectum_nor_mal_cond)])*10
slope_nor_rectum_mal_cond<-data.frame(slope_nor_rectum_mal_cond)
slope_nor_rectum_fem_cond<-(post_rectum_nor_fem_cond[,-1] - post_rectum_nor_fem_cond[,-ncol(post_rectum_nor_fem_cond)])*10
slope_nor_rectum_fem_cond<-data.frame(slope_nor_rectum_fem_cond)

slope_swe_rectum_mal_cond<-(post_rectum_swe_mal_cond[,-1] - post_rectum_swe_mal_cond[,-ncol(post_rectum_swe_mal_cond)])*10
slope_swe_rectum_mal_cond<-data.frame(slope_swe_rectum_mal_cond)
slope_swe_rectum_fem_cond<-(post_rectum_swe_fem_cond[,-1] - post_rectum_swe_fem_cond[,-ncol(post_rectum_swe_fem_cond)])*10
slope_swe_rectum_fem_cond<-data.frame(slope_swe_rectum_fem_cond)

cis_den_rectum_mal_cond<-sapply(slope_den_rectum_mal_cond, function(p) quantile(p, probs = c(0.025,0.975,0.5)))
cis_den_rectum_fem_cond<-sapply(slope_den_rectum_fem_cond, function(p) quantile(p, probs = c(0.025,0.975,0.5)))
cis_fin_rectum_mal_cond<-sapply(slope_fin_rectum_mal_cond, function(p) quantile(p, probs = c(0.025,0.975,0.5)))
cis_fin_rectum_fem_cond<-sapply(slope_fin_rectum_fem_cond, function(p) quantile(p, probs = c(0.025,0.975,0.5)))
cis_nor_rectum_mal_cond<-sapply(slope_nor_rectum_mal_cond, function(p) quantile(p, probs = c(0.025,0.975,0.5)))
cis_nor_rectum_fem_cond<-sapply(slope_nor_rectum_fem_cond, function(p) quantile(p, probs = c(0.025,0.975,0.5)))
cis_swe_rectum_mal_cond<-sapply(slope_swe_rectum_mal_cond, function(p) quantile(p, probs = c(0.025,0.975,0.5)))
cis_swe_rectum_fem_cond<-sapply(slope_swe_rectum_fem_cond, function(p) quantile(p, probs = c(0.025,0.975,0.5)))

dede_den_rectum_mal_cond<-(slope_den_rectum_mal_cond[,-1] - slope_den_rectum_mal_cond[,-ncol(slope_den_rectum_mal_cond)])
dede_den_rectum_mal_cond<-data.frame(dede_den_rectum_mal_cond)
dede_den_rectum_fem_cond<-(slope_den_rectum_fem_cond[,-1] - slope_den_rectum_fem_cond[,-ncol(slope_den_rectum_fem_cond)])
dede_den_rectum_fem_cond<-data.frame(dede_den_rectum_fem_cond)

dede_fin_rectum_mal_cond<-(slope_fin_rectum_mal_cond[,-1] - slope_fin_rectum_mal_cond[,-ncol(slope_fin_rectum_mal_cond)])
dede_fin_rectum_mal_cond<-data.frame(dede_fin_rectum_mal_cond)
dede_fin_rectum_fem_cond<-(slope_fin_rectum_fem_cond[,-1] - slope_fin_rectum_fem_cond[,-ncol(slope_fin_rectum_fem_cond)])
dede_fin_rectum_fem_cond<-data.frame(dede_fin_rectum_fem_cond)

dede_nor_rectum_mal_cond<-(slope_nor_rectum_mal_cond[,-1] - slope_nor_rectum_mal_cond[,-ncol(slope_nor_rectum_mal_cond)])
dede_nor_rectum_mal_cond<-data.frame(dede_nor_rectum_mal_cond)
dede_nor_rectum_fem_cond<-(slope_nor_rectum_fem_cond[,-1] - slope_nor_rectum_fem_cond[,-ncol(slope_nor_rectum_fem_cond)])
dede_nor_rectum_fem_cond<-data.frame(dede_nor_rectum_fem_cond)

dede_swe_rectum_mal_cond<-(slope_swe_rectum_mal_cond[,-1] - slope_swe_rectum_mal_cond[,-ncol(slope_swe_rectum_mal_cond)])
dede_swe_rectum_mal_cond<-data.frame(dede_swe_rectum_mal_cond)
dede_swe_rectum_fem_cond<-(slope_swe_rectum_fem_cond[,-1] - slope_swe_rectum_fem_cond[,-ncol(slope_swe_rectum_fem_cond)])
dede_swe_rectum_fem_cond<-data.frame(dede_swe_rectum_fem_cond)

post_rectum_den_mal_cond<-data.frame(post_rectum_den_mal_cond)
cis2_rectum_den_mal_cond<-sapply(post_rectum_den_mal_cond, function(p) quantile(p, probs = c(0.025,0.975,0.5)))
cis2_rectum_den_mal_cond<-c(cis2_rectum_den_mal_cond[1,],rev(cis2_rectum_den_mal_cond[2,]))

post_rectum_fin_mal_cond<-data.frame(post_rectum_fin_mal_cond)
cis2_rectum_fin_mal_cond<-sapply(post_rectum_fin_mal_cond, function(p) quantile(p, probs = c(0.025,0.975,0.5)))
cis2_rectum_fin_mal_cond<-c(cis2_rectum_fin_mal_cond[1,],rev(cis2_rectum_fin_mal_cond[2,]))

post_rectum_nor_mal_cond<-data.frame(post_rectum_nor_mal_cond)
cis2_rectum_nor_mal_cond<-sapply(post_rectum_nor_mal_cond, function(p) quantile(p, probs = c(0.025,0.975,0.5)))
cis2_rectum_nor_mal_cond<-c(cis2_rectum_nor_mal_cond[1,],rev(cis2_rectum_nor_mal_cond[2,]))

post_rectum_swe_mal_cond<-data.frame(post_rectum_swe_mal_cond)
cis2_rectum_swe_mal_cond<-sapply(post_rectum_swe_mal_cond, function(p) quantile(p, probs = c(0.025,0.975,0.5)))
cis2_rectum_swe_mal_cond<-c(cis2_rectum_swe_mal_cond[1,],rev(cis2_rectum_swe_mal_cond[2,]))

post_rectum_den_fem_cond<-data.frame(post_rectum_den_fem_cond)
cis2_rectum_den_fem_cond<-sapply(post_rectum_den_fem_cond, function(p) quantile(p, probs = c(0.025,0.975,0.5)))
cis2_rectum_den_fem_cond<-c(cis2_rectum_den_fem_cond[1,],rev(cis2_rectum_den_fem_cond[2,]))

post_rectum_fin_fem_cond<-data.frame(post_rectum_fin_fem_cond)
cis2_rectum_fin_fem_cond<-sapply(post_rectum_fin_fem_cond, function(p) quantile(p, probs = c(0.025,0.975,0.5)))
cis2_rectum_fin_fem_cond<-c(cis2_rectum_fin_fem_cond[1,],rev(cis2_rectum_fin_fem_cond[2,]))

post_rectum_nor_fem_cond<-data.frame(post_rectum_nor_fem_cond)
cis2_rectum_nor_fem_cond<-sapply(post_rectum_nor_fem_cond, function(p) quantile(p, probs = c(0.025,0.975,0.5)))
cis2_rectum_nor_fem_cond<-c(cis2_rectum_nor_fem_cond[1,],rev(cis2_rectum_nor_fem_cond[2,]))

post_rectum_swe_fem_cond<-data.frame(post_rectum_swe_fem_cond)
cis2_rectum_swe_fem_cond<-sapply(post_rectum_swe_fem_cond, function(p) quantile(p, probs = c(0.025,0.975,0.5)))
cis2_rectum_swe_fem_cond<-c(cis2_rectum_swe_fem_cond[1,],rev(cis2_rectum_swe_fem_cond[2,]))

cis3_den_rectum_mal_cond<-sapply(dede_den_rectum_mal_cond, function(p) quantile(p, probs = c(0.025,0.975,0.5)))
cis3_den_rectum_fem_cond<-sapply(dede_den_rectum_fem_cond, function(p) quantile(p, probs = c(0.025,0.975,0.5)))
cis3_fin_rectum_mal_cond<-sapply(dede_fin_rectum_mal_cond, function(p) quantile(p, probs = c(0.025,0.975,0.5)))
cis3_fin_rectum_fem_cond<-sapply(dede_fin_rectum_fem_cond, function(p) quantile(p, probs = c(0.025,0.975,0.5)))
cis3_nor_rectum_mal_cond<-sapply(dede_nor_rectum_mal_cond, function(p) quantile(p, probs = c(0.025,0.975,0.5)))
cis3_nor_rectum_fem_cond<-sapply(dede_nor_rectum_fem_cond, function(p) quantile(p, probs = c(0.025,0.975,0.5)))
cis3_swe_rectum_mal_cond<-sapply(dede_swe_rectum_mal_cond, function(p) quantile(p, probs = c(0.025,0.975,0.5)))
cis3_swe_rectum_fem_cond<-sapply(dede_swe_rectum_fem_cond, function(p) quantile(p, probs = c(0.025,0.975,0.5)))


## small_intestine cancer ------------------------------------------------------------

### 1y ----------------------------------------------------------------------
slope_den_small_intestine_mal_1y<-(post_small_intestine_den_mal_1y[,-1] - post_small_intestine_den_mal_1y[,-ncol(post_small_intestine_den_mal_1y)])*10
slope_den_small_intestine_mal_1y<-data.frame(slope_den_small_intestine_mal_1y)
slope_den_small_intestine_fem_1y<-(post_small_intestine_den_fem_1y[,-1] - post_small_intestine_den_fem_1y[,-ncol(post_small_intestine_den_fem_1y)])*10
slope_den_small_intestine_fem_1y<-data.frame(slope_den_small_intestine_fem_1y)

slope_fin_small_intestine_mal_1y<-(post_small_intestine_fin_mal_1y[,-1] - post_small_intestine_fin_mal_1y[,-ncol(post_small_intestine_fin_mal_1y)])*10
slope_fin_small_intestine_mal_1y<-data.frame(slope_fin_small_intestine_mal_1y)
slope_fin_small_intestine_fem_1y<-(post_small_intestine_fin_fem_1y[,-1] - post_small_intestine_fin_fem_1y[,-ncol(post_small_intestine_fin_fem_1y)])*10
slope_fin_small_intestine_fem_1y<-data.frame(slope_fin_small_intestine_fem_1y)

slope_nor_small_intestine_mal_1y<-(post_small_intestine_nor_mal_1y[,-1] - post_small_intestine_nor_mal_1y[,-ncol(post_small_intestine_nor_mal_1y)])*10
slope_nor_small_intestine_mal_1y<-data.frame(slope_nor_small_intestine_mal_1y)
slope_nor_small_intestine_fem_1y<-(post_small_intestine_nor_fem_1y[,-1] - post_small_intestine_nor_fem_1y[,-ncol(post_small_intestine_nor_fem_1y)])*10
slope_nor_small_intestine_fem_1y<-data.frame(slope_nor_small_intestine_fem_1y)

slope_swe_small_intestine_mal_1y<-(post_small_intestine_swe_mal_1y[,-1] - post_small_intestine_swe_mal_1y[,-ncol(post_small_intestine_swe_mal_1y)])*10
slope_swe_small_intestine_mal_1y<-data.frame(slope_swe_small_intestine_mal_1y)
slope_swe_small_intestine_fem_1y<-(post_small_intestine_swe_fem_1y[,-1] - post_small_intestine_swe_fem_1y[,-ncol(post_small_intestine_swe_fem_1y)])*10
slope_swe_small_intestine_fem_1y<-data.frame(slope_swe_small_intestine_fem_1y)

cis_den_small_intestine_mal_1y<-sapply(slope_den_small_intestine_mal_1y, function(p) quantile(p, probs = c(0.025,0.975,0.5)))
cis_den_small_intestine_fem_1y<-sapply(slope_den_small_intestine_fem_1y, function(p) quantile(p, probs = c(0.025,0.975,0.5)))
cis_fin_small_intestine_mal_1y<-sapply(slope_fin_small_intestine_mal_1y, function(p) quantile(p, probs = c(0.025,0.975,0.5)))
cis_fin_small_intestine_fem_1y<-sapply(slope_fin_small_intestine_fem_1y, function(p) quantile(p, probs = c(0.025,0.975,0.5)))
cis_nor_small_intestine_mal_1y<-sapply(slope_nor_small_intestine_mal_1y, function(p) quantile(p, probs = c(0.025,0.975,0.5)))
cis_nor_small_intestine_fem_1y<-sapply(slope_nor_small_intestine_fem_1y, function(p) quantile(p, probs = c(0.025,0.975,0.5)))
cis_swe_small_intestine_mal_1y<-sapply(slope_swe_small_intestine_mal_1y, function(p) quantile(p, probs = c(0.025,0.975,0.5)))
cis_swe_small_intestine_fem_1y<-sapply(slope_swe_small_intestine_fem_1y, function(p) quantile(p, probs = c(0.025,0.975,0.5)))

dede_den_small_intestine_mal_1y<-(slope_den_small_intestine_mal_1y[,-1] - slope_den_small_intestine_mal_1y[,-ncol(slope_den_small_intestine_mal_1y)])
dede_den_small_intestine_mal_1y<-data.frame(dede_den_small_intestine_mal_1y)
dede_den_small_intestine_fem_1y<-(slope_den_small_intestine_fem_1y[,-1] - slope_den_small_intestine_fem_1y[,-ncol(slope_den_small_intestine_fem_1y)])
dede_den_small_intestine_fem_1y<-data.frame(dede_den_small_intestine_fem_1y)

dede_fin_small_intestine_mal_1y<-(slope_fin_small_intestine_mal_1y[,-1] - slope_fin_small_intestine_mal_1y[,-ncol(slope_fin_small_intestine_mal_1y)])
dede_fin_small_intestine_mal_1y<-data.frame(dede_fin_small_intestine_mal_1y)
dede_fin_small_intestine_fem_1y<-(slope_fin_small_intestine_fem_1y[,-1] - slope_fin_small_intestine_fem_1y[,-ncol(slope_fin_small_intestine_fem_1y)])
dede_fin_small_intestine_fem_1y<-data.frame(dede_fin_small_intestine_fem_1y)

dede_nor_small_intestine_mal_1y<-(slope_nor_small_intestine_mal_1y[,-1] - slope_nor_small_intestine_mal_1y[,-ncol(slope_nor_small_intestine_mal_1y)])
dede_nor_small_intestine_mal_1y<-data.frame(dede_nor_small_intestine_mal_1y)
dede_nor_small_intestine_fem_1y<-(slope_nor_small_intestine_fem_1y[,-1] - slope_nor_small_intestine_fem_1y[,-ncol(slope_nor_small_intestine_fem_1y)])
dede_nor_small_intestine_fem_1y<-data.frame(dede_nor_small_intestine_fem_1y)

dede_swe_small_intestine_mal_1y<-(slope_swe_small_intestine_mal_1y[,-1] - slope_swe_small_intestine_mal_1y[,-ncol(slope_swe_small_intestine_mal_1y)])
dede_swe_small_intestine_mal_1y<-data.frame(dede_swe_small_intestine_mal_1y)
dede_swe_small_intestine_fem_1y<-(slope_swe_small_intestine_fem_1y[,-1] - slope_swe_small_intestine_fem_1y[,-ncol(slope_swe_small_intestine_fem_1y)])
dede_swe_small_intestine_fem_1y<-data.frame(dede_swe_small_intestine_fem_1y)

post_small_intestine_den_mal_1y<-data.frame(post_small_intestine_den_mal_1y)
cis2_small_intestine_den_mal_1y<-sapply(post_small_intestine_den_mal_1y, function(p) quantile(p, probs = c(0.025,0.975,0.5)))
cis2_small_intestine_den_mal_1y<-c(cis2_small_intestine_den_mal_1y[1,],rev(cis2_small_intestine_den_mal_1y[2,]))

post_small_intestine_fin_mal_1y<-data.frame(post_small_intestine_fin_mal_1y)
cis2_small_intestine_fin_mal_1y<-sapply(post_small_intestine_fin_mal_1y, function(p) quantile(p, probs = c(0.025,0.975,0.5)))
cis2_small_intestine_fin_mal_1y<-c(cis2_small_intestine_fin_mal_1y[1,],rev(cis2_small_intestine_fin_mal_1y[2,]))

post_small_intestine_nor_mal_1y<-data.frame(post_small_intestine_nor_mal_1y)
cis2_small_intestine_nor_mal_1y<-sapply(post_small_intestine_nor_mal_1y, function(p) quantile(p, probs = c(0.025,0.975,0.5)))
cis2_small_intestine_nor_mal_1y<-c(cis2_small_intestine_nor_mal_1y[1,],rev(cis2_small_intestine_nor_mal_1y[2,]))

post_small_intestine_swe_mal_1y<-data.frame(post_small_intestine_swe_mal_1y)
cis2_small_intestine_swe_mal_1y<-sapply(post_small_intestine_swe_mal_1y, function(p) quantile(p, probs = c(0.025,0.975,0.5)))
cis2_small_intestine_swe_mal_1y<-c(cis2_small_intestine_swe_mal_1y[1,],rev(cis2_small_intestine_swe_mal_1y[2,]))

post_small_intestine_den_fem_1y<-data.frame(post_small_intestine_den_fem_1y)
cis2_small_intestine_den_fem_1y<-sapply(post_small_intestine_den_fem_1y, function(p) quantile(p, probs = c(0.025,0.975,0.5)))
cis2_small_intestine_den_fem_1y<-c(cis2_small_intestine_den_fem_1y[1,],rev(cis2_small_intestine_den_fem_1y[2,]))

post_small_intestine_fin_fem_1y<-data.frame(post_small_intestine_fin_fem_1y)
cis2_small_intestine_fin_fem_1y<-sapply(post_small_intestine_fin_fem_1y, function(p) quantile(p, probs = c(0.025,0.975,0.5)))
cis2_small_intestine_fin_fem_1y<-c(cis2_small_intestine_fin_fem_1y[1,],rev(cis2_small_intestine_fin_fem_1y[2,]))

post_small_intestine_nor_fem_1y<-data.frame(post_small_intestine_nor_fem_1y)
cis2_small_intestine_nor_fem_1y<-sapply(post_small_intestine_nor_fem_1y, function(p) quantile(p, probs = c(0.025,0.975,0.5)))
cis2_small_intestine_nor_fem_1y<-c(cis2_small_intestine_nor_fem_1y[1,],rev(cis2_small_intestine_nor_fem_1y[2,]))

post_small_intestine_swe_fem_1y<-data.frame(post_small_intestine_swe_fem_1y)
cis2_small_intestine_swe_fem_1y<-sapply(post_small_intestine_swe_fem_1y, function(p) quantile(p, probs = c(0.025,0.975,0.5)))
cis2_small_intestine_swe_fem_1y<-c(cis2_small_intestine_swe_fem_1y[1,],rev(cis2_small_intestine_swe_fem_1y[2,]))

cis3_den_small_intestine_mal_1y<-sapply(dede_den_small_intestine_mal_1y, function(p) quantile(p, probs = c(0.025,0.975,0.5)))
cis3_den_small_intestine_fem_1y<-sapply(dede_den_small_intestine_fem_1y, function(p) quantile(p, probs = c(0.025,0.975,0.5)))
cis3_fin_small_intestine_mal_1y<-sapply(dede_fin_small_intestine_mal_1y, function(p) quantile(p, probs = c(0.025,0.975,0.5)))
cis3_fin_small_intestine_fem_1y<-sapply(dede_fin_small_intestine_fem_1y, function(p) quantile(p, probs = c(0.025,0.975,0.5)))
cis3_nor_small_intestine_mal_1y<-sapply(dede_nor_small_intestine_mal_1y, function(p) quantile(p, probs = c(0.025,0.975,0.5)))
cis3_nor_small_intestine_fem_1y<-sapply(dede_nor_small_intestine_fem_1y, function(p) quantile(p, probs = c(0.025,0.975,0.5)))
cis3_swe_small_intestine_mal_1y<-sapply(dede_swe_small_intestine_mal_1y, function(p) quantile(p, probs = c(0.025,0.975,0.5)))
cis3_swe_small_intestine_fem_1y<-sapply(dede_swe_small_intestine_fem_1y, function(p) quantile(p, probs = c(0.025,0.975,0.5)))


### 5y ----------------------------------------------------------------------

slope_den_small_intestine_mal_5y<-(post_small_intestine_den_mal_5y[,-1] - post_small_intestine_den_mal_5y[,-ncol(post_small_intestine_den_mal_5y)])*10
slope_den_small_intestine_mal_5y<-data.frame(slope_den_small_intestine_mal_5y)
slope_den_small_intestine_fem_5y<-(post_small_intestine_den_fem_5y[,-1] - post_small_intestine_den_fem_5y[,-ncol(post_small_intestine_den_fem_5y)])*10
slope_den_small_intestine_fem_5y<-data.frame(slope_den_small_intestine_fem_5y)

slope_fin_small_intestine_mal_5y<-(post_small_intestine_fin_mal_5y[,-1] - post_small_intestine_fin_mal_5y[,-ncol(post_small_intestine_fin_mal_5y)])*10
slope_fin_small_intestine_mal_5y<-data.frame(slope_fin_small_intestine_mal_5y)
slope_fin_small_intestine_fem_5y<-(post_small_intestine_fin_fem_5y[,-1] - post_small_intestine_fin_fem_5y[,-ncol(post_small_intestine_fin_fem_5y)])*10
slope_fin_small_intestine_fem_5y<-data.frame(slope_fin_small_intestine_fem_5y)

slope_nor_small_intestine_mal_5y<-(post_small_intestine_nor_mal_5y[,-1] - post_small_intestine_nor_mal_5y[,-ncol(post_small_intestine_nor_mal_5y)])*10
slope_nor_small_intestine_mal_5y<-data.frame(slope_nor_small_intestine_mal_5y)
slope_nor_small_intestine_fem_5y<-(post_small_intestine_nor_fem_5y[,-1] - post_small_intestine_nor_fem_5y[,-ncol(post_small_intestine_nor_fem_5y)])*10
slope_nor_small_intestine_fem_5y<-data.frame(slope_nor_small_intestine_fem_5y)

slope_swe_small_intestine_mal_5y<-(post_small_intestine_swe_mal_5y[,-1] - post_small_intestine_swe_mal_5y[,-ncol(post_small_intestine_swe_mal_5y)])*10
slope_swe_small_intestine_mal_5y<-data.frame(slope_swe_small_intestine_mal_5y)
slope_swe_small_intestine_fem_5y<-(post_small_intestine_swe_fem_5y[,-1] - post_small_intestine_swe_fem_5y[,-ncol(post_small_intestine_swe_fem_5y)])*10
slope_swe_small_intestine_fem_5y<-data.frame(slope_swe_small_intestine_fem_5y)

cis_den_small_intestine_mal_5y<-sapply(slope_den_small_intestine_mal_5y, function(p) quantile(p, probs = c(0.025,0.975,0.5)))
cis_den_small_intestine_fem_5y<-sapply(slope_den_small_intestine_fem_5y, function(p) quantile(p, probs = c(0.025,0.975,0.5)))
cis_fin_small_intestine_mal_5y<-sapply(slope_fin_small_intestine_mal_5y, function(p) quantile(p, probs = c(0.025,0.975,0.5)))
cis_fin_small_intestine_fem_5y<-sapply(slope_fin_small_intestine_fem_5y, function(p) quantile(p, probs = c(0.025,0.975,0.5)))
cis_nor_small_intestine_mal_5y<-sapply(slope_nor_small_intestine_mal_5y, function(p) quantile(p, probs = c(0.025,0.975,0.5)))
cis_nor_small_intestine_fem_5y<-sapply(slope_nor_small_intestine_fem_5y, function(p) quantile(p, probs = c(0.025,0.975,0.5)))
cis_swe_small_intestine_mal_5y<-sapply(slope_swe_small_intestine_mal_5y, function(p) quantile(p, probs = c(0.025,0.975,0.5)))
cis_swe_small_intestine_fem_5y<-sapply(slope_swe_small_intestine_fem_5y, function(p) quantile(p, probs = c(0.025,0.975,0.5)))

dede_den_small_intestine_mal_5y<-(slope_den_small_intestine_mal_5y[,-1] - slope_den_small_intestine_mal_5y[,-ncol(slope_den_small_intestine_mal_5y)])
dede_den_small_intestine_mal_5y<-data.frame(dede_den_small_intestine_mal_5y)
dede_den_small_intestine_fem_5y<-(slope_den_small_intestine_fem_5y[,-1] - slope_den_small_intestine_fem_5y[,-ncol(slope_den_small_intestine_fem_5y)])
dede_den_small_intestine_fem_5y<-data.frame(dede_den_small_intestine_fem_5y)

dede_fin_small_intestine_mal_5y<-(slope_fin_small_intestine_mal_5y[,-1] - slope_fin_small_intestine_mal_5y[,-ncol(slope_fin_small_intestine_mal_5y)])
dede_fin_small_intestine_mal_5y<-data.frame(dede_fin_small_intestine_mal_5y)
dede_fin_small_intestine_fem_5y<-(slope_fin_small_intestine_fem_5y[,-1] - slope_fin_small_intestine_fem_5y[,-ncol(slope_fin_small_intestine_fem_5y)])
dede_fin_small_intestine_fem_5y<-data.frame(dede_fin_small_intestine_fem_5y)

dede_nor_small_intestine_mal_5y<-(slope_nor_small_intestine_mal_5y[,-1] - slope_nor_small_intestine_mal_5y[,-ncol(slope_nor_small_intestine_mal_5y)])
dede_nor_small_intestine_mal_5y<-data.frame(dede_nor_small_intestine_mal_5y)
dede_nor_small_intestine_fem_5y<-(slope_nor_small_intestine_fem_5y[,-1] - slope_nor_small_intestine_fem_5y[,-ncol(slope_nor_small_intestine_fem_5y)])
dede_nor_small_intestine_fem_5y<-data.frame(dede_nor_small_intestine_fem_5y)

dede_swe_small_intestine_mal_5y<-(slope_swe_small_intestine_mal_5y[,-1] - slope_swe_small_intestine_mal_5y[,-ncol(slope_swe_small_intestine_mal_5y)])
dede_swe_small_intestine_mal_5y<-data.frame(dede_swe_small_intestine_mal_5y)
dede_swe_small_intestine_fem_5y<-(slope_swe_small_intestine_fem_5y[,-1] - slope_swe_small_intestine_fem_5y[,-ncol(slope_swe_small_intestine_fem_5y)])
dede_swe_small_intestine_fem_5y<-data.frame(dede_swe_small_intestine_fem_5y)

post_small_intestine_den_mal_5y<-data.frame(post_small_intestine_den_mal_5y)
cis2_small_intestine_den_mal_5y<-sapply(post_small_intestine_den_mal_5y, function(p) quantile(p, probs = c(0.025,0.975,0.5)))
cis2_small_intestine_den_mal_5y<-c(cis2_small_intestine_den_mal_5y[1,],rev(cis2_small_intestine_den_mal_5y[2,]))

post_small_intestine_fin_mal_5y<-data.frame(post_small_intestine_fin_mal_5y)
cis2_small_intestine_fin_mal_5y<-sapply(post_small_intestine_fin_mal_5y, function(p) quantile(p, probs = c(0.025,0.975,0.5)))
cis2_small_intestine_fin_mal_5y<-c(cis2_small_intestine_fin_mal_5y[1,],rev(cis2_small_intestine_fin_mal_5y[2,]))

post_small_intestine_nor_mal_5y<-data.frame(post_small_intestine_nor_mal_5y)
cis2_small_intestine_nor_mal_5y<-sapply(post_small_intestine_nor_mal_5y, function(p) quantile(p, probs = c(0.025,0.975,0.5)))
cis2_small_intestine_nor_mal_5y<-c(cis2_small_intestine_nor_mal_5y[1,],rev(cis2_small_intestine_nor_mal_5y[2,]))

post_small_intestine_swe_mal_5y<-data.frame(post_small_intestine_swe_mal_5y)
cis2_small_intestine_swe_mal_5y<-sapply(post_small_intestine_swe_mal_5y, function(p) quantile(p, probs = c(0.025,0.975,0.5)))
cis2_small_intestine_swe_mal_5y<-c(cis2_small_intestine_swe_mal_5y[1,],rev(cis2_small_intestine_swe_mal_5y[2,]))

post_small_intestine_den_fem_5y<-data.frame(post_small_intestine_den_fem_5y)
cis2_small_intestine_den_fem_5y<-sapply(post_small_intestine_den_fem_5y, function(p) quantile(p, probs = c(0.025,0.975,0.5)))
cis2_small_intestine_den_fem_5y<-c(cis2_small_intestine_den_fem_5y[1,],rev(cis2_small_intestine_den_fem_5y[2,]))

post_small_intestine_fin_fem_5y<-data.frame(post_small_intestine_fin_fem_5y)
cis2_small_intestine_fin_fem_5y<-sapply(post_small_intestine_fin_fem_5y, function(p) quantile(p, probs = c(0.025,0.975,0.5)))
cis2_small_intestine_fin_fem_5y<-c(cis2_small_intestine_fin_fem_5y[1,],rev(cis2_small_intestine_fin_fem_5y[2,]))

post_small_intestine_nor_fem_5y<-data.frame(post_small_intestine_nor_fem_5y)
cis2_small_intestine_nor_fem_5y<-sapply(post_small_intestine_nor_fem_5y, function(p) quantile(p, probs = c(0.025,0.975,0.5)))
cis2_small_intestine_nor_fem_5y<-c(cis2_small_intestine_nor_fem_5y[1,],rev(cis2_small_intestine_nor_fem_5y[2,]))

post_small_intestine_swe_fem_5y<-data.frame(post_small_intestine_swe_fem_5y)
cis2_small_intestine_swe_fem_5y<-sapply(post_small_intestine_swe_fem_5y, function(p) quantile(p, probs = c(0.025,0.975,0.5)))
cis2_small_intestine_swe_fem_5y<-c(cis2_small_intestine_swe_fem_5y[1,],rev(cis2_small_intestine_swe_fem_5y[2,]))

cis3_den_small_intestine_mal_5y<-sapply(dede_den_small_intestine_mal_5y, function(p) quantile(p, probs = c(0.025,0.975,0.5)))
cis3_den_small_intestine_fem_5y<-sapply(dede_den_small_intestine_fem_5y, function(p) quantile(p, probs = c(0.025,0.975,0.5)))
cis3_fin_small_intestine_mal_5y<-sapply(dede_fin_small_intestine_mal_5y, function(p) quantile(p, probs = c(0.025,0.975,0.5)))
cis3_fin_small_intestine_fem_5y<-sapply(dede_fin_small_intestine_fem_5y, function(p) quantile(p, probs = c(0.025,0.975,0.5)))
cis3_nor_small_intestine_mal_5y<-sapply(dede_nor_small_intestine_mal_5y, function(p) quantile(p, probs = c(0.025,0.975,0.5)))
cis3_nor_small_intestine_fem_5y<-sapply(dede_nor_small_intestine_fem_5y, function(p) quantile(p, probs = c(0.025,0.975,0.5)))
cis3_swe_small_intestine_mal_5y<-sapply(dede_swe_small_intestine_mal_5y, function(p) quantile(p, probs = c(0.025,0.975,0.5)))
cis3_swe_small_intestine_fem_5y<-sapply(dede_swe_small_intestine_fem_5y, function(p) quantile(p, probs = c(0.025,0.975,0.5)))


### cond --------------------------------------------------------------------
slope_den_small_intestine_mal_cond<-(post_small_intestine_den_mal_cond[,-1] - post_small_intestine_den_mal_cond[,-ncol(post_small_intestine_den_mal_cond)])*10
slope_den_small_intestine_mal_cond<-data.frame(slope_den_small_intestine_mal_cond)
slope_den_small_intestine_fem_cond<-(post_small_intestine_den_fem_cond[,-1] - post_small_intestine_den_fem_cond[,-ncol(post_small_intestine_den_fem_cond)])*10
slope_den_small_intestine_fem_cond<-data.frame(slope_den_small_intestine_fem_cond)

slope_fin_small_intestine_mal_cond<-(post_small_intestine_fin_mal_cond[,-1] - post_small_intestine_fin_mal_cond[,-ncol(post_small_intestine_fin_mal_cond)])*10
slope_fin_small_intestine_mal_cond<-data.frame(slope_fin_small_intestine_mal_cond)
slope_fin_small_intestine_fem_cond<-(post_small_intestine_fin_fem_cond[,-1] - post_small_intestine_fin_fem_cond[,-ncol(post_small_intestine_fin_fem_cond)])*10
slope_fin_small_intestine_fem_cond<-data.frame(slope_fin_small_intestine_fem_cond)

slope_nor_small_intestine_mal_cond<-(post_small_intestine_nor_mal_cond[,-1] - post_small_intestine_nor_mal_cond[,-ncol(post_small_intestine_nor_mal_cond)])*10
slope_nor_small_intestine_mal_cond<-data.frame(slope_nor_small_intestine_mal_cond)
slope_nor_small_intestine_fem_cond<-(post_small_intestine_nor_fem_cond[,-1] - post_small_intestine_nor_fem_cond[,-ncol(post_small_intestine_nor_fem_cond)])*10
slope_nor_small_intestine_fem_cond<-data.frame(slope_nor_small_intestine_fem_cond)

slope_swe_small_intestine_mal_cond<-(post_small_intestine_swe_mal_cond[,-1] - post_small_intestine_swe_mal_cond[,-ncol(post_small_intestine_swe_mal_cond)])*10
slope_swe_small_intestine_mal_cond<-data.frame(slope_swe_small_intestine_mal_cond)
slope_swe_small_intestine_fem_cond<-(post_small_intestine_swe_fem_cond[,-1] - post_small_intestine_swe_fem_cond[,-ncol(post_small_intestine_swe_fem_cond)])*10
slope_swe_small_intestine_fem_cond<-data.frame(slope_swe_small_intestine_fem_cond)

cis_den_small_intestine_mal_cond<-sapply(slope_den_small_intestine_mal_cond, function(p) quantile(p, probs = c(0.025,0.975,0.5)))
cis_den_small_intestine_fem_cond<-sapply(slope_den_small_intestine_fem_cond, function(p) quantile(p, probs = c(0.025,0.975,0.5)))
cis_fin_small_intestine_mal_cond<-sapply(slope_fin_small_intestine_mal_cond, function(p) quantile(p, probs = c(0.025,0.975,0.5)))
cis_fin_small_intestine_fem_cond<-sapply(slope_fin_small_intestine_fem_cond, function(p) quantile(p, probs = c(0.025,0.975,0.5)))
cis_nor_small_intestine_mal_cond<-sapply(slope_nor_small_intestine_mal_cond, function(p) quantile(p, probs = c(0.025,0.975,0.5)))
cis_nor_small_intestine_fem_cond<-sapply(slope_nor_small_intestine_fem_cond, function(p) quantile(p, probs = c(0.025,0.975,0.5)))
cis_swe_small_intestine_mal_cond<-sapply(slope_swe_small_intestine_mal_cond, function(p) quantile(p, probs = c(0.025,0.975,0.5)))
cis_swe_small_intestine_fem_cond<-sapply(slope_swe_small_intestine_fem_cond, function(p) quantile(p, probs = c(0.025,0.975,0.5)))

dede_den_small_intestine_mal_cond<-(slope_den_small_intestine_mal_cond[,-1] - slope_den_small_intestine_mal_cond[,-ncol(slope_den_small_intestine_mal_cond)])
dede_den_small_intestine_mal_cond<-data.frame(dede_den_small_intestine_mal_cond)
dede_den_small_intestine_fem_cond<-(slope_den_small_intestine_fem_cond[,-1] - slope_den_small_intestine_fem_cond[,-ncol(slope_den_small_intestine_fem_cond)])
dede_den_small_intestine_fem_cond<-data.frame(dede_den_small_intestine_fem_cond)

dede_fin_small_intestine_mal_cond<-(slope_fin_small_intestine_mal_cond[,-1] - slope_fin_small_intestine_mal_cond[,-ncol(slope_fin_small_intestine_mal_cond)])
dede_fin_small_intestine_mal_cond<-data.frame(dede_fin_small_intestine_mal_cond)
dede_fin_small_intestine_fem_cond<-(slope_fin_small_intestine_fem_cond[,-1] - slope_fin_small_intestine_fem_cond[,-ncol(slope_fin_small_intestine_fem_cond)])
dede_fin_small_intestine_fem_cond<-data.frame(dede_fin_small_intestine_fem_cond)

dede_nor_small_intestine_mal_cond<-(slope_nor_small_intestine_mal_cond[,-1] - slope_nor_small_intestine_mal_cond[,-ncol(slope_nor_small_intestine_mal_cond)])
dede_nor_small_intestine_mal_cond<-data.frame(dede_nor_small_intestine_mal_cond)
dede_nor_small_intestine_fem_cond<-(slope_nor_small_intestine_fem_cond[,-1] - slope_nor_small_intestine_fem_cond[,-ncol(slope_nor_small_intestine_fem_cond)])
dede_nor_small_intestine_fem_cond<-data.frame(dede_nor_small_intestine_fem_cond)

dede_swe_small_intestine_mal_cond<-(slope_swe_small_intestine_mal_cond[,-1] - slope_swe_small_intestine_mal_cond[,-ncol(slope_swe_small_intestine_mal_cond)])
dede_swe_small_intestine_mal_cond<-data.frame(dede_swe_small_intestine_mal_cond)
dede_swe_small_intestine_fem_cond<-(slope_swe_small_intestine_fem_cond[,-1] - slope_swe_small_intestine_fem_cond[,-ncol(slope_swe_small_intestine_fem_cond)])
dede_swe_small_intestine_fem_cond<-data.frame(dede_swe_small_intestine_fem_cond)

post_small_intestine_den_mal_cond<-data.frame(post_small_intestine_den_mal_cond)
cis2_small_intestine_den_mal_cond<-sapply(post_small_intestine_den_mal_cond, function(p) quantile(p, probs = c(0.025,0.975,0.5)))
cis2_small_intestine_den_mal_cond<-c(cis2_small_intestine_den_mal_cond[1,],rev(cis2_small_intestine_den_mal_cond[2,]))

post_small_intestine_fin_mal_cond<-data.frame(post_small_intestine_fin_mal_cond)
cis2_small_intestine_fin_mal_cond<-sapply(post_small_intestine_fin_mal_cond, function(p) quantile(p, probs = c(0.025,0.975,0.5)))
cis2_small_intestine_fin_mal_cond<-c(cis2_small_intestine_fin_mal_cond[1,],rev(cis2_small_intestine_fin_mal_cond[2,]))

post_small_intestine_nor_mal_cond<-data.frame(post_small_intestine_nor_mal_cond)
cis2_small_intestine_nor_mal_cond<-sapply(post_small_intestine_nor_mal_cond, function(p) quantile(p, probs = c(0.025,0.975,0.5)))
cis2_small_intestine_nor_mal_cond<-c(cis2_small_intestine_nor_mal_cond[1,],rev(cis2_small_intestine_nor_mal_cond[2,]))

post_small_intestine_swe_mal_cond<-data.frame(post_small_intestine_swe_mal_cond)
cis2_small_intestine_swe_mal_cond<-sapply(post_small_intestine_swe_mal_cond, function(p) quantile(p, probs = c(0.025,0.975,0.5)))
cis2_small_intestine_swe_mal_cond<-c(cis2_small_intestine_swe_mal_cond[1,],rev(cis2_small_intestine_swe_mal_cond[2,]))

post_small_intestine_den_fem_cond<-data.frame(post_small_intestine_den_fem_cond)
cis2_small_intestine_den_fem_cond<-sapply(post_small_intestine_den_fem_cond, function(p) quantile(p, probs = c(0.025,0.975,0.5)))
cis2_small_intestine_den_fem_cond<-c(cis2_small_intestine_den_fem_cond[1,],rev(cis2_small_intestine_den_fem_cond[2,]))

post_small_intestine_fin_fem_cond<-data.frame(post_small_intestine_fin_fem_cond)
cis2_small_intestine_fin_fem_cond<-sapply(post_small_intestine_fin_fem_cond, function(p) quantile(p, probs = c(0.025,0.975,0.5)))
cis2_small_intestine_fin_fem_cond<-c(cis2_small_intestine_fin_fem_cond[1,],rev(cis2_small_intestine_fin_fem_cond[2,]))

post_small_intestine_nor_fem_cond<-data.frame(post_small_intestine_nor_fem_cond)
cis2_small_intestine_nor_fem_cond<-sapply(post_small_intestine_nor_fem_cond, function(p) quantile(p, probs = c(0.025,0.975,0.5)))
cis2_small_intestine_nor_fem_cond<-c(cis2_small_intestine_nor_fem_cond[1,],rev(cis2_small_intestine_nor_fem_cond[2,]))

post_small_intestine_swe_fem_cond<-data.frame(post_small_intestine_swe_fem_cond)
cis2_small_intestine_swe_fem_cond<-sapply(post_small_intestine_swe_fem_cond, function(p) quantile(p, probs = c(0.025,0.975,0.5)))
cis2_small_intestine_swe_fem_cond<-c(cis2_small_intestine_swe_fem_cond[1,],rev(cis2_small_intestine_swe_fem_cond[2,]))

cis3_den_small_intestine_mal_cond<-sapply(dede_den_small_intestine_mal_cond, function(p) quantile(p, probs = c(0.025,0.975,0.5)))
cis3_den_small_intestine_fem_cond<-sapply(dede_den_small_intestine_fem_cond, function(p) quantile(p, probs = c(0.025,0.975,0.5)))
cis3_fin_small_intestine_mal_cond<-sapply(dede_fin_small_intestine_mal_cond, function(p) quantile(p, probs = c(0.025,0.975,0.5)))
cis3_fin_small_intestine_fem_cond<-sapply(dede_fin_small_intestine_fem_cond, function(p) quantile(p, probs = c(0.025,0.975,0.5)))
cis3_nor_small_intestine_mal_cond<-sapply(dede_nor_small_intestine_mal_cond, function(p) quantile(p, probs = c(0.025,0.975,0.5)))
cis3_nor_small_intestine_fem_cond<-sapply(dede_nor_small_intestine_fem_cond, function(p) quantile(p, probs = c(0.025,0.975,0.5)))
cis3_swe_small_intestine_mal_cond<-sapply(dede_swe_small_intestine_mal_cond, function(p) quantile(p, probs = c(0.025,0.975,0.5)))
cis3_swe_small_intestine_fem_cond<-sapply(dede_swe_small_intestine_fem_cond, function(p) quantile(p, probs = c(0.025,0.975,0.5)))

```

## Visualisation

### Colors

```{r}
cola<-c(
  rgb(1,0,0,alpha=1),
  rgb(0.2,0.2,1,alpha=1),
  rgb(0, 0.9, 0,alpha=1),
  rgb(0.7,0.7,0.1,alpha=1))

colb<-c(
  rgb(1,0,0,alpha=0.2),
  rgb(0.2,0.2,1,alpha=0.2),
  rgb(0, 0.9, 0,alpha=0.2),
  rgb(0.7,0.7,0.1,alpha=0.2))

colc<-c(
  rgb(1,0,0,alpha=0.8),
  rgb(0.2,0.2,1,alpha=0.8),
  rgb(0, 0.9, 0,alpha=0.8),
  rgb(0.7,0.7,0.1,alpha=0.8))
```

### Functions used for plotting
\normalsize
The 1st function, ***tabce2***, draws lines of predicted survival across the 50 years. 

The line is **solid** if there is at least 95% plausibility for an increasing or decreasing trend (95% credible interval does not cross zero), in a duration of at least 5 years. 

***tabce2*** uses 2 arguments:

[1] *data* = bounds of 95% credible interval for **slope** (the 1st derivation) of a given survival measure over time. 

[2] *dat2* = whole posterior distribution for a given survival measure over time (1971-2020 by 1/10 of year)

It returns *data2*, i.e. a table with data where the trend in survival started to be, or stopped to be, at least 95% plausible

\small
```{r}
# 1st function
tabce2<-function(data,dat2){
  data=data[1:2,]
  cbinl<-c()
  x=1
  repeat{
    cbinl[x]<-
      if(data[1,x]>0|data[2,x]<0){cbinl[x]=1}else{cbinl[x]=0}
    x<-x+1
    if(x>length(data[1,])){break}}
  cbin=1;x<-1
  repeat{
    cbin[x+1]<-abs(cbinl[x]-cbinl[x+1])
    x=x+1
    if(x>(length(cbinl)-1)){break}}
  data<-data.frame(rbind(data,cbin));data[4,]<-yreal[c(2:500)]-0.049;data[5,]<-1:499
  row.names(data)<-c("cil","ciu","stat_change","year","timepoint");data[3,499]<-1
  data2=t(data[,data[3,]==1])
  data2<-data.frame(data2)
  tr<-data2;y=1
  yreal=seq(1971,2020,length=500)
  repeat{
    if((((tr[y,1]<0)&(tr[y,2])<0))|(((tr[y,1]>0)&(tr[y,2])>0))&(tr[y+1,4]-tr[y,4])>5)
    {lines(yreal[tr[y,5]:tr[y+1,5]],colMeans(dat2
    )[tr[y,5]:tr[y+1,5]],lwd=1.6,col=cola[xx],lend=1)}
    y<-y+1;if(y>dim(tr)[1]-1){break}}
  lines(yreal[1:500],colMeans(dat2)
        ,lwd=1,col=cola[xx],lty=2,lend=1)
  return(data2)
}
```

\normalsize
The 2nd function, ***tabce3***, identifies ***breaking points***, i.e. detectable **changes** in survival trend (slope), with at least 95% plausibility. 

It is calculated on the basis of a 95% credible interval for the 2nd derivation of a given survival measure. If the 2nd derivation is plausibly non-zero for at least 3 years, the function takes the peak in the 2nd derivation (within the identified time interval) as the *breaking point* (must be between the years 1976 and 2016)

There are 2 arguments in *tabce3*:

[1] *data* = bounds of 95% credible interval for the 2nd derivation of a given survival measure over time (time by 1/10 of year)

[2] *arb* = enables shifting of the *breaking point* on x-axis if brekaing points for difference groups overlap. It is usually zero, or small non-zero number in case of overlap.

The function prints:

[1] *bp* = data (years) of *brekaing points*

[2] *tr* = tables with data where change in survival trend (the 2nd derivation of survival) started to be, or stopped to be, at least 95% plausible (+ "edge" dates)

The function often gives warning: *## Error in xy.coords(x, y): 'x' and 'y' lengths differ*. Warning occurs when there is no *breaking point* in a given group and survival measure, ie, it is not real error. 

\small
```{r}
# 2nd function
tabce3<-function(data,arb){
  cbinl<-c()
  x=1
  repeat{
    cbinl[x]<-
      if(data[1,x]>0|data[2,x]<0){cbinl[x]=1}else{cbinl[x]=0}
    x<-x+1
    if(x>length(data[1,])){break}}
  cbin=1;x<-1
  repeat{
    cbin[x+1]<-abs(cbinl[x]-cbinl[x+1])
    x=x+1
    if(x>(length(cbinl)-1)){break}}
  data<-data.frame(rbind(data,cbin));data[5,]<-yreal[c(2:499)]-0.049
  data[6,]<-1:498;data[4,51]<-1;data[4,449]<-1
  
  row.names(data)<-c("cil","ciu","est","stat_change","year","timepoint")
  data2=t(data[,data[4,]==1])
  data2<-data.frame(data2)
  tr<-subset(data2,data2$timepoint>50&data2$timepoint<450)
  y=1
  bp<-c()
  bx<-1
  repeat{
    if( (tr[y,1]<0) & (tr[y,2]<0) & (  (tr$year[y+1]-tr$year[y])>3   )  ) {
      tr2<-data[,tr[y,6]:(tr[y+1,6]-2)]
      bp[bx]<- tr2[,order(tr2[3,],decreasing=F)[1]][5]
      bx=bx+1
    }
    if( (tr[y,1]>0) & (tr[y,2]>0) & (  (tr$year[y+1]-tr$year[y])>3   )) {
      tr2<-data[,tr[y,6]:(tr[y+1,6]-2)]
      bp[bx]<- tr2[,order(tr2[3,],decreasing=T)[1]][5]
      bx=bx+1
    }
    y=y+1;if(y>(dim(tr)[1]-1)){break}}
  y<-1;repeat{
    lines(c(bp[y]+arb,bp[y]+arb),c(range[1],range[1]+0.025*scal),col=cola[xx],lwd=3.5,lend=1)
    lines(c(bp[y]+arb,bp[y]+arb),c(range[2],range[2]-0.025*scal),col=cola[xx],lwd=3.5,lend=1)
    lines(c(bp[y]+arb,bp[y]+arb),c(range[1],range[1]+0.999*scal),col=colc[xx],lwd=1,lend=1,lty=2)
    y=y+1;if(y>length(bp)){break}}
  print(bp)
  print(tr)}
```

\normalsize
The 3rd function, ***tabce4***, is mixture of previous functions (*tabce2* and *tabce3*). 
Using *data* (bound of 95% credible intervals +median prediction for the 2nd derivation) and *dar2* (bound of 95% credible intervals + median prediction for the 1st derivation), it draws magnitude of change (slope) of the survival. 

**solid** lines imply that there is a plausible trend (decreasing or increasing; plausibility of 95%) in the slope of the survival

```{r}
tabce4<-function(data,dar2){
  dar2<-dar2[3,]
  dar2[dar2<0]<-0
  cbinl<-c()
  x=1
  repeat{
    cbinl[x]<-
      if(data[1,x]>0|data[2,x]<0){cbinl[x]=1}else{cbinl[x]=0}
    x<-x+1
    if(x>length(data[1,])){break}}
  cbin=1;x<-1
  repeat{
    cbin[x+1]<-abs(cbinl[x]-cbinl[x+1])
    x=x+1
    if(x>(length(cbinl)-1)){break}}
  data<-data.frame(rbind(data,cbin));data[5,]<-yreal[c(2:499)]-0.049;data[6,]<-1:498
  row.names(data)<-c("cil","ciu","est","stat_change","year","timepoint")
  data[4,450]<-1
  data[4,50]<-1
  data=data[,50:450]
  lines(yreal[1:499],dar2,lwd=1,col=cola[xx],lty=2,lend=1)
  data2=(t(data[,data[4,]==1]))
  data2<-data.frame(data2)
  tr<-data2;y=1
  yreal=seq(1971,2020,length=498)
  repeat{
    if(((((tr[y,1]<0)&(tr[y,2])<0))|(((tr[y,1]>0)&(tr[y,2])>0)))&(tr[y+1,5]-tr[y,5])>3)
    {lines(yreal[tr[y,6]:tr[y+1,6]],
           dar2[tr[y,6]:tr[y+1,6]]
           ,lwd=1.6,col=cola[xx],lend=1)}
    y<-y+1;if(y>dim(tr)[1]-1){break}}
  return(data2)}
```

### Fig. 1 - Denmark
```{r,fig.height=6.9,fig.width=8,error=TRUE,warning=FALSE,results=FALSE,message=FALSE}
m <- matrix(c(1,2,3
              ,4,6,8
              ,5,7,9), nrow = 3, ncol =3 ,byrow = TRUE)
layout(mat = m,heights = c(0.06,1-0.06))
par(mgp=c(1.6,0.8,0))
par(mar=c(0,0,0,0))
range<-c(0,100);scal<-range[2]-range[1]

plot(NULL, axes=FALSE,xlab="",ylab="",xlim=c(-1,1),ylim=c(-0.85,0.85))
text(0,-0.2,"Colon cancer",cex=1.6,font=3,xpd=TRUE)

plot(NULL, axes=FALSE,xlab="",ylab="",xlim=c(-1,1),ylim=c(-0.85,0.85))
text(0,-0.2,"Rectal cancer",cex=1.6,font=3,xpd=TRUE)

plot(NULL, axes=FALSE,xlab="",ylab="",xlim=c(-1,1),ylim=c(-0.85,0.85))
text(0,-0.2,"Small intestine cancer",cex=1.6,font=3,xpd=TRUE)


par(mgp=c(1.6,0.8,0))
par(mar=c(2,2.5,0,2))

### colon males % 

plot(NULL,xlim=c(1971,2020),ylim=c(range[1],range[2]),xlab="",ylab=""
     ,las=1, axes=FALSE)
rect(1971,range[2],2020,range[1],col="grey90",border=NA)
x<-10
repeat{
  lines(c(1971,2020),c(x,x),col="white")
  x=x+10;if(x>100){break}}

x<-1980
repeat{
  lines(c(x,x),c(range[1],range[2]),col="white")
  x=x+10;if(x>2020){break}}

xx=1
tabce3(cis3_den_colon_mal_1y,-0.6)
xx=xx+1
tabce3(cis3_den_colon_mal_cond,0)
xx=xx+1
tabce3(cis3_den_colon_mal_5y,0.6)
xx=1

x<-c(yreal[1:500],yreal[500:1])
xx=1
polygon(x,cis2_colon_den_mal_1y,border=NA,col=colb[xx],xpd=TRUE)
xx=xx+1
polygon(x,cis2_colon_den_mal_cond,border=NA,col=colb[xx],xpd=TRUE)
xx=xx+1
polygon(x,cis2_colon_den_mal_5y,border=NA,col=colb[xx],xpd=TRUE)

xx=1
points(colon[colon$group=="Denmark.Males",]$surv_1y~colon[colon$group=="Denmark.Males",]$year
       ,pch=17,col=colc[xx],cex=1);xx=xx+1
points(colon[colon$group=="Denmark.Males",]$surv_cond~colon[colon$group=="Denmark.Males",]$year
       ,pch=17,col=colc[xx],cex=1);xx=xx+1
points(colon[colon$group=="Denmark.Males",]$surv_5y~colon[colon$group=="Denmark.Males",]$year
       ,pch=17,col=colc[xx],cex=1)
xx=1
tabce2(cis_den_colon_mal_1y,post_colon_den_mal_1y);xx=xx+1
tabce2(cis_den_colon_mal_cond,post_colon_den_mal_cond);xx=xx+1
tabce2(cis_den_colon_mal_5y,post_colon_den_mal_5y);xx=1


axis(2,las=2,cex.axis=1.4,at=seq(range[1],range[2],by=10),labels=c(range[1],rep("",length(seq(range[1],range[2],by=10))-2),range[2]),pos=1971)
title(ylab="Male relative survival (%)", line=0.5, cex.lab=1.4)

xx=1;yy=range[1]+scal*0.91
xpo=-17
rect(1996+xpo,yy+0.035*scal,2017.9+xpo,yy-0.15*scal,col="white",border="grey50",lwd=0.8)
repeat{
  points(2000+xpo,yy,pch=17,col=cola[xx],cex=1.2)
  lines(c(1997+xpo,2003+xpo),c(yy,yy),lwd=1.6,col=cola[xx],lend=1)
  xx<-xx+1;yy=yy-(scal*0.058);if(xx>3){break}}
xx=1;yy=range[1]+scal*0.91
text(2010+xpo,yy,"1-year",col=cola[xx],cex=1.25);xx=xx+1;yy=yy-(scal*0.058)
text(2010+xpo,yy,"5/1-year",col=cola[xx],cex=1.25);xx=xx+1;yy=yy-(scal*0.058)
text(2010+xpo,yy,"5-year",col=cola[xx],cex=1.25);xx=xx+1;yy=yy-(scal*0.058)
text(1974,range[2]-0.05*scal,"a",cex=2.2)

# slope
x<-c(yreal[1:499],yreal[499:1])
cis2<-c(cis_den_colon_mal_1y[1,],rev(cis_den_colon_mal_1y[2,]));xx=1
cis2[cis2<range[1]]<-range[1]
cis2[cis2>range[2]]<-range[2]
cis2<-cis2*20
polygon(x,cis2,border=NA,col=colb[xx],xpd=F);xx=xx+1

cis2<-c(cis_den_colon_mal_cond[1,],rev(cis_den_colon_mal_cond[2,]))
cis2[cis2<range[1]]<-range[1]
cis2[cis2>range[2]]<-range[2]
cis2<-cis2*20
polygon(x,cis2,border=NA,col=colb[xx],xpd=F);xx=xx+1


cis2<-c(cis_den_colon_mal_5y[1,],rev(cis_den_colon_mal_5y[2,]))
cis2[cis2<range[1]]<-range[1]
cis2[cis2>range[2]]<-range[2]
cis2<-cis2*20
polygon(x,cis2,border=NA,col=colb[xx],xpd=F)

xx=1
tabce4(cis3_den_colon_mal_1y*20,cis_den_colon_mal_1y*20)
xx=xx+1
tabce4(cis3_den_colon_mal_cond*20,cis_den_colon_mal_cond*20)
xx=xx+1
tabce4(cis3_den_colon_mal_5y*20,cis_den_colon_mal_5y*20)

axis(4,las=2,cex.axis=1.4,at=seq(range[1],range[2],by=10),labels=c(range[1],rep("",length(seq(range[1],range[2],by=10))-2),range[2]/20),pos=2020)
text(2024.5,50,"Change in survival over a year",cex=1.3,srt=270,xpd=TRUE)

axis(side=1,las=1,cex.axis=1.4,at=c(seq(1980,2020,by=10)),pos=range[1])
lines(c(1971,2020),c(range[1],range[1]))
title(xlab="Year", line=1, cex.lab=1.4,xpd=TRUE)

### colon females %

plot(NULL,xlim=c(1971,2020),ylim=c(range[1],range[2]),xlab="",ylab=""
     ,las=1, axes=FALSE)
rect(1971,range[2],2020,range[1],col="grey90",border=NA)
x<-10
repeat{
  lines(c(1971,2020),c(x,x),col="white")
  x=x+10;if(x>100){break}}

x<-1980
repeat{
  lines(c(x,x),c(range[1],range[2]),col="white")
  x=x+10;if(x>2020){break}}

x<-c(yreal[1:500],yreal[500:1])
xx=1
tabce3(cis3_den_colon_fem_1y,0)
xx=xx+1
tabce3(cis3_den_colon_fem_cond,0)
xx=xx+1
tabce3(cis3_den_colon_fem_5y,0)

xx=1
polygon(x,cis2_colon_den_fem_1y,border=NA,col=colb[xx],xpd=TRUE);xx=xx+1
polygon(x,cis2_colon_den_fem_cond,border=NA,col=colb[xx],xpd=TRUE);xx=xx+1
polygon(x,cis2_colon_den_fem_5y,border=NA,col=colb[xx],xpd=TRUE);xx=xx+1

xx=1
points(colon[colon$group=="Denmark.Females",]$surv_1y~colon[colon$group=="Denmark.Females",]$year
       ,pch=17,col=colc[xx],cex=1);xx=xx+1
points(colon[colon$group=="Denmark.Females",]$surv_cond~colon[colon$group=="Denmark.Females",]$year
       ,pch=17,col=colc[xx],cex=1);xx=xx+1
points(colon[colon$group=="Denmark.Females",]$surv_5y~colon[colon$group=="Denmark.Females",]$year
       ,pch=17,col=colc[xx],cex=1)
xx=1
tabce2(cis_den_colon_fem_1y,post_colon_den_fem_1y);xx=xx+1
tabce2(cis_den_colon_fem_cond,post_colon_den_fem_cond);xx=xx+1
tabce2(cis_den_colon_fem_5y,post_colon_den_fem_5y);xx=1

axis(2,las=2,cex.axis=1.4,at=seq(range[1],range[2],by=10),labels=c(range[1],rep("",length(seq(range[1],range[2],by=10))-2),range[2]),pos=1971)
title(ylab="Female relative survival (%)", line=0.5, cex.lab=1.4)

xx=1;yy=range[1]+scal*0.91
xpo=-17
text(1974,range[2]-0.05*scal,"d",cex=2.2)

# slope
x<-c(yreal[1:499],yreal[499:1])
cis2<-c(cis_den_colon_fem_1y[1,],rev(cis_den_colon_fem_1y[2,]));xx=1
cis2[cis2<range[1]]<-range[1]
cis2[cis2>range[2]]<-range[2]
cis2<-cis2*20
polygon(x,cis2,border=NA,col=colb[xx],xpd=F);xx=xx+1

cis2<-c(cis_den_colon_fem_cond[1,],rev(cis_den_colon_fem_cond[2,]))
cis2[cis2<range[1]]<-range[1]
cis2[cis2>range[2]]<-range[2]
cis2<-cis2*20
polygon(x,cis2,border=NA,col=colb[xx],xpd=F);xx=xx+1


cis2<-c(cis_den_colon_fem_5y[1,],rev(cis_den_colon_fem_5y[2,]))
cis2[cis2<range[1]]<-range[1]
cis2[cis2>range[2]]<-range[2]
cis2<-cis2*20
polygon(x,cis2,border=NA,col=colb[xx],xpd=F)

xx=1
tabce4(cis3_den_colon_fem_1y*20,cis_den_colon_fem_1y*20)
xx=xx+1
tabce4(cis3_den_colon_fem_cond*20,cis_den_colon_fem_cond*20)
xx=xx+1
tabce4(cis3_den_colon_fem_5y*20,cis_den_colon_fem_5y*20)

axis(4,las=2,cex.axis=1.4,at=seq(range[1],range[2],by=10),labels=c(range[1],rep("",length(seq(range[1],range[2],by=10))-2),range[2]/20),pos=2020)
text(2024.5,50,"Change in survival over a year",cex=1.3,srt=270,xpd=TRUE)

axis(side=1,las=1,cex.axis=1.4,at=c(seq(1980,2020,by=10)),pos=range[1])
lines(c(1971,2020),c(range[1],range[1]))
title(xlab="Year", line=1, cex.lab=1.4,xpd=TRUE)


### rectum males % ------------------------------------------------------

plot(NULL,xlim=c(1971,2020),ylim=c(range[1],range[2]),xlab="",ylab=""
     ,las=1, axes=FALSE)
rect(1971,range[2],2020,range[1],col="grey90",border=NA)
x<-10
repeat{
  lines(c(1971,2020),c(x,x),col="white")
  x=x+10;if(x>100){break}}

x<-1980
repeat{
  lines(c(x,x),c(range[1],range[2]),col="white")
  x=x+10;if(x>2020){break}}


x<-c(yreal[1:500],yreal[500:1])
xx=1
tabce3(cis3_den_rectum_mal_1y,0)
xx=xx+1
tabce3(cis3_den_rectum_mal_cond,-1)
xx=xx+1
tabce3(cis3_den_rectum_mal_5y,1)

xx=1
polygon(x,cis2_rectum_den_mal_1y,border=NA,col=colb[xx],xpd=TRUE);xx=xx+1
polygon(x,cis2_rectum_den_mal_cond,border=NA,col=colb[xx],xpd=TRUE);xx=xx+1
polygon(x,cis2_rectum_den_mal_5y,border=NA,col=colb[xx],xpd=TRUE);xx=xx+1

xx=1
points(rectum[rectum$group=="Denmark.Males",]$surv_1y~rectum[rectum$group=="Denmark.Males",]$year
       ,pch=17,col=colc[xx],cex=1);xx=xx+1
points(rectum[rectum$group=="Denmark.Males",]$surv_cond~rectum[rectum$group=="Denmark.Males",]$year
       ,pch=17,col=colc[xx],cex=1);xx=xx+1
points(rectum[rectum$group=="Denmark.Males",]$surv_5y~rectum[rectum$group=="Denmark.Males",]$year
       ,pch=17,col=colc[xx],cex=1)
xx=1
tabce2(cis_den_rectum_mal_1y,post_rectum_den_mal_1y);xx=xx+1
tabce2(cis_den_rectum_mal_cond,post_rectum_den_mal_cond);xx=xx+1
tabce2(cis_den_rectum_mal_5y,post_rectum_den_mal_5y);xx=1


axis(2,las=2,cex.axis=1.4,at=seq(range[1],range[2],by=10),labels=c(range[1],rep("",length(seq(range[1],range[2],by=10))-2),range[2]),pos=1971)
title(ylab="Male relative survival (%)", line=0.5, cex.lab=1.4)
text(1974,range[2]-0.05*scal,"b",cex=2.2)

# slope
x<-c(yreal[1:499],yreal[499:1])
cis2<-c(cis_den_rectum_mal_1y[1,],rev(cis_den_rectum_mal_1y[2,]));xx=1
cis2[cis2<range[1]]<-range[1]
cis2[cis2>range[2]]<-range[2]
cis2<-cis2*20
polygon(x,cis2,border=NA,col=colb[xx],xpd=F);xx=xx+1

cis2<-c(cis_den_rectum_mal_cond[1,],rev(cis_den_rectum_mal_cond[2,]))
cis2[cis2<range[1]]<-range[1]
cis2[cis2>range[2]]<-range[2]
cis2<-cis2*20
polygon(x,cis2,border=NA,col=colb[xx],xpd=F);xx=xx+1


cis2<-c(cis_den_rectum_mal_5y[1,],rev(cis_den_rectum_mal_5y[2,]))
cis2[cis2<range[1]]<-range[1]
cis2[cis2>range[2]]<-range[2]
cis2<-cis2*20
polygon(x,cis2,border=NA,col=colb[xx],xpd=F)

xx=1
tabce4(cis3_den_rectum_mal_1y*20,cis_den_rectum_mal_1y*20)
xx=xx+1
tabce4(cis3_den_rectum_mal_cond*20,cis_den_rectum_mal_cond*20)
xx=xx+1
tabce4(cis3_den_rectum_mal_5y*20,cis_den_rectum_mal_5y*20)

axis(4,las=2,cex.axis=1.4,at=seq(range[1],range[2],by=10),labels=c(range[1],rep("",length(seq(range[1],range[2],by=10))-2),range[2]/20),pos=2020)
text(2024.5,50,"Change in survival over a year",cex=1.3,srt=270,xpd=TRUE)

axis(side=1,las=1,cex.axis=1.4,at=c(seq(1980,2020,by=10)),pos=range[1])
lines(c(1971,2020),c(range[1],range[1]))
title(xlab="Year", line=1, cex.lab=1.4,xpd=TRUE)



### rectum females % ------------------------------------------------------

plot(NULL,xlim=c(1971,2020),ylim=c(range[1],range[2]),xlab="",ylab=""
     ,las=1, axes=FALSE)
rect(1971,range[2],2020,range[1],col="grey90",border=NA)
x<-10
repeat{
  lines(c(1971,2020),c(x,x),col="white")
  x=x+10;if(x>100){break}}

x<-1980
repeat{
  lines(c(x,x),c(range[1],range[2]),col="white")
  x=x+10;if(x>2020){break}}

x<-c(yreal[1:500],yreal[500:1])
xx=1
tabce3(cis3_den_rectum_fem_1y,0)
xx=xx+1
tabce3(cis3_den_rectum_fem_cond,-0.6)
xx=xx+1
tabce3(cis3_den_rectum_fem_5y,0.6)

xx=1
polygon(x,cis2_rectum_den_fem_1y,border=NA,col=colb[xx],xpd=TRUE);xx=xx+1
polygon(x,cis2_rectum_den_fem_cond,border=NA,col=colb[xx],xpd=TRUE);xx=xx+1
polygon(x,cis2_rectum_den_fem_5y,border=NA,col=colb[xx],xpd=TRUE);xx=xx+1

xx=1
points(rectum[rectum$group=="Denmark.Females",]$surv_1y~rectum[rectum$group=="Denmark.Females",]$year ,pch=17,col=colc[xx],cex=1);xx=xx+1
points(rectum[rectum$group=="Denmark.Females",]$surv_cond~rectum[rectum$group=="Denmark.Females",]$year,pch=17,col=colc[xx],cex=1);xx=xx+1
points(rectum[rectum$group=="Denmark.Females",]$surv_5y~rectum[rectum$group=="Denmark.Females",]$year,pch=17,col=colc[xx],cex=1)
xx=1
tabce2(cis_den_rectum_fem_1y,post_rectum_den_fem_1y);xx=xx+1
tabce2(cis_den_rectum_fem_cond,post_rectum_den_fem_cond);xx=xx+1
tabce2(cis_den_rectum_fem_5y,post_rectum_den_fem_5y);xx=1


axis(2,las=2,cex.axis=1.4,at=seq(range[1],range[2],by=10),labels=c(range[1],rep("",length(seq(range[1],range[2],by=10))-2),range[2]),pos=1971)
title(ylab="Female relative survival (%)", line=0.5, cex.lab=1.4)
text(1974,range[2]-0.05*scal,"e",cex=2.2)

# slope
x<-c(yreal[1:499],yreal[499:1])
cis2<-c(cis_den_rectum_fem_1y[1,],rev(cis_den_rectum_fem_1y[2,]));xx=1
cis2[cis2<range[1]]<-range[1]
cis2[cis2>range[2]]<-range[2]
cis2<-cis2*20
polygon(x,cis2,border=NA,col=colb[xx],xpd=F);xx=xx+1

cis2<-c(cis_den_rectum_fem_cond[1,],rev(cis_den_rectum_fem_cond[2,]))
cis2[cis2<range[1]]<-range[1]
cis2[cis2>range[2]]<-range[2]
cis2<-cis2*20
polygon(x,cis2,border=NA,col=colb[xx],xpd=F);xx=xx+1


cis2<-c(cis_den_rectum_fem_5y[1,],rev(cis_den_rectum_fem_5y[2,]))
cis2[cis2<range[1]]<-range[1]
cis2[cis2>range[2]]<-range[2]
cis2<-cis2*20
polygon(x,cis2,border=NA,col=colb[xx],xpd=F)

xx=1
tabce4(cis3_den_rectum_fem_1y*20,cis_den_rectum_fem_1y*20)
xx=xx+1
tabce4(cis3_den_rectum_fem_cond*20,cis_den_rectum_fem_cond*20)
xx=xx+1
tabce4(cis3_den_rectum_fem_5y*20,cis_den_rectum_fem_5y*20)

axis(4,las=2,cex.axis=1.4,at=seq(range[1],range[2],by=10),labels=c(range[1],rep("",length(seq(range[1],range[2],by=10))-2),range[2]/20),pos=2020)
text(2024.5,50,"Change in survival over a year",cex=1.3,srt=270,xpd=TRUE)

axis(side=1,las=1,cex.axis=1.4,at=c(seq(1980,2020,by=10)),pos=range[1])
lines(c(1971,2020),c(range[1],range[1]))
title(xlab="Year", line=1, cex.lab=1.4,xpd=TRUE)


### small_intestine males % ------------------------------------------------------

plot(NULL,xlim=c(1971,2020),ylim=c(range[1],range[2]),xlab="",ylab=""
     ,las=1, axes=FALSE)
rect(1971,range[2],2020,range[1],col="grey90",border=NA)
x<-10
repeat{
  lines(c(1971,2020),c(x,x),col="white")
  x=x+10;if(x>100){break}}

x<-1980
repeat{
  lines(c(x,x),c(range[1],range[2]),col="white")
  x=x+10;if(x>2020){break}}

x<-c(yreal[1:500],yreal[500:1])

xx=1
tabce3(cis3_den_small_intestine_mal_1y,0)
xx=xx+1
tabce3(cis3_den_small_intestine_mal_cond,-0.6)
xx=xx+1
tabce3(cis3_den_small_intestine_mal_5y,0.6)

xx=1
polygon(x,cis2_small_intestine_den_mal_1y,border=NA,col=colb[xx],xpd=TRUE);xx=xx+1
polygon(x,cis2_small_intestine_den_mal_cond,border=NA,col=colb[xx],xpd=TRUE);xx=xx+1
polygon(x,cis2_small_intestine_den_mal_5y,border=NA,col=colb[xx],xpd=TRUE);xx=xx+1

xx=1
points(small_intestine[small_intestine$group=="Denmark.Males",]$surv_1y~small_intestine[small_intestine$group=="Denmark.Males",]$year
       ,pch=17,col=colc[xx],cex=1);xx=xx+1
points(small_intestine[small_intestine$group=="Denmark.Males",]$surv_cond~small_intestine[small_intestine$group=="Denmark.Males",]$year
       ,pch=17,col=colc[xx],cex=1);xx=xx+1
points(small_intestine[small_intestine$group=="Denmark.Males",]$surv_5y~small_intestine[small_intestine$group=="Denmark.Males",]$year
       ,pch=17,col=colc[xx],cex=1)
xx=1
tabce2(cis_den_small_intestine_mal_1y,post_small_intestine_den_mal_1y);xx=xx+1
tabce2(cis_den_small_intestine_mal_cond,post_small_intestine_den_mal_cond);xx=xx+1
tabce2(cis_den_small_intestine_mal_5y,post_small_intestine_den_mal_5y);xx=1


axis(2,las=2,cex.axis=1.4,at=seq(range[1],range[2],by=10),labels=c(range[1],rep("",length(seq(range[1],range[2],by=10))-2),range[2]),pos=1971)
title(ylab="Male relative survival (%)", line=0.5, cex.lab=1.4)
axis(side=1,las=1,cex.axis=1.4,at=c(seq(1980,2020,by=10)),pos=range[1])
lines(c(1971,2020),c(range[1],range[1]))
title(xlab="Year", line=1, cex.lab=1.4,xpd=TRUE)
text(1974,range[2]-0.05*scal,"c",cex=2.2)

ypo=-78
xfl=48
rect(1956+xfl,range[1]+scal*0.965+ypo,1968+xfl,range[1]+scal*0.84+ypo,col="red2",border="grey50")
rect(1956+xfl,range[1]+scal*0.9135+ypo,1968+xfl,range[1]+scal*0.8865+ypo,col="white",border=NA)
rect(1960+xfl,range[1]+scal*0.965+ypo,1962+xfl,range[1]+scal*0.84+ypo,col="white",border=NA)


### small_intestine females % ------------------------------------------------------

plot(NULL,xlim=c(1971,2020),ylim=c(range[1],range[2]),xlab="",ylab=""
     ,las=1, axes=FALSE)
rect(1971,range[2],2020,range[1],col="grey90",border=NA)
x<-10
repeat{
  lines(c(1971,2020),c(x,x),col="white")
  x=x+10;if(x>100){break}}

x<-1980
repeat{
  lines(c(x,x),c(range[1],range[2]),col="white")
  x=x+10;if(x>2020){break}}

x<-c(yreal[1:500],yreal[500:1])

xx=1
tabce3(cis3_den_small_intestine_fem_1y,0)
xx=xx+1
tabce3(cis3_den_small_intestine_fem_cond,-0.6)
xx=xx+1
tabce3(cis3_den_small_intestine_fem_5y,0.6)


xx=1
polygon(x,cis2_small_intestine_den_fem_1y,border=NA,col=colb[xx],xpd=TRUE);xx=xx+1
polygon(x,cis2_small_intestine_den_fem_cond,border=NA,col=colb[xx],xpd=TRUE);xx=xx+1
polygon(x,cis2_small_intestine_den_fem_5y,border=NA,col=colb[xx],xpd=TRUE);xx=xx+1

xx=1
points(small_intestine[small_intestine$group=="Denmark.Females",]$surv_1y~small_intestine[small_intestine$group=="Denmark.Females",]$year
       ,pch=17,col=colc[xx],cex=1);xx=xx+1
points(small_intestine[small_intestine$group=="Denmark.Females",]$surv_cond~small_intestine[small_intestine$group=="Denmark.Females",]$year
       ,pch=17,col=colc[xx],cex=1);xx=xx+1
points(small_intestine[small_intestine$group=="Denmark.Females",]$surv_5y~small_intestine[small_intestine$group=="Denmark.Females",]$year
       ,pch=17,col=colc[xx],cex=1)
xx=1
tabce2(cis_den_small_intestine_fem_1y,post_small_intestine_den_fem_1y);xx=xx+1
tabce2(cis_den_small_intestine_fem_cond,post_small_intestine_den_fem_cond);xx=xx+1
tabce2(cis_den_small_intestine_fem_5y,post_small_intestine_den_fem_5y);xx=1

axis(2,las=2,cex.axis=1.4,at=seq(range[1],range[2],by=10),labels=c(range[1],rep("",length(seq(range[1],range[2],by=10))-2),range[2]),pos=1971)
title(ylab="Female relative survival (%)", line=0.5, cex.lab=1.4)
axis(side=1,las=1,cex.axis=1.4,at=c(seq(1980,2020,by=10)),pos=range[1])
lines(c(1971,2020),c(range[1],range[1]))
title(xlab="Year", line=1, cex.lab=1.4,xpd=TRUE)

text(1974,range[2]-0.05*scal,"f",cex=2.2)
```

### Fig. 2 - Finland
```{r,fig.height=6.9,fig.width=8,error=TRUE,warning=FALSE,results=FALSE,message=FALSE}
## FIN figures -----------------
m <- matrix(c(1,2,3
              ,4,6,8
              ,5,7,9), nrow = 3, ncol =3 ,byrow = TRUE)
layout(mat = m,heights = c(0.06,1-0.06))
par(mgp=c(1.6,0.8,0))
par(mar=c(0,0,0,0))
range<-c(0,100);scal<-range[2]-range[1]

plot(NULL, axes=FALSE,xlab="",ylab="",xlim=c(-1,1),ylim=c(-0.85,0.85))
text(0,-0.2,"Colon cancer",cex=1.6,font=3,xpd=TRUE)

plot(NULL, axes=FALSE,xlab="",ylab="",xlim=c(-1,1),ylim=c(-0.85,0.85))
text(0,-0.2,"Rectal cancer",cex=1.6,font=3,xpd=TRUE)

plot(NULL, axes=FALSE,xlab="",ylab="",xlim=c(-1,1),ylim=c(-0.85,0.85))
text(0,-0.2,"Small intestine cancer",cex=1.6,font=3,xpd=TRUE)


par(mgp=c(1.6,0.8,0))
par(mar=c(2,2.5,0,2))

### colon males % ------------------------------------------------------

plot(NULL,xlim=c(1971,2020),ylim=c(range[1],range[2]),xlab="",ylab=""
     ,las=1, axes=FALSE)
rect(1971,range[2],2020,range[1],col="grey90",border=NA)
x<-10
repeat{
  lines(c(1971,2020),c(x,x),col="white")
  x=x+10;if(x>100){break}}

x<-1980
repeat{
  lines(c(x,x),c(range[1],range[2]),col="white")
  x=x+10;if(x>2020){break}}

x<-c(yreal[1:500],yreal[500:1])
xx=1
tabce3(cis3_fin_colon_mal_1y,0)
xx=xx+1
tabce3(cis3_fin_colon_mal_cond,-0.6)
xx=xx+1
tabce3(cis3_fin_colon_mal_5y,0.6)


xx=1
polygon(x,cis2_colon_fin_mal_1y,border=NA,col=colb[xx],xpd=TRUE);xx=xx+1
polygon(x,cis2_colon_fin_mal_cond,border=NA,col=colb[xx],xpd=TRUE);xx=xx+1
polygon(x,cis2_colon_fin_mal_5y,border=NA,col=colb[xx],xpd=TRUE)

xx=1
points(colon[colon$group=="Finland.Males",]$surv_1y~colon[colon$group=="Finland.Males",]$year
       ,pch=17,col=colc[xx],cex=1);xx=xx+1
points(colon[colon$group=="Finland.Males",]$surv_cond~colon[colon$group=="Finland.Males",]$year
       ,pch=17,col=colc[xx],cex=1);xx=xx+1
points(colon[colon$group=="Finland.Males",]$surv_5y~colon[colon$group=="Finland.Males",]$year
       ,pch=17,col=colc[xx],cex=1)
xx=1
tabce2(cis_fin_colon_mal_1y,post_colon_fin_mal_1y);xx=xx+1
tabce2(cis_fin_colon_mal_cond,post_colon_fin_mal_cond);xx=xx+1
tabce2(cis_fin_colon_mal_5y,post_colon_fin_mal_5y);xx=1


axis(2,las=2,cex.axis=1.4,at=seq(range[1],range[2],by=10),labels=c(range[1],rep("",length(seq(range[1],range[2],by=10))-2),range[2]),pos=1971)
title(ylab="Male relative survival (%)", line=0.5, cex.lab=1.4)

xx=1;yy=range[1]+scal*0.37
xpo=-1
rect(1996+xpo,yy+0.035*scal,2017.9+xpo,yy-0.15*scal,col="white",border="grey50",lwd=0.8)
repeat{
  points(2000+xpo,yy,pch=17,col=cola[xx],cex=1.2)
  lines(c(1997+xpo,2003+xpo),c(yy,yy),lwd=1.6,col=cola[xx],lend=1)
  xx<-xx+1;yy=yy-(scal*0.058);if(xx>3){break}}
xx=1;yy=range[1]+scal*0.37
text(2010+xpo,yy,"1-year",col=cola[xx],cex=1.25);xx=xx+1;yy=yy-(scal*0.058)
text(2010+xpo,yy,"5/1-year",col=cola[xx],cex=1.25);xx=xx+1;yy=yy-(scal*0.058)
text(2010+xpo,yy,"5-year",col=cola[xx],cex=1.25);xx=xx+1;yy=yy-(scal*0.058)
text(1974,range[2]-0.05*scal,"a",cex=2.2)

# slope
x<-c(yreal[1:499],yreal[499:1])
cis2<-c(cis_fin_colon_mal_1y[1,],rev(cis_fin_colon_mal_1y[2,]));xx=1
cis2[cis2<range[1]]<-range[1]
cis2[cis2>range[2]]<-range[2]
cis2<-cis2*20
polygon(x,cis2,border=NA,col=colb[xx],xpd=F);xx=xx+1

cis2<-c(cis_fin_colon_mal_cond[1,],rev(cis_fin_colon_mal_cond[2,]))
cis2[cis2<range[1]]<-range[1]
cis2[cis2>range[2]]<-range[2]
cis2<-cis2*20
polygon(x,cis2,border=NA,col=colb[xx],xpd=F);xx=xx+1


cis2<-c(cis_fin_colon_mal_5y[1,],rev(cis_fin_colon_mal_5y[2,]))
cis2[cis2<range[1]]<-range[1]
cis2[cis2>range[2]]<-range[2]
cis2<-cis2*20
polygon(x,cis2,border=NA,col=colb[xx],xpd=F)

xx=1
tabce4(cis3_fin_colon_mal_1y*20,cis_fin_colon_mal_1y*20)
xx=xx+1
tabce4(cis3_fin_colon_mal_cond*20,cis_fin_colon_mal_cond*20)
xx=xx+1
tabce4(cis3_fin_colon_mal_5y*20,cis_fin_colon_mal_5y*20)

axis(4,las=2,cex.axis=1.4,at=seq(range[1],range[2],by=10),labels=c(range[1],rep("",length(seq(range[1],range[2],by=10))-2),range[2]/20),pos=2020)
text(2024.5,50,"Change in survival over a year",cex=1.3,srt=270,xpd=TRUE)

axis(side=1,las=1,cex.axis=1.4,at=c(seq(1980,2020,by=10)),pos=range[1])
lines(c(1971,2020),c(range[1],range[1]))
title(xlab="Year", line=1, cex.lab=1.4,xpd=TRUE)

### colon females % ------------------------------------------------------

plot(NULL,xlim=c(1971,2020),ylim=c(range[1],range[2]),xlab="",ylab=""
     ,las=1, axes=FALSE)
rect(1971,range[2],2020,range[1],col="grey90",border=NA)
x<-10
repeat{
  lines(c(1971,2020),c(x,x),col="white")
  x=x+10;if(x>100){break}}

x<-1980
repeat{
  lines(c(x,x),c(range[1],range[2]),col="white")
  x=x+10;if(x>2020){break}}

x<-c(yreal[1:500],yreal[500:1])

xx=1
tabce3(cis3_fin_colon_fem_1y,0)
xx=xx+1
tabce3(cis3_fin_colon_fem_cond,0)
xx=xx+1
tabce3(cis3_fin_colon_fem_5y,0)

xx=1
polygon(x,cis2_colon_fin_fem_1y,border=NA,col=colb[xx],xpd=TRUE);xx=xx+1
polygon(x,cis2_colon_fin_fem_cond,border=NA,col=colb[xx],xpd=TRUE);xx=xx+1
polygon(x,cis2_colon_fin_fem_5y,border=NA,col=colb[xx],xpd=TRUE);xx=xx+1

xx=1
points(colon[colon$group=="Finland.Females",]$surv_1y~colon[colon$group=="Finland.Females",]$year
       ,pch=17,col=colc[xx],cex=1);xx=xx+1
points(colon[colon$group=="Finland.Females",]$surv_cond~colon[colon$group=="Finland.Females",]$year
       ,pch=17,col=colc[xx],cex=1);xx=xx+1
points(colon[colon$group=="Finland.Females",]$surv_5y~colon[colon$group=="Finland.Females",]$year
       ,pch=17,col=colc[xx],cex=1)
xx=1
tabce2(cis_fin_colon_fem_1y,post_colon_fin_fem_1y);xx=xx+1
tabce2(cis_fin_colon_fem_cond,post_colon_fin_fem_cond);xx=xx+1
tabce2(cis_fin_colon_fem_5y,post_colon_fin_fem_5y);xx=1

axis(2,las=2,cex.axis=1.4,at=seq(range[1],range[2],by=10),labels=c(range[1],rep("",length(seq(range[1],range[2],by=10))-2),range[2]),pos=1971)
title(ylab="Female relative survival (%)", line=0.5, cex.lab=1.4)

xx=1;yy=range[1]+scal*0.91
xpo=-17
text(1974,range[2]-0.05*scal,"d",cex=2.2)

# slope
x<-c(yreal[1:499],yreal[499:1])
cis2<-c(cis_fin_colon_fem_1y[1,],rev(cis_fin_colon_fem_1y[2,]));xx=1
cis2[cis2<range[1]]<-range[1]
cis2[cis2>range[2]]<-range[2]
cis2<-cis2*20
polygon(x,cis2,border=NA,col=colb[xx],xpd=F);xx=xx+1

cis2<-c(cis_fin_colon_fem_cond[1,],rev(cis_fin_colon_fem_cond[2,]))
cis2[cis2<range[1]]<-range[1]
cis2[cis2>range[2]]<-range[2]
cis2<-cis2*20
polygon(x,cis2,border=NA,col=colb[xx],xpd=F);xx=xx+1


cis2<-c(cis_fin_colon_fem_5y[1,],rev(cis_fin_colon_fem_5y[2,]))
cis2[cis2<range[1]]<-range[1]
cis2[cis2>range[2]]<-range[2]
cis2<-cis2*20
polygon(x,cis2,border=NA,col=colb[xx],xpd=F)

xx=1
tabce4(cis3_fin_colon_fem_1y*20,cis_fin_colon_fem_1y*20)
xx=xx+1
tabce4(cis3_fin_colon_fem_cond*20,cis_fin_colon_fem_cond*20)
xx=xx+1
tabce4(cis3_fin_colon_fem_5y*20,cis_fin_colon_fem_5y*20)

axis(4,las=2,cex.axis=1.4,at=seq(range[1],range[2],by=10),labels=c(range[1],rep("",length(seq(range[1],range[2],by=10))-2),range[2]/20),pos=2020)
text(2024.5,50,"Change in survival over a year",cex=1.3,srt=270,xpd=TRUE)

axis(side=1,las=1,cex.axis=1.4,at=c(seq(1980,2020,by=10)),pos=range[1])
lines(c(1971,2020),c(range[1],range[1]))
title(xlab="Year", line=1, cex.lab=1.4,xpd=TRUE)


### rectum males % ------------------------------------------------------

plot(NULL,xlim=c(1971,2020),ylim=c(range[1],range[2]),xlab="",ylab=""
     ,las=1, axes=FALSE)
rect(1971,range[2],2020,range[1],col="grey90",border=NA)
x<-10
repeat{
  lines(c(1971,2020),c(x,x),col="white")
  x=x+10;if(x>100){break}}

x<-1980
repeat{
  lines(c(x,x),c(range[1],range[2]),col="white")
  x=x+10;if(x>2020){break}}

x<-c(yreal[1:500],yreal[500:1])
xx=1
tabce3(cis3_fin_rectum_mal_1y,0)
xx=xx+1
tabce3(cis3_fin_rectum_mal_cond,-0.2)
xx=xx+1
tabce3(cis3_fin_rectum_mal_5y,0.2)

xx=1
polygon(x,cis2_rectum_fin_mal_1y,border=NA,col=colb[xx],xpd=TRUE);xx=xx+1
polygon(x,cis2_rectum_fin_mal_cond,border=NA,col=colb[xx],xpd=TRUE);xx=xx+1
polygon(x,cis2_rectum_fin_mal_5y,border=NA,col=colb[xx],xpd=TRUE);xx=xx+1

xx=1
points(rectum[rectum$group=="Finland.Males",]$surv_1y~rectum[rectum$group=="Finland.Males",]$year
       ,pch=17,col=colc[xx],cex=1);xx=xx+1
points(rectum[rectum$group=="Finland.Males",]$surv_cond~rectum[rectum$group=="Finland.Males",]$year
       ,pch=17,col=colc[xx],cex=1);xx=xx+1
points(rectum[rectum$group=="Finland.Males",]$surv_5y~rectum[rectum$group=="Finland.Males",]$year
       ,pch=17,col=colc[xx],cex=1)
xx=1
tabce2(cis_fin_rectum_mal_1y,post_rectum_fin_mal_1y);xx=xx+1
tabce2(cis_fin_rectum_mal_cond,post_rectum_fin_mal_cond);xx=xx+1
tabce2(cis_fin_rectum_mal_5y,post_rectum_fin_mal_5y);xx=1


axis(2,las=2,cex.axis=1.4,at=seq(range[1],range[2],by=10),labels=c(range[1],rep("",length(seq(range[1],range[2],by=10))-2),range[2]),pos=1971)
title(ylab="Male relative survival (%)", line=0.5, cex.lab=1.4)
text(1974,range[2]-0.05*scal,"b",cex=2.2)

# slope
x<-c(yreal[1:499],yreal[499:1])
cis2<-c(cis_fin_rectum_mal_1y[1,],rev(cis_fin_rectum_mal_1y[2,]));xx=1
cis2[cis2<range[1]]<-range[1]
cis2[cis2>range[2]]<-range[2]
cis2<-cis2*20
polygon(x,cis2,border=NA,col=colb[xx],xpd=F);xx=xx+1

cis2<-c(cis_fin_rectum_mal_cond[1,],rev(cis_fin_rectum_mal_cond[2,]))
cis2[cis2<range[1]]<-range[1]
cis2[cis2>range[2]]<-range[2]
cis2<-cis2*20
polygon(x,cis2,border=NA,col=colb[xx],xpd=F);xx=xx+1


cis2<-c(cis_fin_rectum_mal_5y[1,],rev(cis_fin_rectum_mal_5y[2,]))
cis2[cis2<range[1]]<-range[1]
cis2[cis2>range[2]]<-range[2]
cis2<-cis2*20
polygon(x,cis2,border=NA,col=colb[xx],xpd=F)

xx=1
tabce4(cis3_fin_rectum_mal_1y*20,cis_fin_rectum_mal_1y*20)
xx=xx+1
tabce4(cis3_fin_rectum_mal_cond*20,cis_fin_rectum_mal_cond*20)
xx=xx+1
tabce4(cis3_fin_rectum_mal_5y*20,cis_fin_rectum_mal_5y*20)

axis(4,las=2,cex.axis=1.4,at=seq(range[1],range[2],by=10),labels=c(range[1],rep("",length(seq(range[1],range[2],by=10))-2),range[2]/20),pos=2020)
text(2024.5,50,"Change in survival over a year",cex=1.3,srt=270,xpd=TRUE)

axis(side=1,las=1,cex.axis=1.4,at=c(seq(1980,2020,by=10)),pos=range[1])
lines(c(1971,2020),c(range[1],range[1]))
title(xlab="Year", line=1, cex.lab=1.4,xpd=TRUE)


### rectum females % ------------------------------------------------------

plot(NULL,xlim=c(1971,2020),ylim=c(range[1],range[2]),xlab="",ylab=""
     ,las=1, axes=FALSE)
rect(1971,range[2],2020,range[1],col="grey90",border=NA)
x<-10
repeat{
  lines(c(1971,2020),c(x,x),col="white")
  x=x+10;if(x>100){break}}

x<-1980
repeat{
  lines(c(x,x),c(range[1],range[2]),col="white")
  x=x+10;if(x>2020){break}}

x<-c(yreal[1:500],yreal[500:1])
xx=1
tabce3(cis3_fin_rectum_fem_1y,0)
xx=xx+1
tabce3(cis3_fin_rectum_fem_cond,0)
xx=xx+1
tabce3(cis3_fin_rectum_fem_5y,0)
xx=1
polygon(x,cis2_rectum_fin_fem_1y,border=NA,col=colb[xx],xpd=TRUE);xx=xx+1
polygon(x,cis2_rectum_fin_fem_cond,border=NA,col=colb[xx],xpd=TRUE);xx=xx+1
polygon(x,cis2_rectum_fin_fem_5y,border=NA,col=colb[xx],xpd=TRUE);xx=xx+1

xx=1
points(rectum[rectum$group=="Finland.Females",]$surv_1y~rectum[rectum$group=="Finland.Females",]$year
       ,pch=17,col=colc[xx],cex=1);xx=xx+1
points(rectum[rectum$group=="Finland.Females",]$surv_cond~rectum[rectum$group=="Finland.Females",]$year
       ,pch=17,col=colc[xx],cex=1);xx=xx+1
points(rectum[rectum$group=="Finland.Females",]$surv_5y~rectum[rectum$group=="Finland.Females",]$year
       ,pch=17,col=colc[xx],cex=1)
xx=1
tabce2(cis_fin_rectum_fem_1y,post_rectum_fin_fem_1y);xx=xx+1
tabce2(cis_fin_rectum_fem_cond,post_rectum_fin_fem_cond);xx=xx+1
tabce2(cis_fin_rectum_fem_5y,post_rectum_fin_fem_5y);xx=1


axis(2,las=2,cex.axis=1.4,at=seq(range[1],range[2],by=10),labels=c(range[1],rep("",length(seq(range[1],range[2],by=10))-2),range[2]),pos=1971)
title(ylab="Female relative survival (%)", line=0.5, cex.lab=1.4)
text(1974,range[2]-0.05*scal,"e",cex=2.2)

# slope
x<-c(yreal[1:499],yreal[499:1])
cis2<-c(cis_fin_rectum_fem_1y[1,],rev(cis_fin_rectum_fem_1y[2,]));xx=1
cis2[cis2<range[1]]<-range[1]
cis2[cis2>range[2]]<-range[2]
cis2<-cis2*20
polygon(x,cis2,border=NA,col=colb[xx],xpd=F);xx=xx+1

cis2<-c(cis_fin_rectum_fem_cond[1,],rev(cis_fin_rectum_fem_cond[2,]))
cis2[cis2<range[1]]<-range[1]
cis2[cis2>range[2]]<-range[2]
cis2<-cis2*20
polygon(x,cis2,border=NA,col=colb[xx],xpd=F);xx=xx+1


cis2<-c(cis_fin_rectum_fem_5y[1,],rev(cis_fin_rectum_fem_5y[2,]))
cis2[cis2<range[1]]<-range[1]
cis2[cis2>range[2]]<-range[2]
cis2<-cis2*20
polygon(x,cis2,border=NA,col=colb[xx],xpd=F)

xx=1
tabce4(cis3_fin_rectum_fem_1y*20,cis_fin_rectum_fem_1y*20)
xx=xx+1
tabce4(cis3_fin_rectum_fem_cond*20,cis_fin_rectum_fem_cond*20)
xx=xx+1
tabce4(cis3_fin_rectum_fem_5y*20,cis_fin_rectum_fem_5y*20)

axis(4,las=2,cex.axis=1.4,at=seq(range[1],range[2],by=10),labels=c(range[1],rep("",length(seq(range[1],range[2],by=10))-2),range[2]/20),pos=2020)
text(2024.5,50,"Change in survival over a year",cex=1.3,srt=270,xpd=TRUE)

axis(side=1,las=1,cex.axis=1.4,at=c(seq(1980,2020,by=10)),pos=range[1])
lines(c(1971,2020),c(range[1],range[1]))
title(xlab="Year", line=1, cex.lab=1.4,xpd=TRUE)


### small_intestine males % ------------------------------------------------------

plot(NULL,xlim=c(1971,2020),ylim=c(range[1],range[2]),xlab="",ylab=""
     ,las=1, axes=FALSE)
rect(1971,range[2],2020,range[1],col="grey90",border=NA)
x<-10
repeat{
  lines(c(1971,2020),c(x,x),col="white")
  x=x+10;if(x>100){break}}

x<-1980
repeat{
  lines(c(x,x),c(range[1],range[2]),col="white")
  x=x+10;if(x>2020){break}}

x<-c(yreal[1:500],yreal[500:1])
xx=1
tabce3(cis3_fin_small_intestine_mal_1y,0)
xx=xx+1
tabce3(cis3_fin_small_intestine_mal_cond,0)
xx=xx+1
tabce3(cis3_fin_small_intestine_mal_5y,0)

xx=1
polygon(x,cis2_small_intestine_fin_mal_1y,border=NA,col=colb[xx],xpd=TRUE);xx=xx+1
polygon(x,cis2_small_intestine_fin_mal_cond,border=NA,col=colb[xx],xpd=TRUE);xx=xx+1
polygon(x,cis2_small_intestine_fin_mal_5y,border=NA,col=colb[xx],xpd=TRUE);xx=xx+1

xx=1
points(small_intestine[small_intestine$group=="Finland.Males",]$surv_1y~small_intestine[small_intestine$group=="Finland.Males",]$year
       ,pch=17,col=colc[xx],cex=1);xx=xx+1
points(small_intestine[small_intestine$group=="Finland.Males",]$surv_cond~small_intestine[small_intestine$group=="Finland.Males",]$year
       ,pch=17,col=colc[xx],cex=1);xx=xx+1
points(small_intestine[small_intestine$group=="Finland.Males",]$surv_5y~small_intestine[small_intestine$group=="Finland.Males",]$year
       ,pch=17,col=colc[xx],cex=1)
xx=1
tabce2(cis_fin_small_intestine_mal_1y,post_small_intestine_fin_mal_1y);xx=xx+1
tabce2(cis_fin_small_intestine_mal_cond,post_small_intestine_fin_mal_cond);xx=xx+1
tabce2(cis_fin_small_intestine_mal_5y,post_small_intestine_fin_mal_5y);xx=1


axis(2,las=2,cex.axis=1.4,at=seq(range[1],range[2],by=10),labels=c(range[1],rep("",length(seq(range[1],range[2],by=10))-2),range[2]),pos=1971)
title(ylab="Male relative survival (%)", line=0.5, cex.lab=1.4)
axis(side=1,las=1,cex.axis=1.4,at=c(seq(1980,2020,by=10)),pos=range[1])
lines(c(1971,2020),c(range[1],range[1]))
title(xlab="Year", line=1, cex.lab=1.4,xpd=TRUE)
text(1974,range[2]-0.05*scal,"c",cex=2.2)

ypo=-78
xfl=48
rect(1956+xfl,range[1]+scal*0.965+ypo,1968+xfl,range[1]+scal*0.84+ypo,col="white",border="grey50")
rect(1956+xfl,range[1]+scal*0.9135+ypo,1968+xfl,range[1]+scal*0.8865+ypo,col="dodgerblue3",border=NA)
rect(1960+xfl,range[1]+scal*0.965+ypo,1962+xfl,range[1]+scal*0.84+ypo,col="dodgerblue3",border=NA)


### small_intestine females % ------------------------------------------------------

plot(NULL,xlim=c(1971,2020),ylim=c(range[1],range[2]),xlab="",ylab=""
     ,las=1, axes=FALSE)
rect(1971,range[2],2020,range[1],col="grey90",border=NA)
x<-10
repeat{
  lines(c(1971,2020),c(x,x),col="white")
  x=x+10;if(x>100){break}}

x<-1980
repeat{
  lines(c(x,x),c(range[1],range[2]),col="white")
  x=x+10;if(x>2020){break}}

x<-c(yreal[1:500],yreal[500:1])
xx=1
tabce3(cis3_fin_small_intestine_fem_1y,0)
xx=xx+1
tabce3(cis3_fin_small_intestine_fem_cond,0)
xx=xx+1
tabce3(cis3_fin_small_intestine_fem_5y,0)
xx=1
polygon(x,cis2_small_intestine_fin_fem_1y,border=NA,col=colb[xx],xpd=TRUE);xx=xx+1
polygon(x,cis2_small_intestine_fin_fem_cond,border=NA,col=colb[xx],xpd=TRUE);xx=xx+1
polygon(x,cis2_small_intestine_fin_fem_5y,border=NA,col=colb[xx],xpd=TRUE);xx=xx+1

xx=1
points(small_intestine[small_intestine$group=="Finland.Females",]$surv_1y~small_intestine[small_intestine$group=="Finland.Females",]$year
       ,pch=17,col=colc[xx],cex=1);xx=xx+1
points(small_intestine[small_intestine$group=="Finland.Females",]$surv_cond~small_intestine[small_intestine$group=="Finland.Females",]$year
       ,pch=17,col=colc[xx],cex=1);xx=xx+1
points(small_intestine[small_intestine$group=="Finland.Females",]$surv_5y~small_intestine[small_intestine$group=="Finland.Females",]$year
       ,pch=17,col=colc[xx],cex=1)
xx=1
tabce2(cis_fin_small_intestine_fem_1y,post_small_intestine_fin_fem_1y);xx=xx+1
tabce2(cis_fin_small_intestine_fem_cond,post_small_intestine_fin_fem_cond);xx=xx+1
tabce2(cis_fin_small_intestine_fem_5y,post_small_intestine_fin_fem_5y);xx=1

axis(2,las=2,cex.axis=1.4,at=seq(range[1],range[2],by=10),labels=c(range[1],rep("",length(seq(range[1],range[2],by=10))-2),range[2]),pos=1971)
title(ylab="Female relative survival (%)", line=0.5, cex.lab=1.4)
axis(side=1,las=1,cex.axis=1.4,at=c(seq(1980,2020,by=10)),pos=range[1])
lines(c(1971,2020),c(range[1],range[1]))
title(xlab="Year", line=1, cex.lab=1.4,xpd=TRUE)

text(1974,range[2]-0.05*scal,"f",cex=2.2)
```


### Fig. 3 - Norway
```{r,fig.height=6.9,fig.width=8,error=TRUE,warning=FALSE,results=FALSE,message=FALSE}
## NOR figures -----------------
m <- matrix(c(1,2,3
              ,4,6,8
              ,5,7,9), nrow = 3, ncol =3 ,byrow = TRUE)
layout(mat = m,heights = c(0.06,1-0.06))
par(mgp=c(1.6,0.8,0))
par(mar=c(0,0,0,0))
range<-c(0,100);scal<-range[2]-range[1]

plot(NULL, axes=FALSE,xlab="",ylab="",xlim=c(-1,1),ylim=c(-0.85,0.85))
text(0,-0.2,"Colon cancer",cex=1.6,font=3,xpd=TRUE)

plot(NULL, axes=FALSE,xlab="",ylab="",xlim=c(-1,1),ylim=c(-0.85,0.85))
text(0,-0.2,"Rectal cancer",cex=1.6,font=3,xpd=TRUE)

plot(NULL, axes=FALSE,xlab="",ylab="",xlim=c(-1,1),ylim=c(-0.85,0.85))
text(0,-0.2,"Small intestine cancer",cex=1.6,font=3,xpd=TRUE)


par(mgp=c(1.6,0.8,0))
par(mar=c(2,2.5,0,2))

### colon males % ------------------------------------------------------

plot(NULL,xlim=c(1971,2020),ylim=c(range[1],range[2]),xlab="",ylab=""
     ,las=1, axes=FALSE)
rect(1971,range[2],2020,range[1],col="grey90",border=NA)
x<-10
repeat{
  lines(c(1971,2020),c(x,x),col="white")
  x=x+10;if(x>100){break}}

x<-1980
repeat{
  lines(c(x,x),c(range[1],range[2]),col="white")
  x=x+10;if(x>2020){break}}

x<-c(yreal[1:500],yreal[500:1])

xx=1
tabce3(cis3_nor_colon_mal_1y,0)
xx=xx+1
tabce3(cis3_nor_colon_mal_cond,0)
xx=xx+1
tabce3(cis3_nor_colon_mal_5y,0)

xx=1
polygon(x,cis2_colon_nor_mal_1y,border=NA,col=colb[xx],xpd=TRUE);xx=xx+1
polygon(x,cis2_colon_nor_mal_cond,border=NA,col=colb[xx],xpd=TRUE);xx=xx+1
polygon(x,cis2_colon_nor_mal_5y,border=NA,col=colb[xx],xpd=TRUE)

xx=1
points(colon[colon$group=="Norway.Males",]$surv_1y~colon[colon$group=="Norway.Males",]$year
       ,pch=17,col=colc[xx],cex=1);xx=xx+1
points(colon[colon$group=="Norway.Males",]$surv_cond~colon[colon$group=="Norway.Males",]$year
       ,pch=17,col=colc[xx],cex=1);xx=xx+1
points(colon[colon$group=="Norway.Males",]$surv_5y~colon[colon$group=="Norway.Males",]$year
       ,pch=17,col=colc[xx],cex=1)
xx=1
tabce2(cis_nor_colon_mal_1y,post_colon_nor_mal_1y);xx=xx+1
tabce2(cis_nor_colon_mal_cond,post_colon_nor_mal_cond);xx=xx+1
tabce2(cis_nor_colon_mal_5y,post_colon_nor_mal_5y);xx=1


axis(2,las=2,cex.axis=1.4,at=seq(range[1],range[2],by=10),labels=c(range[1],rep("",length(seq(range[1],range[2],by=10))-2),range[2]),pos=1971)
title(ylab="Male relative survival (%)", line=0.5, cex.lab=1.4)

xx=1;yy=range[1]+scal*0.37
xpo=-1
rect(1996+xpo,yy+0.035*scal,2017.9+xpo,yy-0.15*scal,col="white",border="grey50",lwd=0.8)
repeat{
  points(2000+xpo,yy,pch=17,col=cola[xx],cex=1.2)
  lines(c(1997+xpo,2003+xpo),c(yy,yy),lwd=1.6,col=cola[xx],lend=1)
  xx<-xx+1;yy=yy-(scal*0.058);if(xx>3){break}}
xx=1;yy=range[1]+scal*0.37
text(2010+xpo,yy,"1-year",col=cola[xx],cex=1.25);xx=xx+1;yy=yy-(scal*0.058)
text(2010+xpo,yy,"5/1-year",col=cola[xx],cex=1.25);xx=xx+1;yy=yy-(scal*0.058)
text(2010+xpo,yy,"5-year",col=cola[xx],cex=1.25);xx=xx+1;yy=yy-(scal*0.058)
text(1974,range[2]-0.05*scal,"a",cex=2.2)

# slope
x<-c(yreal[1:499],yreal[499:1])
cis2<-c(cis_nor_colon_mal_1y[1,],rev(cis_nor_colon_mal_1y[2,]));xx=1
cis2[cis2<range[1]]<-range[1]
cis2[cis2>range[2]]<-range[2]
cis2<-cis2*20
polygon(x,cis2,border=NA,col=colb[xx],xpd=F);xx=xx+1

cis2<-c(cis_nor_colon_mal_cond[1,],rev(cis_nor_colon_mal_cond[2,]))
cis2[cis2<range[1]]<-range[1]
cis2[cis2>range[2]]<-range[2]
cis2<-cis2*20
polygon(x,cis2,border=NA,col=colb[xx],xpd=F);xx=xx+1


cis2<-c(cis_nor_colon_mal_5y[1,],rev(cis_nor_colon_mal_5y[2,]))
cis2[cis2<range[1]]<-range[1]
cis2[cis2>range[2]]<-range[2]
cis2<-cis2*20
polygon(x,cis2,border=NA,col=colb[xx],xpd=F)

xx=1
tabce4(cis3_nor_colon_mal_1y*20,cis_nor_colon_mal_1y*20)
xx=xx+1
tabce4(cis3_nor_colon_mal_cond*20,cis_nor_colon_mal_cond*20)
xx=xx+1
tabce4(cis3_nor_colon_mal_5y*20,cis_nor_colon_mal_5y*20)

axis(4,las=2,cex.axis=1.4,at=seq(range[1],range[2],by=10),labels=c(range[1],rep("",length(seq(range[1],range[2],by=10))-2),range[2]/20),pos=2020)
text(2024.5,50,"Change in survival over a year",cex=1.3,srt=270,xpd=TRUE)

axis(side=1,las=1,cex.axis=1.4,at=c(seq(1980,2020,by=10)),pos=range[1])
lines(c(1971,2020),c(range[1],range[1]))
title(xlab="Year", line=1, cex.lab=1.4,xpd=TRUE)



### colon females % ------------------------------------------------------

plot(NULL,xlim=c(1971,2020),ylim=c(range[1],range[2]),xlab="",ylab=""
     ,las=1, axes=FALSE)
rect(1971,range[2],2020,range[1],col="grey90",border=NA)
x<-10
repeat{
  lines(c(1971,2020),c(x,x),col="white")
  x=x+10;if(x>100){break}}

x<-1980
repeat{
  lines(c(x,x),c(range[1],range[2]),col="white")
  x=x+10;if(x>2020){break}}

x<-c(yreal[1:500],yreal[500:1])
xx=1
tabce3(cis3_nor_colon_fem_1y,0)
xx=xx+1
tabce3(cis3_nor_colon_fem_cond,0)
xx=xx+1
tabce3(cis3_nor_colon_fem_5y,0)

xx=1
polygon(x,cis2_colon_nor_fem_1y,border=NA,col=colb[xx],xpd=TRUE);xx=xx+1
polygon(x,cis2_colon_nor_fem_cond,border=NA,col=colb[xx],xpd=TRUE);xx=xx+1
polygon(x,cis2_colon_nor_fem_5y,border=NA,col=colb[xx],xpd=TRUE);xx=xx+1

xx=1
points(colon[colon$group=="Norway.Females",]$surv_1y~colon[colon$group=="Norway.Females",]$year
       ,pch=17,col=colc[xx],cex=1);xx=xx+1
points(colon[colon$group=="Norway.Females",]$surv_cond~colon[colon$group=="Norway.Females",]$year
       ,pch=17,col=colc[xx],cex=1);xx=xx+1
points(colon[colon$group=="Norway.Females",]$surv_5y~colon[colon$group=="Norway.Females",]$year
       ,pch=17,col=colc[xx],cex=1)
xx=1
tabce2(cis_nor_colon_fem_1y,post_colon_nor_fem_1y);xx=xx+1
tabce2(cis_nor_colon_fem_cond,post_colon_nor_fem_cond);xx=xx+1
tabce2(cis_nor_colon_fem_5y,post_colon_nor_fem_5y);xx=1

axis(2,las=2,cex.axis=1.4,at=seq(range[1],range[2],by=10),labels=c(range[1],rep("",length(seq(range[1],range[2],by=10))-2),range[2]),pos=1971)
title(ylab="Female relative survival (%)", line=0.5, cex.lab=1.4)

xx=1;yy=range[1]+scal*0.91
xpo=-17
text(1974,range[2]-0.05*scal,"d",cex=2.2)

# slope
x<-c(yreal[1:499],yreal[499:1])
cis2<-c(cis_nor_colon_fem_1y[1,],rev(cis_nor_colon_fem_1y[2,]));xx=1
cis2[cis2<range[1]]<-range[1]
cis2[cis2>range[2]]<-range[2]
cis2<-cis2*20
polygon(x,cis2,border=NA,col=colb[xx],xpd=F);xx=xx+1

cis2<-c(cis_nor_colon_fem_cond[1,],rev(cis_nor_colon_fem_cond[2,]))
cis2[cis2<range[1]]<-range[1]
cis2[cis2>range[2]]<-range[2]
cis2<-cis2*20
polygon(x,cis2,border=NA,col=colb[xx],xpd=F);xx=xx+1


cis2<-c(cis_nor_colon_fem_5y[1,],rev(cis_nor_colon_fem_5y[2,]))
cis2[cis2<range[1]]<-range[1]
cis2[cis2>range[2]]<-range[2]
cis2<-cis2*20
polygon(x,cis2,border=NA,col=colb[xx],xpd=F)

xx=1
tabce4(cis3_nor_colon_fem_1y*20,cis_nor_colon_fem_1y*20)
xx=xx+1
tabce4(cis3_nor_colon_fem_cond*20,cis_nor_colon_fem_cond*20)
xx=xx+1
tabce4(cis3_nor_colon_fem_5y*20,cis_nor_colon_fem_5y*20)

axis(4,las=2,cex.axis=1.4,at=seq(range[1],range[2],by=10),labels=c(range[1],rep("",length(seq(range[1],range[2],by=10))-2),range[2]/20),pos=2020)
text(2024.5,50,"Change in survival over a year",cex=1.3,srt=270,xpd=TRUE)

axis(side=1,las=1,cex.axis=1.4,at=c(seq(1980,2020,by=10)),pos=range[1])
lines(c(1971,2020),c(range[1],range[1]))
title(xlab="Year", line=1, cex.lab=1.4,xpd=TRUE)



### rectum males % ------------------------------------------------------

plot(NULL,xlim=c(1971,2020),ylim=c(range[1],range[2]),xlab="",ylab=""
     ,las=1, axes=FALSE)
rect(1971,range[2],2020,range[1],col="grey90",border=NA)
x<-10
repeat{
  lines(c(1971,2020),c(x,x),col="white")
  x=x+10;if(x>100){break}}

x<-1980
repeat{
  lines(c(x,x),c(range[1],range[2]),col="white")
  x=x+10;if(x>2020){break}}




x<-c(yreal[1:500],yreal[500:1])

xx=1
tabce3(cis3_nor_rectum_mal_1y,0)
xx=xx+1
tabce3(cis3_nor_rectum_mal_cond,0)
xx=xx+1
tabce3(cis3_nor_rectum_mal_5y,0)

xx=1
polygon(x,cis2_rectum_nor_mal_1y,border=NA,col=colb[xx],xpd=TRUE);xx=xx+1
polygon(x,cis2_rectum_nor_mal_cond,border=NA,col=colb[xx],xpd=TRUE);xx=xx+1
polygon(x,cis2_rectum_nor_mal_5y,border=NA,col=colb[xx],xpd=TRUE);xx=xx+1

xx=1
points(rectum[rectum$group=="Norway.Males",]$surv_1y~rectum[rectum$group=="Norway.Males",]$year
       ,pch=17,col=colc[xx],cex=1);xx=xx+1
points(rectum[rectum$group=="Norway.Males",]$surv_cond~rectum[rectum$group=="Norway.Males",]$year
       ,pch=17,col=colc[xx],cex=1);xx=xx+1
points(rectum[rectum$group=="Norway.Males",]$surv_5y~rectum[rectum$group=="Norway.Males",]$year
       ,pch=17,col=colc[xx],cex=1)
xx=1
tabce2(cis_nor_rectum_mal_1y,post_rectum_nor_mal_1y);xx=xx+1
tabce2(cis_nor_rectum_mal_cond,post_rectum_nor_mal_cond);xx=xx+1
tabce2(cis_nor_rectum_mal_5y,post_rectum_nor_mal_5y);xx=1

axis(2,las=2,cex.axis=1.4,at=seq(range[1],range[2],by=10),labels=c(range[1],rep("",length(seq(range[1],range[2],by=10))-2),range[2]),pos=1971)
title(ylab="Male relative survival (%)", line=0.5, cex.lab=1.4)
text(1974,range[2]-0.05*scal,"b",cex=2.2)

# slope
x<-c(yreal[1:499],yreal[499:1])
cis2<-c(cis_nor_rectum_mal_1y[1,],rev(cis_nor_rectum_mal_1y[2,]));xx=1
cis2[cis2<range[1]]<-range[1]
cis2[cis2>range[2]]<-range[2]
cis2<-cis2*20
polygon(x,cis2,border=NA,col=colb[xx],xpd=F);xx=xx+1

cis2<-c(cis_nor_rectum_mal_cond[1,],rev(cis_nor_rectum_mal_cond[2,]))
cis2[cis2<range[1]]<-range[1]
cis2[cis2>range[2]]<-range[2]
cis2<-cis2*20
polygon(x,cis2,border=NA,col=colb[xx],xpd=F);xx=xx+1


cis2<-c(cis_nor_rectum_mal_5y[1,],rev(cis_nor_rectum_mal_5y[2,]))
cis2[cis2<range[1]]<-range[1]
cis2[cis2>range[2]]<-range[2]
cis2<-cis2*20
polygon(x,cis2,border=NA,col=colb[xx],xpd=F)

xx=1
tabce4(cis3_nor_rectum_mal_1y*20,cis_nor_rectum_mal_1y*20)
xx=xx+1
tabce4(cis3_nor_rectum_mal_cond*20,cis_nor_rectum_mal_cond*20)
xx=xx+1
tabce4(cis3_nor_rectum_mal_5y*20,cis_nor_rectum_mal_5y*20)

axis(4,las=2,cex.axis=1.4,at=seq(range[1],range[2],by=10),labels=c(range[1],rep("",length(seq(range[1],range[2],by=10))-2),range[2]/20),pos=2020)
text(2024.5,50,"Change in survival over a year",cex=1.3,srt=270,xpd=TRUE)

axis(side=1,las=1,cex.axis=1.4,at=c(seq(1980,2020,by=10)),pos=range[1])
lines(c(1971,2020),c(range[1],range[1]))
title(xlab="Year", line=1, cex.lab=1.4,xpd=TRUE)




### rectum females % ------------------------------------------------------

plot(NULL,xlim=c(1971,2020),ylim=c(range[1],range[2]),xlab="",ylab=""
     ,las=1, axes=FALSE)
rect(1971,range[2],2020,range[1],col="grey90",border=NA)
x<-10
repeat{
  lines(c(1971,2020),c(x,x),col="white")
  x=x+10;if(x>100){break}}

x<-1980
repeat{
  lines(c(x,x),c(range[1],range[2]),col="white")
  x=x+10;if(x>2020){break}}

x<-c(yreal[1:500],yreal[500:1])

xx=1
tabce3(cis3_nor_rectum_fem_1y,0)
xx=xx+1
tabce3(cis3_nor_rectum_fem_cond,0)
xx=xx+1
tabce3(cis3_nor_rectum_fem_5y,0)


xx=1
polygon(x,cis2_rectum_nor_fem_1y,border=NA,col=colb[xx],xpd=TRUE);xx=xx+1
polygon(x,cis2_rectum_nor_fem_cond,border=NA,col=colb[xx],xpd=TRUE);xx=xx+1
polygon(x,cis2_rectum_nor_fem_5y,border=NA,col=colb[xx],xpd=TRUE);xx=xx+1

xx=1
points(rectum[rectum$group=="Norway.Females",]$surv_1y~rectum[rectum$group=="Norway.Females",]$year
       ,pch=17,col=colc[xx],cex=1);xx=xx+1
points(rectum[rectum$group=="Norway.Females",]$surv_cond~rectum[rectum$group=="Norway.Females",]$year
       ,pch=17,col=colc[xx],cex=1);xx=xx+1
points(rectum[rectum$group=="Norway.Females",]$surv_5y~rectum[rectum$group=="Norway.Females",]$year
       ,pch=17,col=colc[xx],cex=1)
xx=1
tabce2(cis_nor_rectum_fem_1y,post_rectum_nor_fem_1y);xx=xx+1
tabce2(cis_nor_rectum_fem_cond,post_rectum_nor_fem_cond);xx=xx+1
tabce2(cis_nor_rectum_fem_5y,post_rectum_nor_fem_5y);xx=1

axis(2,las=2,cex.axis=1.4,at=seq(range[1],range[2],by=10),labels=c(range[1],rep("",length(seq(range[1],range[2],by=10))-2),range[2]),pos=1971)
title(ylab="Female relative survival (%)", line=0.5, cex.lab=1.4)
text(1974,range[2]-0.05*scal,"e",cex=2.2)

# slope
x<-c(yreal[1:499],yreal[499:1])
cis2<-c(cis_nor_rectum_fem_1y[1,],rev(cis_nor_rectum_fem_1y[2,]));xx=1
cis2[cis2<range[1]]<-range[1]
cis2[cis2>range[2]]<-range[2]
cis2<-cis2*20
polygon(x,cis2,border=NA,col=colb[xx],xpd=F);xx=xx+1

cis2<-c(cis_nor_rectum_fem_cond[1,],rev(cis_nor_rectum_fem_cond[2,]))
cis2[cis2<range[1]]<-range[1]
cis2[cis2>range[2]]<-range[2]
cis2<-cis2*20
polygon(x,cis2,border=NA,col=colb[xx],xpd=F);xx=xx+1


cis2<-c(cis_nor_rectum_fem_5y[1,],rev(cis_nor_rectum_fem_5y[2,]))
cis2[cis2<range[1]]<-range[1]
cis2[cis2>range[2]]<-range[2]
cis2<-cis2*20
polygon(x,cis2,border=NA,col=colb[xx],xpd=F)

xx=1
tabce4(cis3_nor_rectum_fem_1y*20,cis_nor_rectum_fem_1y*20)
xx=xx+1
tabce4(cis3_nor_rectum_fem_cond*20,cis_nor_rectum_fem_cond*20)
xx=xx+1
tabce4(cis3_nor_rectum_fem_5y*20,cis_nor_rectum_fem_5y*20)

axis(4,las=2,cex.axis=1.4,at=seq(range[1],range[2],by=10),labels=c(range[1],rep("",length(seq(range[1],range[2],by=10))-2),range[2]/20),pos=2020)
text(2024.5,50,"Change in survival over a year",cex=1.3,srt=270,xpd=TRUE)

axis(side=1,las=1,cex.axis=1.4,at=c(seq(1980,2020,by=10)),pos=range[1])
lines(c(1971,2020),c(range[1],range[1]))
title(xlab="Year", line=1, cex.lab=1.4,xpd=TRUE)



### small_intestine males % ------------------------------------------------------

plot(NULL,xlim=c(1971,2020),ylim=c(range[1],range[2]),xlab="",ylab=""
     ,las=1, axes=FALSE)
rect(1971,range[2],2020,range[1],col="grey90",border=NA)
x<-10
repeat{
  lines(c(1971,2020),c(x,x),col="white")
  x=x+10;if(x>100){break}}

x<-1980
repeat{
  lines(c(x,x),c(range[1],range[2]),col="white")
  x=x+10;if(x>2020){break}}

x<-c(yreal[1:500],yreal[500:1])

xx=1
tabce3(cis3_nor_small_intestine_mal_1y,0)
xx=xx+1
tabce3(cis3_nor_small_intestine_mal_cond,0)
xx=xx+1
tabce3(cis3_nor_small_intestine_mal_5y,0)

xx=1
polygon(x,cis2_small_intestine_nor_mal_1y,border=NA,col=colb[xx],xpd=TRUE);xx=xx+1
polygon(x,cis2_small_intestine_nor_mal_cond,border=NA,col=colb[xx],xpd=TRUE);xx=xx+1
polygon(x,cis2_small_intestine_nor_mal_5y,border=NA,col=colb[xx],xpd=TRUE);xx=xx+1

xx=1
points(small_intestine[small_intestine$group=="Norway.Males",]$surv_1y~small_intestine[small_intestine$group=="Norway.Males",]$year
       ,pch=17,col=colc[xx],cex=1);xx=xx+1
points(small_intestine[small_intestine$group=="Norway.Males",]$surv_cond~small_intestine[small_intestine$group=="Norway.Males",]$year
       ,pch=17,col=colc[xx],cex=1);xx=xx+1
points(small_intestine[small_intestine$group=="Norway.Males",]$surv_5y~small_intestine[small_intestine$group=="Norway.Males",]$year
       ,pch=17,col=colc[xx],cex=1)
xx=1
tabce2(cis_nor_small_intestine_mal_1y,post_small_intestine_nor_mal_1y);xx=xx+1
tabce2(cis_nor_small_intestine_mal_cond,post_small_intestine_nor_mal_cond);xx=xx+1
tabce2(cis_nor_small_intestine_mal_5y,post_small_intestine_nor_mal_5y);xx=1


axis(2,las=2,cex.axis=1.4,at=seq(range[1],range[2],by=10),labels=c(range[1],rep("",length(seq(range[1],range[2],by=10))-2),range[2]),pos=1971)
title(ylab="Male relative survival (%)", line=0.5, cex.lab=1.4)
axis(side=1,las=1,cex.axis=1.4,at=c(seq(1980,2020,by=10)),pos=range[1])
lines(c(1971,2020),c(range[1],range[1]))
title(xlab="Year", line=1, cex.lab=1.4,xpd=TRUE)
text(1974,range[2]-0.05*scal,"c",cex=2.2)

ypo=-78
xfl=48
rect(1956+xfl,range[1]+scal*0.965+ypo,1968+xfl,range[1]+scal*0.84+ypo,col="red2",border="grey50")
rect(1956+xfl,range[1]+scal*0.9285+ypo,1968+xfl,range[1]+scal*0.8735+ypo,col="white",border=NA)
rect(1959+xfl,range[1]+scal*0.965+ypo,1963+xfl,range[1]+scal*0.84+ypo,col="white",border=NA)
rect(1956+xfl,range[1]+scal*0.9135+ypo,1968+xfl,range[1]+scal*0.8865+ypo,col="darkblue",border=NA)
rect(1960+xfl,range[1]+scal*0.965+ypo,1962+xfl,range[1]+scal*0.84+ypo,col="darkblue",border=NA)

### small_intestine females % ------------------------------------------------------

plot(NULL,xlim=c(1971,2020),ylim=c(range[1],range[2]),xlab="",ylab=""
     ,las=1, axes=FALSE)
rect(1971,range[2],2020,range[1],col="grey90",border=NA)
x<-10
repeat{
  lines(c(1971,2020),c(x,x),col="white")
  x=x+10;if(x>100){break}}

x<-1980
repeat{
  lines(c(x,x),c(range[1],range[2]),col="white")
  x=x+10;if(x>2020){break}}

x<-c(yreal[1:500],yreal[500:1])

xx=1
tabce3(cis3_nor_small_intestine_fem_1y,0)
xx=xx+1
tabce3(cis3_nor_small_intestine_fem_cond,0)
xx=xx+1
tabce3(cis3_nor_small_intestine_fem_5y,0)

xx=1
polygon(x,cis2_small_intestine_nor_fem_1y,border=NA,col=colb[xx],xpd=TRUE);xx=xx+1
polygon(x,cis2_small_intestine_nor_fem_cond,border=NA,col=colb[xx],xpd=TRUE);xx=xx+1
polygon(x,cis2_small_intestine_nor_fem_5y,border=NA,col=colb[xx],xpd=TRUE);xx=xx+1

xx=1
points(small_intestine[small_intestine$group=="Norway.Females",]$surv_1y~small_intestine[small_intestine$group=="Norway.Females",]$year
       ,pch=17,col=colc[xx],cex=1);xx=xx+1
points(small_intestine[small_intestine$group=="Norway.Females",]$surv_cond~small_intestine[small_intestine$group=="Norway.Females",]$year
       ,pch=17,col=colc[xx],cex=1);xx=xx+1
points(small_intestine[small_intestine$group=="Norway.Females",]$surv_5y~small_intestine[small_intestine$group=="Norway.Females",]$year
       ,pch=17,col=colc[xx],cex=1)
xx=1
tabce2(cis_nor_small_intestine_fem_1y,post_small_intestine_nor_fem_1y);xx=xx+1
tabce2(cis_nor_small_intestine_fem_cond,post_small_intestine_nor_fem_cond);xx=xx+1
tabce2(cis_nor_small_intestine_fem_5y,post_small_intestine_nor_fem_5y);xx=1

axis(2,las=2,cex.axis=1.4,at=seq(range[1],range[2],by=10),labels=c(range[1],rep("",length(seq(range[1],range[2],by=10))-2),range[2]),pos=1971)
title(ylab="Female relative survival (%)", line=0.5, cex.lab=1.4)
axis(side=1,las=1,cex.axis=1.4,at=c(seq(1980,2020,by=10)),pos=range[1])
lines(c(1971,2020),c(range[1],range[1]))
title(xlab="Year", line=1, cex.lab=1.4,xpd=TRUE)

text(1974,range[2]-0.05*scal,"f",cex=2.2)
```

### Fig. 4 - Sweden
```{r,fig.height=6.9,fig.width=8,error=TRUE,warning=FALSE,results=FALSE,message=FALSE}
## SWE figures -----------------
m <- matrix(c(1,2,3
              ,4,6,8
              ,5,7,9), nrow = 3, ncol =3 ,byrow = TRUE)
layout(mat = m,heights = c(0.06,1-0.06))
par(mgp=c(1.6,0.8,0))
par(mar=c(0,0,0,0))
range<-c(0,100);scal<-range[2]-range[1]

plot(NULL, axes=FALSE,xlab="",ylab="",xlim=c(-1,1),ylim=c(-0.85,0.85))
text(0,-0.2,"Colon cancer",cex=1.6,font=3,xpd=TRUE)

plot(NULL, axes=FALSE,xlab="",ylab="",xlim=c(-1,1),ylim=c(-0.85,0.85))
text(0,-0.2,"Rectal cancer",cex=1.6,font=3,xpd=TRUE)

plot(NULL, axes=FALSE,xlab="",ylab="",xlim=c(-1,1),ylim=c(-0.85,0.85))
text(0,-0.2,"Small intestine cancer",cex=1.6,font=3,xpd=TRUE)


par(mgp=c(1.6,0.8,0))
par(mar=c(2,2.5,0,2))

### colon males % ------------------------------------------------------

plot(NULL,xlim=c(1971,2020),ylim=c(range[1],range[2]),xlab="",ylab=""
     ,las=1, axes=FALSE)
rect(1971,range[2],2020,range[1],col="grey90",border=NA)
x<-10
repeat{
  lines(c(1971,2020),c(x,x),col="white")
  x=x+10;if(x>100){break}}

x<-1980
repeat{
  lines(c(x,x),c(range[1],range[2]),col="white")
  x=x+10;if(x>2020){break}}

x<-c(yreal[1:500],yreal[500:1])

xx=1
tabce3(cis3_swe_colon_mal_1y,-0.6)
xx=xx+1
tabce3(cis3_swe_colon_mal_cond,0)
xx=xx+1
tabce3(cis3_swe_colon_mal_5y,0.6)

xx=1
polygon(x,cis2_colon_swe_mal_1y,border=NA,col=colb[xx],xpd=TRUE);xx=xx+1
polygon(x,cis2_colon_swe_mal_cond,border=NA,col=colb[xx],xpd=TRUE);xx=xx+1
polygon(x,cis2_colon_swe_mal_5y,border=NA,col=colb[xx],xpd=TRUE)

xx=1
points(colon[colon$group=="Sweden.Males",]$surv_1y~colon[colon$group=="Sweden.Males",]$year
       ,pch=17,col=colc[xx],cex=1);xx=xx+1
points(colon[colon$group=="Sweden.Males",]$surv_cond~colon[colon$group=="Sweden.Males",]$year
       ,pch=17,col=colc[xx],cex=1);xx=xx+1
points(colon[colon$group=="Sweden.Males",]$surv_5y~colon[colon$group=="Sweden.Males",]$year
       ,pch=17,col=colc[xx],cex=1)
xx=1
tabce2(cis_swe_colon_mal_1y,post_colon_swe_mal_1y);xx=xx+1
tabce2(cis_swe_colon_mal_cond,post_colon_swe_mal_cond);xx=xx+1
tabce2(cis_swe_colon_mal_5y,post_colon_swe_mal_5y);xx=1



axis(2,las=2,cex.axis=1.4,at=seq(range[1],range[2],by=10),labels=c(range[1],rep("",length(seq(range[1],range[2],by=10))-2),range[2]),pos=1971)
title(ylab="Male relative survival (%)", line=0.5, cex.lab=1.4)

xx=1;yy=range[1]+scal*0.37
xpo=-1
rect(1996+xpo,yy+0.035*scal,2017.9+xpo,yy-0.15*scal,col="white",border="grey50",lwd=0.8)
repeat{
  points(2000+xpo,yy,pch=17,col=cola[xx],cex=1.2)
  lines(c(1997+xpo,2003+xpo),c(yy,yy),lwd=1.6,col=cola[xx],lend=1)
  xx<-xx+1;yy=yy-(scal*0.058);if(xx>3){break}}
xx=1;yy=range[1]+scal*0.37
text(2010+xpo,yy,"1-year",col=cola[xx],cex=1.25);xx=xx+1;yy=yy-(scal*0.058)
text(2010+xpo,yy,"5/1-year",col=cola[xx],cex=1.25);xx=xx+1;yy=yy-(scal*0.058)
text(2010+xpo,yy,"5-year",col=cola[xx],cex=1.25);xx=xx+1;yy=yy-(scal*0.058)
text(1974,range[2]-0.05*scal,"a",cex=2.2)

# slope
x<-c(yreal[1:499],yreal[499:1])
cis2<-c(cis_swe_colon_mal_1y[1,],rev(cis_swe_colon_mal_1y[2,]));xx=1
cis2[cis2<range[1]]<-range[1]
cis2[cis2>range[2]]<-range[2]
cis2<-cis2*20
polygon(x,cis2,border=NA,col=colb[xx],xpd=F);xx=xx+1

cis2<-c(cis_swe_colon_mal_cond[1,],rev(cis_swe_colon_mal_cond[2,]))
cis2[cis2<range[1]]<-range[1]
cis2[cis2>range[2]]<-range[2]
cis2<-cis2*20
polygon(x,cis2,border=NA,col=colb[xx],xpd=F);xx=xx+1


cis2<-c(cis_swe_colon_mal_5y[1,],rev(cis_swe_colon_mal_5y[2,]))
cis2[cis2<range[1]]<-range[1]
cis2[cis2>range[2]]<-range[2]
cis2<-cis2*20
polygon(x,cis2,border=NA,col=colb[xx],xpd=F)

xx=1
tabce4(cis3_swe_colon_mal_1y*20,cis_swe_colon_mal_1y*20)
xx=xx+1
tabce4(cis3_swe_colon_mal_cond*20,cis_swe_colon_mal_cond*20)
xx=xx+1
tabce4(cis3_swe_colon_mal_5y*20,cis_swe_colon_mal_5y*20)

axis(4,las=2,cex.axis=1.4,at=seq(range[1],range[2],by=10),labels=c(range[1],rep("",length(seq(range[1],range[2],by=10))-2),range[2]/20),pos=2020)
text(2024.5,50,"Change in survival over a year",cex=1.3,srt=270,xpd=TRUE)

axis(side=1,las=1,cex.axis=1.4,at=c(seq(1980,2020,by=10)),pos=range[1])
lines(c(1971,2020),c(range[1],range[1]))
title(xlab="Year", line=1, cex.lab=1.4,xpd=TRUE)


### colon females % ------------------------------------------------------

plot(NULL,xlim=c(1971,2020),ylim=c(range[1],range[2]),xlab="",ylab=""
     ,las=1, axes=FALSE)
rect(1971,range[2],2020,range[1],col="grey90",border=NA)
x<-10
repeat{
  lines(c(1971,2020),c(x,x),col="white")
  x=x+10;if(x>100){break}}

x<-1980
repeat{
  lines(c(x,x),c(range[1],range[2]),col="white")
  x=x+10;if(x>2020){break}}

x<-c(yreal[1:500],yreal[500:1])

xx=1
tabce3(cis3_swe_colon_fem_1y,-0.6)
xx=xx+1
tabce3(cis3_swe_colon_fem_cond,0)
xx=xx+1
tabce3(cis3_swe_colon_fem_5y,0.6)

xx=1
polygon(x,cis2_colon_swe_fem_1y,border=NA,col=colb[xx],xpd=TRUE);xx=xx+1
polygon(x,cis2_colon_swe_fem_cond,border=NA,col=colb[xx],xpd=TRUE);xx=xx+1
polygon(x,cis2_colon_swe_fem_5y,border=NA,col=colb[xx],xpd=TRUE);xx=xx+1

xx=1
points(colon[colon$group=="Sweden.Females",]$surv_1y~colon[colon$group=="Sweden.Females",]$year
       ,pch=17,col=colc[xx],cex=1);xx=xx+1
points(colon[colon$group=="Sweden.Females",]$surv_cond~colon[colon$group=="Sweden.Females",]$year
       ,pch=17,col=colc[xx],cex=1);xx=xx+1
points(colon[colon$group=="Sweden.Females",]$surv_5y~colon[colon$group=="Sweden.Females",]$year
       ,pch=17,col=colc[xx],cex=1)
xx=1
tabce2(cis_swe_colon_fem_1y,post_colon_swe_fem_1y);xx=xx+1
tabce2(cis_swe_colon_fem_cond,post_colon_swe_fem_cond);xx=xx+1
tabce2(cis_swe_colon_fem_5y,post_colon_swe_fem_5y);xx=1

axis(2,las=2,cex.axis=1.4,at=seq(range[1],range[2],by=10),labels=c(range[1],rep("",length(seq(range[1],range[2],by=10))-2),range[2]),pos=1971)
title(ylab="Female relative survival (%)", line=0.5, cex.lab=1.4)

xx=1;yy=range[1]+scal*0.91
xpo=-17
text(1974,range[2]-0.05*scal,"d",cex=2.2)

# slope
x<-c(yreal[1:499],yreal[499:1])
cis2<-c(cis_swe_colon_fem_1y[1,],rev(cis_swe_colon_fem_1y[2,]));xx=1
cis2[cis2<range[1]]<-range[1]
cis2[cis2>range[2]]<-range[2]
cis2<-cis2*20
polygon(x,cis2,border=NA,col=colb[xx],xpd=F);xx=xx+1

cis2<-c(cis_swe_colon_fem_cond[1,],rev(cis_swe_colon_fem_cond[2,]))
cis2[cis2<range[1]]<-range[1]
cis2[cis2>range[2]]<-range[2]
cis2<-cis2*20
polygon(x,cis2,border=NA,col=colb[xx],xpd=F);xx=xx+1


cis2<-c(cis_swe_colon_fem_5y[1,],rev(cis_swe_colon_fem_5y[2,]))
cis2[cis2<range[1]]<-range[1]
cis2[cis2>range[2]]<-range[2]
cis2<-cis2*20
polygon(x,cis2,border=NA,col=colb[xx],xpd=F)

xx=1
tabce4(cis3_swe_colon_fem_1y*20,cis_swe_colon_fem_1y*20)
xx=xx+1
tabce4(cis3_swe_colon_fem_cond*20,cis_swe_colon_fem_cond*20)
xx=xx+1
tabce4(cis3_swe_colon_fem_5y*20,cis_swe_colon_fem_5y*20)

axis(4,las=2,cex.axis=1.4,at=seq(range[1],range[2],by=10),labels=c(range[1],rep("",length(seq(range[1],range[2],by=10))-2),range[2]/20),pos=2020)
text(2024.5,50,"Change in survival over a year",cex=1.3,srt=270,xpd=TRUE)

axis(side=1,las=1,cex.axis=1.4,at=c(seq(1980,2020,by=10)),pos=range[1])
lines(c(1971,2020),c(range[1],range[1]))
title(xlab="Year", line=1, cex.lab=1.4,xpd=TRUE)




### rectum males % ------------------------------------------------------

plot(NULL,xlim=c(1971,2020),ylim=c(range[1],range[2]),xlab="",ylab=""
     ,las=1, axes=FALSE)
rect(1971,range[2],2020,range[1],col="grey90",border=NA)
x<-10
repeat{
  lines(c(1971,2020),c(x,x),col="white")
  x=x+10;if(x>100){break}}

x<-1980
repeat{
  lines(c(x,x),c(range[1],range[2]),col="white")
  x=x+10;if(x>2020){break}}




x<-c(yreal[1:500],yreal[500:1])

xx=1
tabce3(cis3_swe_rectum_mal_1y,0)
xx=xx+1
tabce3(cis3_swe_rectum_mal_cond,0)
xx=xx+1
tabce3(cis3_swe_rectum_mal_5y,0)

xx=1
polygon(x,cis2_rectum_swe_mal_1y,border=NA,col=colb[xx],xpd=TRUE);xx=xx+1
polygon(x,cis2_rectum_swe_mal_cond,border=NA,col=colb[xx],xpd=TRUE);xx=xx+1
polygon(x,cis2_rectum_swe_mal_5y,border=NA,col=colb[xx],xpd=TRUE);xx=xx+1

xx=1
points(rectum[rectum$group=="Sweden.Males",]$surv_1y~rectum[rectum$group=="Sweden.Males",]$year
       ,pch=17,col=colc[xx],cex=1);xx=xx+1
points(rectum[rectum$group=="Sweden.Males",]$surv_cond~rectum[rectum$group=="Sweden.Males",]$year
       ,pch=17,col=colc[xx],cex=1);xx=xx+1
points(rectum[rectum$group=="Sweden.Males",]$surv_5y~rectum[rectum$group=="Sweden.Males",]$year
       ,pch=17,col=colc[xx],cex=1)
xx=1
tabce2(cis_swe_rectum_mal_1y,post_rectum_swe_mal_1y);xx=xx+1
tabce2(cis_swe_rectum_mal_cond,post_rectum_swe_mal_cond);xx=xx+1
tabce2(cis_swe_rectum_mal_5y,post_rectum_swe_mal_5y);xx=1

axis(2,las=2,cex.axis=1.4,at=seq(range[1],range[2],by=10),labels=c(range[1],rep("",length(seq(range[1],range[2],by=10))-2),range[2]),pos=1971)
title(ylab="Male relative survival (%)", line=0.5, cex.lab=1.4)
text(1974,range[2]-0.05*scal,"b",cex=2.2)

# slope
x<-c(yreal[1:499],yreal[499:1])
cis2<-c(cis_swe_rectum_mal_1y[1,],rev(cis_swe_rectum_mal_1y[2,]));xx=1
cis2[cis2<range[1]]<-range[1]
cis2[cis2>range[2]]<-range[2]
cis2<-cis2*20
polygon(x,cis2,border=NA,col=colb[xx],xpd=F);xx=xx+1

cis2<-c(cis_swe_rectum_mal_cond[1,],rev(cis_swe_rectum_mal_cond[2,]))
cis2[cis2<range[1]]<-range[1]
cis2[cis2>range[2]]<-range[2]
cis2<-cis2*20
polygon(x,cis2,border=NA,col=colb[xx],xpd=F);xx=xx+1


cis2<-c(cis_swe_rectum_mal_5y[1,],rev(cis_swe_rectum_mal_5y[2,]))
cis2[cis2<range[1]]<-range[1]
cis2[cis2>range[2]]<-range[2]
cis2<-cis2*20
polygon(x,cis2,border=NA,col=colb[xx],xpd=F)

xx=1
tabce4(cis3_swe_rectum_mal_1y*20,cis_swe_rectum_mal_1y*20)
xx=xx+1
tabce4(cis3_swe_rectum_mal_cond*20,cis_swe_rectum_mal_cond*20)
xx=xx+1
tabce4(cis3_swe_rectum_mal_5y*20,cis_swe_rectum_mal_5y*20)

axis(4,las=2,cex.axis=1.4,at=seq(range[1],range[2],by=10),labels=c(range[1],rep("",length(seq(range[1],range[2],by=10))-2),range[2]/20),pos=2020)
text(2024.5,50,"Change in survival over a year",cex=1.3,srt=270,xpd=TRUE)

axis(side=1,las=1,cex.axis=1.4,at=c(seq(1980,2020,by=10)),pos=range[1])
lines(c(1971,2020),c(range[1],range[1]))
title(xlab="Year", line=1, cex.lab=1.4,xpd=TRUE)




### rectum females % ------------------------------------------------------

plot(NULL,xlim=c(1971,2020),ylim=c(range[1],range[2]),xlab="",ylab=""
     ,las=1, axes=FALSE)
rect(1971,range[2],2020,range[1],col="grey90",border=NA)
x<-10
repeat{
  lines(c(1971,2020),c(x,x),col="white")
  x=x+10;if(x>100){break}}

x<-1980
repeat{
  lines(c(x,x),c(range[1],range[2]),col="white")
  x=x+10;if(x>2020){break}}

x<-c(yreal[1:500],yreal[500:1])
xx=1
tabce3(cis3_swe_rectum_fem_1y,-0.6)
xx=xx+1
tabce3(cis3_swe_rectum_fem_cond,0)
xx=xx+1
tabce3(cis3_swe_rectum_fem_5y,0.6)

xx=1
polygon(x,cis2_rectum_swe_fem_1y,border=NA,col=colb[xx],xpd=TRUE);xx=xx+1
polygon(x,cis2_rectum_swe_fem_cond,border=NA,col=colb[xx],xpd=TRUE);xx=xx+1
polygon(x,cis2_rectum_swe_fem_5y,border=NA,col=colb[xx],xpd=TRUE);xx=xx+1

xx=1
points(rectum[rectum$group=="Sweden.Females",]$surv_1y~rectum[rectum$group=="Sweden.Females",]$year
       ,pch=17,col=colc[xx],cex=1);xx=xx+1
points(rectum[rectum$group=="Sweden.Females",]$surv_cond~rectum[rectum$group=="Sweden.Females",]$year
       ,pch=17,col=colc[xx],cex=1);xx=xx+1
points(rectum[rectum$group=="Sweden.Females",]$surv_5y~rectum[rectum$group=="Sweden.Females",]$year
       ,pch=17,col=colc[xx],cex=1)
xx=1
tabce2(cis_swe_rectum_fem_1y,post_rectum_swe_fem_1y);xx=xx+1
tabce2(cis_swe_rectum_fem_cond,post_rectum_swe_fem_cond);xx=xx+1
tabce2(cis_swe_rectum_fem_5y,post_rectum_swe_fem_5y);xx=1

axis(2,las=2,cex.axis=1.4,at=seq(range[1],range[2],by=10),labels=c(range[1],rep("",length(seq(range[1],range[2],by=10))-2),range[2]),pos=1971)
title(ylab="Female relative survival (%)", line=0.5, cex.lab=1.4)
text(1974,range[2]-0.05*scal,"e",cex=2.2)

# slope
x<-c(yreal[1:499],yreal[499:1])
cis2<-c(cis_swe_rectum_fem_1y[1,],rev(cis_swe_rectum_fem_1y[2,]));xx=1
cis2[cis2<range[1]]<-range[1]
cis2[cis2>range[2]]<-range[2]
cis2<-cis2*20
polygon(x,cis2,border=NA,col=colb[xx],xpd=F);xx=xx+1

cis2<-c(cis_swe_rectum_fem_cond[1,],rev(cis_swe_rectum_fem_cond[2,]))
cis2[cis2<range[1]]<-range[1]
cis2[cis2>range[2]]<-range[2]
cis2<-cis2*20
polygon(x,cis2,border=NA,col=colb[xx],xpd=F);xx=xx+1


cis2<-c(cis_swe_rectum_fem_5y[1,],rev(cis_swe_rectum_fem_5y[2,]))
cis2[cis2<range[1]]<-range[1]
cis2[cis2>range[2]]<-range[2]
cis2<-cis2*20
polygon(x,cis2,border=NA,col=colb[xx],xpd=F)

xx=1
tabce4(cis3_swe_rectum_fem_1y*20,cis_swe_rectum_fem_1y*20)
xx=xx+1
tabce4(cis3_swe_rectum_fem_cond*20,cis_swe_rectum_fem_cond*20)
xx=xx+1
tabce4(cis3_swe_rectum_fem_5y*20,cis_swe_rectum_fem_5y*20)

axis(4,las=2,cex.axis=1.4,at=seq(range[1],range[2],by=10),labels=c(range[1],rep("",length(seq(range[1],range[2],by=10))-2),range[2]/20),pos=2020)
text(2024.5,50,"Change in survival over a year",cex=1.3,srt=270,xpd=TRUE)

axis(side=1,las=1,cex.axis=1.4,at=c(seq(1980,2020,by=10)),pos=range[1])
lines(c(1971,2020),c(range[1],range[1]))
title(xlab="Year", line=1, cex.lab=1.4,xpd=TRUE)


### small_intestine males % ------------------------------------------------------

plot(NULL,xlim=c(1971,2020),ylim=c(range[1],range[2]),xlab="",ylab=""
     ,las=1, axes=FALSE)
rect(1971,range[2],2020,range[1],col="grey90",border=NA)
x<-10
repeat{
  lines(c(1971,2020),c(x,x),col="white")
  x=x+10;if(x>100){break}}

x<-1980
repeat{
  lines(c(x,x),c(range[1],range[2]),col="white")
  x=x+10;if(x>2020){break}}

x<-c(yreal[1:500],yreal[500:1])

xx=1
tabce3(cis3_swe_small_intestine_mal_1y,-0)
xx=xx+1
tabce3(cis3_swe_small_intestine_mal_cond,0)
xx=xx+1
tabce3(cis3_swe_small_intestine_mal_5y,0)

xx=1
polygon(x,cis2_small_intestine_swe_mal_1y,border=NA,col=colb[xx],xpd=TRUE);xx=xx+1
polygon(x,cis2_small_intestine_swe_mal_cond,border=NA,col=colb[xx],xpd=TRUE);xx=xx+1
polygon(x,cis2_small_intestine_swe_mal_5y,border=NA,col=colb[xx],xpd=TRUE);xx=xx+1

xx=1
points(small_intestine[small_intestine$group=="Sweden.Males",]$surv_1y~small_intestine[small_intestine$group=="Sweden.Males",]$year
       ,pch=17,col=colc[xx],cex=1);xx=xx+1
points(small_intestine[small_intestine$group=="Sweden.Males",]$surv_cond~small_intestine[small_intestine$group=="Sweden.Males",]$year
       ,pch=17,col=colc[xx],cex=1);xx=xx+1
points(small_intestine[small_intestine$group=="Sweden.Males",]$surv_5y~small_intestine[small_intestine$group=="Sweden.Males",]$year
       ,pch=17,col=colc[xx],cex=1)
xx=1
tabce2(cis_swe_small_intestine_mal_1y,post_small_intestine_swe_mal_1y);xx=xx+1
tabce2(cis_swe_small_intestine_mal_cond,post_small_intestine_swe_mal_cond);xx=xx+1
tabce2(cis_swe_small_intestine_mal_5y,post_small_intestine_swe_mal_5y);xx=1


axis(2,las=2,cex.axis=1.4,at=seq(range[1],range[2],by=10),labels=c(range[1],rep("",length(seq(range[1],range[2],by=10))-2),range[2]),pos=1971)
title(ylab="Male relative survival (%)", line=0.5, cex.lab=1.4)
axis(side=1,las=1,cex.axis=1.4,at=c(seq(1980,2020,by=10)),pos=range[1])
lines(c(1971,2020),c(range[1],range[1]))
title(xlab="Year", line=1, cex.lab=1.4,xpd=TRUE)
text(1974,range[2]-0.05*scal,"c",cex=2.2)

ypo=-78
xfl=48
rect(1956+xfl,range[1]+scal*0.965+ypo,1968+xfl,range[1]+scal*0.84+ypo,col="blue",border="grey50")
rect(1956+xfl,range[1]+scal*0.9135+ypo,1968+xfl,range[1]+scal*0.8865+ypo,col="yellow",border=NA)
rect(1960+xfl,range[1]+scal*0.965+ypo,1962+xfl,range[1]+scal*0.84+ypo,col="yellow",border=NA)


### small_intestine females % ------------------------------------------------------

plot(NULL,xlim=c(1971,2020),ylim=c(range[1],range[2]),xlab="",ylab=""
     ,las=1, axes=FALSE)
rect(1971,range[2],2020,range[1],col="grey90",border=NA)
x<-10
repeat{
  lines(c(1971,2020),c(x,x),col="white")
  x=x+10;if(x>100){break}}

x<-1980
repeat{
  lines(c(x,x),c(range[1],range[2]),col="white")
  x=x+10;if(x>2020){break}}

x<-c(yreal[1:500],yreal[500:1])

xx=1
tabce3(cis3_swe_small_intestine_fem_1y,-0.6)
xx=xx+1
tabce3(cis3_swe_small_intestine_fem_cond,0)
xx=xx+1
tabce3(cis3_swe_small_intestine_fem_5y,0.6)

xx=1
polygon(x,cis2_small_intestine_swe_fem_1y,border=NA,col=colb[xx],xpd=TRUE);xx=xx+1
polygon(x,cis2_small_intestine_swe_fem_cond,border=NA,col=colb[xx],xpd=TRUE);xx=xx+1
polygon(x,cis2_small_intestine_swe_fem_5y,border=NA,col=colb[xx],xpd=TRUE);xx=xx+1

xx=1
points(small_intestine[small_intestine$group=="Sweden.Females",]$surv_1y~small_intestine[small_intestine$group=="Sweden.Females",]$year,pch=17,col=colc[xx],cex=1);xx=xx+1
points(small_intestine[small_intestine$group=="Sweden.Females",]$surv_cond~small_intestine[small_intestine$group=="Sweden.Females",]$year ,pch=17,col=colc[xx],cex=1);xx=xx+1
points(small_intestine[small_intestine$group=="Sweden.Females",]$surv_5y~small_intestine[small_intestine$group=="Sweden.Females",]$year,pch=17,col=colc[xx],cex=1)
xx=1
tabce2(cis_swe_small_intestine_fem_1y,post_small_intestine_swe_fem_1y);xx=xx+1
tabce2(cis_swe_small_intestine_fem_cond,post_small_intestine_swe_fem_cond);xx=xx+1
tabce2(cis_swe_small_intestine_fem_5y,post_small_intestine_swe_fem_5y);xx=1

axis(2,las=2,cex.axis=1.4,at=seq(range[1],range[2],by=10),labels=c(range[1],rep("",length(seq(range[1],range[2],by=10))-2),range[2]),pos=1971)
title(ylab="Female relative survival (%)", line=0.5, cex.lab=1.4)
axis(side=1,las=1,cex.axis=1.4,at=c(seq(1980,2020,by=10)),pos=range[1])
lines(c(1971,2020),c(range[1],range[1]))
title(xlab="Year", line=1, cex.lab=1.4,xpd=TRUE)

text(1974,range[2]-0.05*scal,"f",cex=2.2)
```


### Suppl. Fig. 3 - Small intestine - change in trend
```{r,fig.height=6.9,fig.width=8,error=TRUE,warning=FALSE,results=FALSE,message=FALSE}
#  Small intestine change in survival ----------------

m <- matrix(c(1,2, 3, 4
              ,5,7, 9,11
              ,6,8,10,12), nrow = 3, ncol = 4 ,byrow = TRUE)
layout(mat = m,heights = c(0.04,0.48,0.48))
par(mgp=c(1.6,0.8,0))
par(mar=c(0,0,0,0))
range<-c(-2,3);scal<-range[2]-range[1]

plot(NULL, axes=FALSE,xlab="",ylab="",xlim=c(-1,1),ylim=c(-0.85,0.85))
text(0,-0.2,"Denmark",cex=1.6,font=3,xpd=TRUE)

plot(NULL, axes=FALSE,xlab="",ylab="",xlim=c(-1,1),ylim=c(-0.85,0.85))
text(0,-0.2,"Finland",cex=1.6,font=3,xpd=TRUE)

plot(NULL, axes=FALSE,xlab="",ylab="",xlim=c(-1,1),ylim=c(-0.85,0.85))
text(0,-0.2,"Norway",cex=1.6,font=3,xpd=TRUE)

plot(NULL, axes=FALSE,xlab="",ylab="",xlim=c(-1,1),ylim=c(-0.85,0.85))
text(0,-0.2,"Sweden",cex=1.6,font=3,xpd=TRUE)


par(mgp=c(1.6,0.8,0))
par(mar=c(2,1.5,0,0.5))

### DEN males % ------------------------------------------------------
plot(NULL,xlim=c(1971,2020),ylim=c(range[1],range[2]),xlab="",ylab=""
     ,las=1, axes=FALSE)
rect(1971,range[2],2020,range[1],col="grey90",border=NA)
x<-range[1]
repeat{
  lines(c(1971,2020),c(x,x),col="white")
  x=x+1;if(x>range[2]){break}}

x<-1980
repeat{
  lines(c(x,x),c(range[1],range[2]),col="white")
  x=x+10;if(x>2020){break}}
lines(yreal[1:499],rep(0,499),lwd=1,col="black",lty=1,lend=1)

x<-c(yreal[1:499],yreal[499:1])

cis2<-c(cis_den_small_intestine_mal_1y[1,],rev(cis_den_small_intestine_mal_1y[2,]));xx=1
cis2[cis2<range[1]]<-range[1]
cis2[cis2>range[2]]<-range[2]
polygon(x,cis2,border=NA,col=colb[xx],xpd=F);xx=xx+1

cis2<-c(cis_den_small_intestine_mal_cond[1,],rev(cis_den_small_intestine_mal_cond[2,]))
cis2[cis2<range[1]]<-range[1]
cis2[cis2>range[2]]<-range[2]
polygon(x,cis2,border=NA,col=colb[xx],xpd=F);xx=xx+1

cis2<-c(cis_den_small_intestine_mal_5y[1,],rev(cis_den_small_intestine_mal_5y[2,]))
cis2[cis2<range[1]]<-range[1]
cis2[cis2>range[2]]<-range[2]
polygon(x,cis2,border=NA,col=colb[xx],xpd=F);xx=1

xx=1
tabce4(cis3_den_small_intestine_mal_1y,cis_den_small_intestine_mal_1y)
xx=xx+1
tabce4(cis3_den_small_intestine_mal_cond,cis_den_small_intestine_mal_cond)
xx=xx+1
tabce4(cis3_den_small_intestine_mal_5y,cis_den_small_intestine_mal_5y)

axis(2,las=2,cex.axis=1.4,at=seq(range[1],range[2],by=1),labels=c(range[1],rep("",length(seq(range[1],range[2],by=1))-2),range[2]),pos=1971)
title(ylab="Change in male survival (%)", line=0.3, cex.lab=1.4)
axis(side=1,las=1,cex.axis=1.4,at=c(seq(1980,2020,by=10)),pos=range[1],labels=c(rep("",5)));text(c(seq(1978,2020,by=20)),c(rep(range[1]-0.05*scal,3)),c(seq(1980,2020,by=20)),xpd=TRUE,cex=1.4);
lines(c(1971,2020),c(range[1],range[1]))
title(xlab="Year", line=1, cex.lab=1.4,xpd=TRUE)

xx=1;yy=range[1]+scal*0.2
rect(1996,yy+0.035*scal,2019,yy-0.15*scal,col="white",border="grey50",lwd=0.8)
repeat{
  points(2000,yy,pch=17,col=cola[xx],cex=1.5)
  lines(c(1997,2003),c(yy,yy),lwd=1.6,col=cola[xx],lend=1)
  xx<-xx+1;yy=yy-(scal*0.058);if(xx>3){break}}
xx=1;yy=range[1]+scal*0.2
text(2011,yy,"1-year",col=cola[xx],cex=1.15);xx=xx+1;yy=yy-(scal*0.058)
text(2011,yy,"5/1-year",col=cola[xx],cex=1.15);xx=xx+1;yy=yy-(scal*0.058)
text(2011,yy,"5-year",col=cola[xx],cex=1.15);xx=xx+1;yy=yy-(scal*0.058)

text(1974.5,range[2]-0.05*scal,"a",cex=1.9)

ypo=0
xfl=30
rect(1956+xfl,range[1]+scal*0.965+ypo,1968+xfl,range[1]+scal*0.84+ypo,col="red2",border="grey50")
rect(1956+xfl,range[1]+scal*0.9135+ypo,1968+xfl,range[1]+scal*0.8865+ypo,col="white",border=NA)
rect(1960+xfl,range[1]+scal*0.965+ypo,1962+xfl,range[1]+scal*0.84+ypo,col="white",border=NA)


### DEN females % ------------------------------------------------------
plot(NULL,xlim=c(1971,2020),ylim=c(range[1],range[2]),xlab="",ylab=""
     ,las=1, axes=FALSE)
rect(1971,range[2],2020,range[1],col="grey90",border=NA)
x<-range[1]
repeat{
  lines(c(1971,2020),c(x,x),col="white")
  x=x+1;if(x>range[2]){break}}

x<-1980
repeat{
  lines(c(x,x),c(range[1],range[2]),col="white")
  x=x+10;if(x>2020){break}}
lines(yreal[1:499],rep(0,499),lwd=1,col="black",lty=1,lend=1)

x<-c(yreal[1:499],yreal[499:1])

cis2<-c(cis_den_small_intestine_fem_1y[1,],rev(cis_den_small_intestine_fem_1y[2,]));xx=1
polygon(x,cis2,border=NA,col=colb[xx],xpd=TRUE);xx=xx+1

cis2<-c(cis_den_small_intestine_fem_cond[1,],rev(cis_den_small_intestine_fem_cond[2,]))
polygon(x,cis2,border=NA,col=colb[xx],xpd=TRUE);xx=xx+1

cis2<-c(cis_den_small_intestine_fem_5y[1,],rev(cis_den_small_intestine_fem_5y[2,]))
polygon(x,cis2,border=NA,col=colb[xx],xpd=TRUE);xx=1

xx=1
tabce4(cis3_den_small_intestine_fem_1y,cis_den_small_intestine_fem_1y)
xx=xx+1
tabce4(cis3_den_small_intestine_fem_cond,cis_den_small_intestine_fem_cond)
xx=xx+1
tabce4(cis3_den_small_intestine_fem_5y,cis_den_small_intestine_fem_5y)

axis(2,las=2,cex.axis=1.4,at=seq(range[1],range[2],by=1),labels=c(range[1],rep("",length(seq(range[1],range[2],by=1))-2),range[2]),pos=1971)
title(ylab="Change in female survival (%)", line=0.3, cex.lab=1.4)
axis(side=1,las=1,cex.axis=1.4,at=c(seq(1980,2020,by=10)),pos=range[1],labels=c(rep("",5)));text(c(seq(1978,2020,by=20)),c(rep(range[1]-0.05*scal,3)),c(seq(1980,2020,by=20)),xpd=TRUE,cex=1.4);
lines(c(1971,2020),c(range[1],range[1]))
title(xlab="Year", line=1, cex.lab=1.4,xpd=TRUE)
text(1974.5,range[2]-0.05*scal,"e",cex=1.9)

### FIN males % ------------------------------------------------------
plot(NULL,xlim=c(1971,2020),ylim=c(range[1],range[2]),xlab="",ylab=""
     ,las=1, axes=FALSE)
rect(1971,range[2],2020,range[1],col="grey90",border=NA)
x<-range[1]
repeat{
  lines(c(1971,2020),c(x,x),col="white")
  x=x+1;if(x>range[2]){break}}

x<-1980
repeat{
  lines(c(x,x),c(range[1],range[2]),col="white")
  x=x+10;if(x>2020){break}}
lines(yreal[1:499],rep(0,499),lwd=1,col="black",lty=1,lend=1)

x<-c(yreal[1:499],yreal[499:1])

cis2<-c(cis_fin_small_intestine_mal_1y[1,],rev(cis_fin_small_intestine_mal_1y[2,]));xx=1
cis2[cis2<range[1]]<-range[1]
cis2[cis2>range[2]]<-range[2]
polygon(x,cis2,border=NA,col=colb[xx],xpd=F);xx=xx+1

cis2<-c(cis_fin_small_intestine_mal_cond[1,],rev(cis_fin_small_intestine_mal_cond[2,]))
cis2[cis2<range[1]]<-range[1]
cis2[cis2>range[2]]<-range[2]
polygon(x,cis2,border=NA,col=colb[xx],xpd=F);xx=xx+1

cis2<-c(cis_fin_small_intestine_mal_5y[1,],rev(cis_fin_small_intestine_mal_5y[2,]))
polygon(x,cis2,border=NA,col=colb[xx],xpd=F);xx=1

xx=1
tabce4(cis3_fin_small_intestine_mal_1y,cis_fin_small_intestine_mal_1y)
xx=xx+1
tabce4(cis3_fin_small_intestine_mal_cond,cis_fin_small_intestine_mal_cond)
xx=xx+1
tabce4(cis3_fin_small_intestine_mal_5y,cis_fin_small_intestine_mal_5y)

axis(2,las=2,cex.axis=1.4,at=seq(range[1],range[2],by=1),labels=c(range[1],rep("",length(seq(range[1],range[2],by=1))-2),range[2]),pos=1971)
#title(ylab="Change in male survival (%)", line=1, cex.lab=1.4)
axis(side=1,las=1,cex.axis=1.4,at=c(seq(1980,2020,by=10)),pos=range[1],labels=c(rep("",5)));text(c(seq(1978,2020,by=20)),c(rep(range[1]-0.05*scal,3)),c(seq(1980,2020,by=20)),xpd=TRUE,cex=1.4);
lines(c(1971,2020),c(range[1],range[1]))
title(xlab="Year", line=1, cex.lab=1.4,xpd=TRUE)

text(1974.5,range[2]-0.05*scal,"b",cex=1.9)

ypo=0
xfl=30
rect(1956+xfl,range[1]+scal*0.965+ypo,1968+xfl,range[1]+scal*0.84+ypo,col="white",border="grey50")
rect(1956+xfl,range[1]+scal*0.9135+ypo,1968+xfl,range[1]+scal*0.8865+ypo,col="dodgerblue3",border=NA)
rect(1960+xfl,range[1]+scal*0.965+ypo,1962+xfl,range[1]+scal*0.84+ypo,col="dodgerblue3",border=NA)


### FIN females % ------------------------------------------------------
plot(NULL,xlim=c(1971,2020),ylim=c(range[1],range[2]),xlab="",ylab=""
     ,las=1, axes=FALSE)
rect(1971,range[2],2020,range[1],col="grey90",border=NA)
x<-range[1]
repeat{
  lines(c(1971,2020),c(x,x),col="white")
  x=x+1;if(x>range[2]){break}}

x<-1980
repeat{
  lines(c(x,x),c(range[1],range[2]),col="white")
  x=x+10;if(x>2020){break}}
lines(yreal[1:499],rep(0,499),lwd=1,col="black",lty=1,lend=1)

x<-c(yreal[1:499],yreal[499:1])

cis2<-c(cis_fin_small_intestine_fem_1y[1,],rev(cis_fin_small_intestine_fem_1y[2,]));xx=1
polygon(x,cis2,border=NA,col=colb[xx],xpd=TRUE);xx=xx+1

cis2<-c(cis_fin_small_intestine_fem_cond[1,],rev(cis_fin_small_intestine_fem_cond[2,]))
cis2[cis2<range[1]]<-range[1]
cis2[cis2>range[2]]<-range[2]
polygon(x,cis2,border=NA,col=colb[xx],xpd=TRUE);xx=xx+1

cis2<-c(cis_fin_small_intestine_fem_5y[1,],rev(cis_fin_small_intestine_fem_5y[2,]))
polygon(x,cis2,border=NA,col=colb[xx],xpd=TRUE);xx=1

xx=1
tabce4(cis3_fin_small_intestine_fem_1y,cis_fin_small_intestine_fem_1y)
xx=xx+1
tabce4(cis3_fin_small_intestine_fem_cond,cis_fin_small_intestine_fem_cond)
xx=xx+1
tabce4(cis3_fin_small_intestine_fem_5y,cis_fin_small_intestine_fem_5y)

axis(2,las=2,cex.axis=1.4,at=seq(range[1],range[2],by=1),labels=c(range[1],rep("",length(seq(range[1],range[2],by=1))-2),range[2]),pos=1971)
#title(ylab="Change in female survival (%)", line=1, cex.lab=1.4)
axis(side=1,las=1,cex.axis=1.4,at=c(seq(1980,2020,by=10)),pos=range[1],labels=c(rep("",5)));text(c(seq(1978,2020,by=20)),c(rep(range[1]-0.05*scal,3)),c(seq(1980,2020,by=20)),xpd=TRUE,cex=1.4);
lines(c(1971,2020),c(range[1],range[1]))
title(xlab="Year", line=1, cex.lab=1.4,xpd=TRUE)
text(1974.5,range[2]-0.05*scal,"f",cex=1.9)


### NOR males % ------------------------------------------------------
plot(NULL,xlim=c(1971,2020),ylim=c(range[1],range[2]),xlab="",ylab=""
     ,las=1, axes=FALSE)
rect(1971,range[2],2020,range[1],col="grey90",border=NA)
x<-range[1]
repeat{
  lines(c(1971,2020),c(x,x),col="white")
  x=x+1;if(x>range[2]){break}}

x<-1980
repeat{
  lines(c(x,x),c(range[1],range[2]),col="white")
  x=x+10;if(x>2020){break}}
lines(yreal[1:499],rep(0,499),lwd=1,col="black",lty=1,lend=1)

x<-c(yreal[1:499],yreal[499:1])

cis2<-c(cis_nor_small_intestine_mal_1y[1,],rev(cis_nor_small_intestine_mal_1y[2,]));xx=1
polygon(x,cis2,border=NA,col=colb[xx],xpd=F);xx=xx+1

cis2<-c(cis_nor_small_intestine_mal_cond[1,],rev(cis_nor_small_intestine_mal_cond[2,]))
polygon(x,cis2,border=NA,col=colb[xx],xpd=F);xx=xx+1

cis2<-c(cis_nor_small_intestine_mal_5y[1,],rev(cis_nor_small_intestine_mal_5y[2,]))
polygon(x,cis2,border=NA,col=colb[xx],xpd=F);xx=1

xx=1
tabce4(cis3_nor_small_intestine_mal_1y,cis_nor_small_intestine_mal_1y)
xx=xx+1
tabce4(cis3_nor_small_intestine_mal_cond,cis_nor_small_intestine_mal_cond)
xx=xx+1
tabce4(cis3_nor_small_intestine_mal_5y,cis_nor_small_intestine_mal_5y)

axis(2,las=2,cex.axis=1.4,at=seq(range[1],range[2],by=1),labels=c(range[1],rep("",length(seq(range[1],range[2],by=1))-2),range[2]),pos=1971)
#title(ylab="Change in male survival (%)", line=1, cex.lab=1.4)
axis(side=1,las=1,cex.axis=1.4,at=c(seq(1980,2020,by=10)),pos=range[1],labels=c(rep("",5)));text(c(seq(1978,2020,by=20)),c(rep(range[1]-0.05*scal,3)),c(seq(1980,2020,by=20)),xpd=TRUE,cex=1.4);
lines(c(1971,2020),c(range[1],range[1]))
title(xlab="Year", line=1, cex.lab=1.4,xpd=TRUE)

text(1974.5,range[2]-0.05*scal,"c",cex=1.9)

ypo=0
xfl=30
rect(1956+xfl,range[1]+scal*0.965+ypo,1968+xfl,range[1]+scal*0.84+ypo,col="red2",border="grey50")
rect(1956+xfl,range[1]+scal*0.9285+ypo,1968+xfl,range[1]+scal*0.8735+ypo,col="white",border=NA)
rect(1959+xfl,range[1]+scal*0.965+ypo,1963+xfl,range[1]+scal*0.84+ypo,col="white",border=NA)
rect(1956+xfl,range[1]+scal*0.9135+ypo,1968+xfl,range[1]+scal*0.8865+ypo,col="darkblue",border=NA)
rect(1960+xfl,range[1]+scal*0.965+ypo,1962+xfl,range[1]+scal*0.84+ypo,col="darkblue",border=NA)

### NOR females % ------------------------------------------------------
plot(NULL,xlim=c(1971,2020),ylim=c(range[1],range[2]),xlab="",ylab=""
     ,las=1, axes=FALSE)
rect(1971,range[2],2020,range[1],col="grey90",border=NA)
x<-range[1]
repeat{
  lines(c(1971,2020),c(x,x),col="white")
  x=x+1;if(x>range[2]){break}}

x<-1980
repeat{
  lines(c(x,x),c(range[1],range[2]),col="white")
  x=x+10;if(x>2020){break}}
lines(yreal[1:499],rep(0,499),lwd=1,col="black",lty=1,lend=1)

x<-c(yreal[1:499],yreal[499:1])

cis2<-c(cis_nor_small_intestine_fem_1y[1,],rev(cis_nor_small_intestine_fem_1y[2,]));xx=1
polygon(x,cis2,border=NA,col=colb[xx],xpd=TRUE);xx=xx+1

cis2<-c(cis_nor_small_intestine_fem_cond[1,],rev(cis_nor_small_intestine_fem_cond[2,]))
cis2[cis2<range[1]]<-range[1]
cis2[cis2>range[2]]<-range[2]
polygon(x,cis2,border=NA,col=colb[xx],xpd=TRUE);xx=xx+1

cis2<-c(cis_nor_small_intestine_fem_5y[1,],rev(cis_nor_small_intestine_fem_5y[2,]))
polygon(x,cis2,border=NA,col=colb[xx],xpd=TRUE);xx=1

xx=1
tabce4(cis3_nor_small_intestine_fem_1y,cis_nor_small_intestine_fem_1y)
xx=xx+1
tabce4(cis3_nor_small_intestine_fem_cond,cis_nor_small_intestine_fem_cond)
xx=xx+1
tabce4(cis3_nor_small_intestine_fem_5y,cis_nor_small_intestine_fem_5y)

axis(2,las=2,cex.axis=1.4,at=seq(range[1],range[2],by=1),labels=c(range[1],rep("",length(seq(range[1],range[2],by=1))-2),range[2]),pos=1971)
#title(ylab="Change in female survival (%)", line=1, cex.lab=1.4)
axis(side=1,las=1,cex.axis=1.4,at=c(seq(1980,2020,by=10)),pos=range[1],labels=c(rep("",5)));text(c(seq(1978,2020,by=20)),c(rep(range[1]-0.05*scal,3)),c(seq(1980,2020,by=20)),xpd=TRUE,cex=1.4);
lines(c(1971,2020),c(range[1],range[1]))
title(xlab="Year", line=1, cex.lab=1.4,xpd=TRUE)
text(1974.5,range[2]-0.05*scal,"g",cex=1.9)


### SWE males % ------------------------------------------------------
plot(NULL,xlim=c(1971,2020),ylim=c(range[1],range[2]),xlab="",ylab=""
     ,las=1, axes=FALSE)
rect(1971,range[2],2020,range[1],col="grey90",border=NA)
x<-range[1]
repeat{
  lines(c(1971,2020),c(x,x),col="white")
  x=x+1;if(x>range[2]){break}}

x<-1980
repeat{
  lines(c(x,x),c(range[1],range[2]),col="white")
  x=x+10;if(x>2020){break}}
lines(yreal[1:499],rep(0,499),lwd=1,col="black",lty=1,lend=1)

x<-c(yreal[1:499],yreal[499:1])

cis2<-c(cis_swe_small_intestine_mal_1y[1,],rev(cis_swe_small_intestine_mal_1y[2,]));xx=1
polygon(x,cis2,border=NA,col=colb[xx],xpd=F);xx=xx+1

cis2<-c(cis_swe_small_intestine_mal_cond[1,],rev(cis_swe_small_intestine_mal_cond[2,]))
polygon(x,cis2,border=NA,col=colb[xx],xpd=F);xx=xx+1

cis2<-c(cis_swe_small_intestine_mal_5y[1,],rev(cis_swe_small_intestine_mal_5y[2,]))
polygon(x,cis2,border=NA,col=colb[xx],xpd=F);xx=1

xx=1
tabce4(cis3_swe_small_intestine_mal_1y,cis_swe_small_intestine_mal_1y)
xx=xx+1
tabce4(cis3_swe_small_intestine_mal_cond,cis_swe_small_intestine_mal_cond)
xx=xx+1
tabce4(cis3_swe_small_intestine_mal_5y,cis_swe_small_intestine_mal_5y)

axis(2,las=2,cex.axis=1.4,at=seq(range[1],range[2],by=1),labels=c(range[1],rep("",length(seq(range[1],range[2],by=1))-2),range[2]),pos=1971)
#title(ylab="Change in male survival (%)", line=1, cex.lab=1.4)
axis(side=1,las=1,cex.axis=1.4,at=c(seq(1980,2020,by=10)),pos=range[1],labels=c(rep("",5)));text(c(seq(1978,2020,by=20)),c(rep(range[1]-0.05*scal,3)),c(seq(1980,2020,by=20)),xpd=TRUE,cex=1.4);
lines(c(1971,2020),c(range[1],range[1]))
title(xlab="Year", line=1, cex.lab=1.4,xpd=TRUE)

text(1974.5,range[2]-0.05*scal,"d",cex=1.9)

ypo=0
xfl=30
rect(1956+xfl,range[1]+scal*0.965+ypo,1968+xfl,range[1]+scal*0.84+ypo,col="blue",border="grey50")
rect(1956+xfl,range[1]+scal*0.9135+ypo,1968+xfl,range[1]+scal*0.8865+ypo,col="yellow",border=NA)
rect(1960+xfl,range[1]+scal*0.965+ypo,1962+xfl,range[1]+scal*0.84+ypo,col="yellow",border=NA)

### SWE females % ------------------------------------------------------
plot(NULL,xlim=c(1971,2020),ylim=c(range[1],range[2]),xlab="",ylab=""
     ,las=1, axes=FALSE)
rect(1971,range[2],2020,range[1],col="grey90",border=NA)
x<-range[1]
repeat{
  lines(c(1971,2020),c(x,x),col="white")
  x=x+1;if(x>range[2]){break}}

x<-1980
repeat{
  lines(c(x,x),c(range[1],range[2]),col="white")
  x=x+10;if(x>2020){break}}
lines(yreal[1:499],rep(0,499),lwd=1,col="black",lty=1,lend=1)

x<-c(yreal[1:499],yreal[499:1])

cis2<-c(cis_swe_small_intestine_fem_1y[1,],rev(cis_swe_small_intestine_fem_1y[2,]));xx=1
polygon(x,cis2,border=NA,col=colb[xx],xpd=TRUE);xx=xx+1

cis2<-c(cis_swe_small_intestine_fem_cond[1,],rev(cis_swe_small_intestine_fem_cond[2,]))
polygon(x,cis2,border=NA,col=colb[xx],xpd=TRUE);xx=xx+1

cis2<-c(cis_swe_small_intestine_fem_5y[1,],rev(cis_swe_small_intestine_fem_5y[2,]))
polygon(x,cis2,border=NA,col=colb[xx],xpd=TRUE);xx=1

xx=1
tabce4(cis3_swe_small_intestine_fem_1y,cis_swe_small_intestine_fem_1y)
xx=xx+1
tabce4(cis3_swe_small_intestine_fem_cond,cis_swe_small_intestine_fem_cond)
xx=xx+1
tabce4(cis3_swe_small_intestine_fem_5y,cis_swe_small_intestine_fem_5y)

axis(2,las=2,cex.axis=1.4,at=seq(range[1],range[2],by=1),labels=c(range[1],rep("",length(seq(range[1],range[2],by=1))-2),range[2]),pos=1971)
#title(ylab="Change in female survival (%)", line=1, cex.lab=1.4)
axis(side=1,las=1,cex.axis=1.4,at=c(seq(1980,2020,by=10)),pos=range[1],labels=c(rep("",5)));text(c(seq(1978,2020,by=20)),c(rep(range[1]-0.05*scal,3)),c(seq(1980,2020,by=20)),xpd=TRUE,cex=1.4);
lines(c(1971,2020),c(range[1],range[1]))
title(xlab="Year", line=1, cex.lab=1.4,xpd=TRUE)
text(1974.5,range[2]-0.05*scal,"h",cex=1.9)
```


